### 2017-03-25 paper/paper.tex
Added some unfinished Python files for file and data manipulation

% Paper template for TAR 2016
% (C) 2014 Jan Šnajder, Goran Glavaš, Domagoj Alagić, Mladen Karan
% TakeLab, FER

\documentclass[10pt, a4paper]{article}

\usepackage{tar2016}

\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{amssymb}

\title{Template for writing TAR project papers}

\name{Author1, Author2, Author3}

\address{
University of Zagreb, Faculty of Electrical Engineering and Computing\\
Unska 3, 10000 Zagreb, Croatia\\ 
\texttt{autor1@xxx.hr}, \texttt{\{autor2,autor3\}@zz.com}\\
}

\abstract{ 
This document provides the instructions on formatting the TAR project paper in \LaTeX{}. This is where you write the abstract (i.e., summary) of the work you carried out. The abstract is a paragraph of text ranging between 70 and 150 words.
}

\begin{document}

\maketitleabstract

\section{Introduction}

This section is the introduction to your paper. Introduction should not be too elaborate, that is what other sections are for (the Introduction should definitely not spill over to the second page).

This is the second paragraph of the introduction. In \LaTeX , paragraphs are separated by inserting an empty line in between them.  Avoid very large paragraphs (larger than half of the page height), but also avoid tiny paragraphs (e.g., one-sentence paragraphs).

\section{Second section}

In scientific papers, this section usually (but not necessarily) briefly describes the related research.

\subsection{First subsection}
\label{sec:first}

This is a subsection of the second section.

\subsection{Second subsection}

This is the second subsection of the second section. Referencing the (sub)sections in text is performed as follows: ``in Section \ref{sec:first} we have shown \dots''.

\subsubsection{Sub-subsection example}

This is a sub-subsection. If possible, it is better to avoid sub-subsections.

\section{Extent of the paper}

The paper should have a minimum of 3 and a maximum of 5 pages, plus an additional page for references.

\section{Figures and tables}

\subsection{Figures}

Here is an example on how to include figures in the paper. Figures are included in \LaTeX{} code immediately \textit{after} the text in which these figures are referenced. Allow \LaTeX{} to place the figure where it believes is best (usually on top of the page of at the position where you would not place the figure). Figures are referenced as follows: ``Figure~\ref{fig:figure1} shows \dots''. Use tilde (\verb.~.) to prevent separation between the word ``Figure'' and its enumeration.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{drawing.pdf}
\caption{This is the figure caption. Full sentences should be followed with a dot. The caption should be placed \textit{below} the figure. Caption should be short; details should be explained in the text.}
\label{fig:figure1}
\end{center}
\end{figure}

\subsection{Tables}

There are two types of tables: narrow tables that fit into one column and a wide table that spreads over both columns.

\subsubsection{Narrow tables}

Table~\ref{tab:narrow-table} is an example of a narrow table. Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive.

\begin{table}
\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
\label{tab:narrow-table}
\begin{center}
\begin{tabular}{ll}
\toprule
Heading1 & Heading2 \\
\midrule
One & First row text \\
Two   & Second row text \\
Three   & Third row text \\
      & Fourth row text \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\subsection{Wide tables}

Table~\ref{tab:wide-table} is an example of a wide table that spreads across both columns. The same can be done for wide figures that should spread across the whole width of the page.

\begin{table*}
\caption{Wide-table caption}
\label{tab:wide-table}
\begin{center}
\begin{tabular}{llr}
\toprule
Heading1 & Heading2 & Heading3\\
\midrule
A & A very long text, longer that the width of a single column & $128$\\
B & A very long text, longer that the width of a single column & $3123$\\
C & A very long text, longer that the width of a single column & $-32$\\
\bottomrule
\end{tabular}
\end{center}
\end{table*}

\section{Math expressions and formulas}

Math expressions and formulas that appear within the sentence should be written inside the so-called \emph{inline} math environment: $2+3$, $\sqrt{16}$, $h(x)=\mathbf{1}(\theta_1 x_1 + \theta_0>0)$. Larger expressions and formulas (e.g., equations) should be written in the so-called \emph{displayed} math environment:

\[
b^{(i)}_k = \begin{cases}
1 & \text{if 
    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|$}\\
0 & \text{otherwise}
\end{cases}
\]

Math expressions which you reference in the text should be written inside the \textit{equation} environment:

\begin{equation}\label{eq:kmeans-error}
J = \sum_{i=1}^N \sum_{k=1}^K 
b^{(i)}_k \| \mathbf{x}^{(i)} - \mathbf{\mu}_k \|^2
\end{equation}

Now you can reference equation \eqref{eq:kmeans-error}. If the paragraph continues right after the formula

\begin{equation}
f(x) = x^2 + \varepsilon
\end{equation}

\noindent like this one does, use the command \emph{noindent} after the equation to remove the indentation of the row.

Multi-letter words in the math environment should be written inside the command \emph{mathit}, otherwise \LaTeX{} will insert spacing between the letters to denote the multiplication of values denoted by symbols. For example, compare
$\mathit{Consistent}(h,\mathcal{D})$ and\\
$Consistent(h,\mathcal{D})$.

If you need a math symbol, but you don't know the corresponding \LaTeX{} command that generates it, try
\emph{Detexify}.\footnote{\texttt{http://detexify.kirelabs.org/}}

\section{Referencing literature}

References to other publications should be written in brackets with the last name of the first author and the year of publication, e.g., \citep{chomsky-73}.  Multiple references are written in sequence, one after another, separated by semicolon and without whitespaces in between, e.g., \citep{chomsky-73,chave-64,feigl-58}. References are typically written at the end of the sentence and necessarily before the sentence punctuation.

If the publication is authored by more than one author, only the name of the first author is written, after which abbreviation \emph{et al.}, meaning \emph{et alia}, i.e.,~and others is written as in \citep{johnson-etc}. If the publication is authored by only two authors, then the last names of both authors are written \citep{johnson-howells}.

If the name of the author is incorporated into the text of the sentence, it should not be in the brackets (only the year should be there). E.g.,~``\citet{chomsky-73}
suggested that \dots''. The difference is whether you reference the publication or the author who wrote it.

The list of all literature references is given alphabetically at the end of the paper. The form of the reference depends on the type of the bibliographic unit: conference papers,
\citep{chave-64}, books \citep{butcher-81}, journal articles
\citep{howells-51}, doctoral dissertations \citep{croft-78}, and book chapters \citep{feigl-58}.

All of this is automatically produced when using BibTeX. Insert all the BibTeX entries into the file \texttt{tar2016.bib}, and then reference them via their symbolic names.

\section{Conclusion}

Conclusion is the last enumerated section of the paper. It should not exceed half of a column and is typically split into 2--3 paragraphs. No new information should be presented in the conclusion; this section only summarizes and concludes the paper.

\section*{Acknowledgements}

If suitable, you can include the \textit{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.

\bibliographystyle{tar2016}
\bibliography{tar2016}

\end{document}

### 2017-03-25 software/abstract_model.py

@@ -1,0 +1,11 @@
+from abc import ABC, abstractmethod
+from data import Document, Solution
+from typing import List, Tuple
+
+
+def AbstractAuthorDiarizer(ABC):
+    def train(self, dataset: List[Tuple[Document, Solution]]):
+        pass
+
+    def predict(document: Document) -> Solution:
+        pass

### 2017-03-25 software/data/__init__.py

@@ -1,0 +1,5 @@
+from .dataset import Dataset
+from .document import Document
+from .solution import Solution
+from .dataset_reader import MiniBatchReader
+from data import preparers

### 2017-03-25 software/data/dataset.py

@@ -1,0 +1,45 @@
+from typing import Tuple, List
+import numpy as np
+import random
+from .abstract_dataset import AbstractDataset
+from data.dataset_dir import load_documents, load_solutions
+
+
+class Dataset():
+    def __init__(self, documents: List[np.ndarray], solutions: List[np.ndarray]):
+        self.documents = documents
+        self.solutions = solutions
+
+    def __len__(self):
+        return len(self.documents)
+
+    def __getitem__(self, key):
+        if isinstance(key, slice):
+            return self.documents[key.start:key.stop:key.step], self.solutions[key.start:key.stop:key.step]
+        else:  # int
+            return self.documents[key], self.solutions[key]
+
+    @property
+    def size(self) -> int:
+        return len(self)
+
+    def shuffle(self, order_determining_number: float = -1):
+        """ Shuffles the data. """
+        document_solution_pairs = list(zip(self.documents, self.solutions))
+        if order_determining_number < 0:
+            random.shuffle(document_solution_pairs)
+        else:
+            random.shuffle(document_solution_pairs, lambda: order_determining_number)
+        self.documents[:], self.solutions[:] = zip(*document_solution_pairs)
+
+    def split(self, start, end):
+        """ Splits the dataset into two smaller datasets. """
+        first = Dataset(self.documents[start:end], self.solutions[start:end])
+        second = Dataset(self.documents[:start] + self.documents[end:], self.solutions[:start] + self.solutions[end:])
+        return first, second
+
+    @staticmethod
+    def load(dataset_directory: str):
+        documents = load_documents(dataset_directory)
+        solutions = load_solutions(dataset_directory)
+        return Dataset(documents, solutions)

### 2017-03-25 software/data/dataset_reader.py

@@ -1,0 +1,30 @@
+from .dataset import Dataset
+
+
+class MiniBatchReader:
+    def __init__(self, dataset: Dataset, batch_size: int):
+        self.current_batch_number = 0
+        self.dataset = dataset
+        self.batch_size = batch_size
+        self.number_of_batches = dataset.size // batch_size
+
+    def reset(self, shuffle: bool = False):
+        if shuffle:
+            self.dataset.shuffle()
+        self.current_batch_number = 0
+
+    def get_next_batch(self):
+        """ Return the next `batch_size` image-label pairs. """
+        end = self.current_batch_number + self.batch_size
+        if end > self.dataset.size:  # Finished epoch
+            return None
+        else:
+            start = self.current_batch_number
+        self.current_batch_number = end
+        return self.dataset[start:end]
+
+    def __iter__(self):
+        b = self.get_next_batch()
+        while b is not None:
+            b = self.get_next_batch()
+            yield b

### 2017-03-25 software/data/document.py

@@ -1,0 +1,4 @@
+## This file should define the class that corresponds to documents (.txt files)
+
+class Document():
+    pass

### 2017-03-25 software/data/solution.py

@@ -1,0 +1,4 @@
+## This file should define the class that corresponds to .truth files
+
+class Solution():
+    pass

### 2017-03-25 software/labeling.py

@@ -1,0 +1,8 @@
+from abc import ABC, abstractmethod
+
+
+def AbstractAuthorDiarizer(ABC):
+    def train(self, document_set):
+        pass
+    def predict(document):
+        pass

### 2017-03-25 software/util/console.py

@@ -1,0 +1,20 @@
+import select
+import sys
+
+
+def read_line(wait: bool = True, skip_to_last_line: bool = False):
+    """
+    Returns a line from standard input.
+    :param wait: If set to False and no input is available, returns None.
+    :param skip_to_last_line: If set to True and more lines are available, consumes all lines and returns the last.
+    """
+    def input_available():
+        return select.select([sys.stdin], [], [], 0)[0]
+
+    cmd = None
+    if wait or input_available():
+        cmd = input()
+        if skip_to_last_line:
+            while input_available():
+                cmd = input()
+    return cmd

### 2017-03-25 software/util/directory.py

@@ -1,0 +1,10 @@
+from typing import List
+import os.path
+
+
+def get_files(directory: str) -> List[str]:
+    """ Returns a sorted list of full paths of files in the directory. """
+    files = [f for f in (os.path.join(directory, e) for e in os.listdir(directory)) if os.path.isfile(f)]
+    files.sort()
+    return files
+

### 2017-03-25 software/util/file.py

@@ -1,0 +1,9 @@
+
+def write_all_text(path: str, text: str):
+    with open(path, mode='w') as fs:
+        fs.write(text)
+        fs.flush()
+
+def read_all_text(path: str) -> object:
+    with open(path, mode='r') as fs:
+        return fs.read()

### 2017-03-25 software/util/path.py

@@ -1,0 +1,9 @@
+import os.path
+
+
+def get_file_name(file_path: str) -> str:
+    return os.path.basename(file_path)
+
+
+def get_file_name_without_extension(file_path: str) -> str:
+    return os.path.splitext(os.path.basename(file_path))[0]

### 2017-03-25 software/labeling.py
Deleted labeling.py

@@ -1,8 +1,0 @@
-from abc import ABC, abstractmethod
-
-
-def AbstractAuthorDiarizer(ABC):
-    def train(self, document_set):
-        pass
-    def predict(document):
-        pass

### 2017-03-25 software/abstract_model.py
Added "TODO" comments

@@ -3,7 +3,7 @@ from data import Document, Solution
 from typing import List, Tuple
 
 
-def AbstractAuthorDiarizer(ABC):
+def AbstractAuthorDiarizer(ABC):  # TODO
     def train(self, dataset: List[Tuple[Document, Solution]]):
         pass
 

### 2017-03-25 software/data/dataset.py

@@ -1,12 +1,10 @@
 from typing import Tuple, List
-import numpy as np
+from data import Document, Solution
 import random
-from .abstract_dataset import AbstractDataset
-from data.dataset_dir import load_documents, load_solutions
 
 
 class Dataset():
-    def __init__(self, documents: List[np.ndarray], solutions: List[np.ndarray]):
+    def __init__(self, documents: List[Document], solutions: List[Solution]):
         self.documents = documents
         self.solutions = solutions
 
@@ -40,6 +38,6 @@ class Dataset():
 
     @staticmethod
     def load(dataset_directory: str):
-        documents = load_documents(dataset_directory)
-        solutions = load_solutions(dataset_directory)
+        documents = load_documents(dataset_directory)  # TODO
+        solutions = load_solutions(dataset_directory)  # TODO
         return Dataset(documents, solutions)

### 2017-03-25 software/data/document.py

@@ -1,4 +1,4 @@
 ## This file should define the class that corresponds to documents (.txt files)
 
-class Document():
+class Document():  # TODO
     pass

### 2017-03-25 software/data/solution.py

@@ -1,4 +1,4 @@
 ## This file should define the class that corresponds to .truth files
 
-class Solution():
+class Solution():  # TODO
     pass

### 2017-05-18 software/inpladesys/models/misc/misc.py
Fixed TokenizerPreprocessor and PipelineAuthorDiarizer

@@ -1,0 +1,25 @@
+from inpladesys.datatypes import Segment, Segmentation
+from typing import List
+import numpy as np
+
+
+def generate_segmentation(preprocessed_documents: List[List[tuple]], documents_features: List[np.ndarray],
+             document_label_lists, documents) -> List[Segmentation]:
+    assert len(documents_features) == len(preprocessed_documents)
+    segmentations = []
+    for i in range(len(documents_features)):
+        preprocessed_doc_tokens = preprocessed_documents[i]
+        doc_features = documents_features[i]
+        assert doc_features.shape[0] == len(preprocessed_doc_tokens)
+        labels = document_label_lists[i]
+        segments = []
+        for k in range(doc_features.shape[0]):
+            prep_token = preprocessed_doc_tokens[k]
+            segments.append(Segment(offset=prep_token[1],
+                                    length=prep_token[2] - prep_token[1],
+                                    author=labels[k]))
+        segmentations.append(Segmentation(author_count=max(labels) + 1,
+                                          segments=segments,
+                                          max_repairable_error=60,
+                                          document_length=len(documents[i])))
+    return segmentations

### 2017-05-19 software/inpladesys/models/feature_transformation/grouprepel_feature_transformer.py
Fixed some issues regarding PipelineAuthorDiarizer and GroupRepel

@@ -10,11 +10,13 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
     def __init__(self,
                  input_dimension,
                  output_dimension,
+                 reinitialize_on_fit,
                  nonlinear_layer_count=1,
                  nonlinearity=tf.nn.tanh,
+                 learning_rate=1e-3,
                  iteration_count=10000,
                  regularization=1,
-                 reinitialize_on_fit=True):
+                 verbose=False):
         self.iteration_count = iteration_count
         self.reinitialize_on_fit = reinitialize_on_fit
         self.initialized = False
@@ -26,9 +28,12 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
         with self.graph.as_default():
             self.sess = tf.Session()
             self._build_graph(input_dimension, output_dimension,
-                              nonlinear_layer_count, nonlinearity, regularization)
+                              nonlinear_layer_count, nonlinearity,
+                              learning_rate, regularization)
+        self.verbose = verbose
 
     def fit(self, X: List[np.ndarray], G: List[np.ndarray]):
+        assert (len(X) == len(G))
         with self.graph.as_default():
             if self.reinitialize_on_fit or not self.initialized:
                 self.sess.run(tf.global_variables_initializer())
@@ -40,17 +45,17 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
                     fetches = [self.train_step_nd, self.loss_nd, self.y]
                     feed_dict = {self.x: x, self.labels: labels}
                     _, cost, y = self.sess.run(fetches, feed_dict)
-                    if i % 100 == 9:
+                    if self.verbose and i % 100 == 9:
                         print(cost)
-                        print(y)
+                    print(cost)
 
     def transform(self, X: List[np.ndarray]) -> List[np.ndarray]:
-        with self.graph.as_default():
-            if X is not list:
-                return self.sess.run([self.y], {self.x: X})
-            return [self.sess.run([self.y], {self.x: x}) for x in X]
+        # with self.graph.as_default():
+        #    if X is not list:
+        #        return self.sess.run([self.y], {self.x: X})
[…]

### 2017-05-19 software/inpladesys/models/pipeline_author_diarizer.py

@@ -1,7 +1,9 @@
 from inpladesys.datatypes import Document, Segment, Segmentation, Dataset
 from .abstract_author_diarizer import AbstractAuthorDiarizer
 from inpladesys.models.feature_transformation import GroupRepelFeatureTransformer
-import pickle
+from inpladesys.util.cacher import Cacher
+from sklearn import preprocessing
+import numpy as np
 
 
 class PipelineAuthorDiarizer(AbstractAuthorDiarizer):
@@ -9,9 +11,10 @@ class PipelineAuthorDiarizer(AbstractAuthorDiarizer):
         self.preprocessor = parameters['document_preprocessor']
         self.bfe = parameters['basic_feature_extractor']
         # TODO: move to bfe constructor
-        #self.bfe.context_size = parameters['context_size']
+        # self.bfe.context_size = parameters['context_size']
         self.ft = parameters['feature_transformer']
         self.segmentation_generator = parameters['model']
+        self.cacher = Cacher(cache_dir, dummy=cache_dir is None)
 
     def train(self, dataset: Dataset):
         docs, segmentations = dataset.documents, dataset.segmentations
@@ -21,34 +24,50 @@ class PipelineAuthorDiarizer(AbstractAuthorDiarizer):
         preprocessed_corpus = self.preprocessor.fit_transform(corpus)
         self.bfe.fit(corpus, preprocessed_corpus)
 
+        @self.cacher.cache()
+        def preprocess_training_data():
+            preprocessed_docs = []
+            document_token_features = []  # [document index][token index]
+            document_token_labels = []
+            for i in range(dataset.size):
+                doc = docs[i]
+                prepr_doc = self.preprocessor.fit_transform(docs[i])
+                preprocessed_docs.append(prepr_doc)
+                document_token_features.append(
+                    preprocessing.scale(self.bfe.transform(doc, prepr_doc)))
+                o2a = segmentations[i].offsets_to_authors
+                document_token_labels.append(o2a(t[1] for t in prepr_doc))
+                print('Document {}/{}'.format(i + 1, dataset.size))
+            return preprocessed_docs, document_token_features, document_token_labels
+
         print("(2/5) Preprocessing training data...")
-        preprocessed_docs = []
-        document_token_features = []  # [document index][token index]
-        document_token_labels = []
-        for i in range(dataset.size):
-            doc = docs[i]
[…]

### 2017-05-19 software/inpladesys/util/cacher.py

@@ -1,0 +1,54 @@
+import pickle
+import os
+import os.path as path
+from inpladesys.util.directory import get_files
+
+
+class Cacher:
+    def __init__(self, dir, dummy=False):
+        self._dummy = dummy
+        if dummy:
+            return
+        self._dir = dir
+        if not os.path.exists(dir):
+            os.makedirs(dir)
+        self._files = set(path.splitext(file)[0] for file in os.listdir(dir))
+        pass
+
+    def _open(self, name, mode):
+        return open(path.join(self._dir, name + ".p"), mode)
+
+    def __contains__(self, item):
+        return item in self._files
+
+    def __getitem__(self, item):
+        return pickle.load(self._open(item, 'rb'))
+
+    def __setitem__(self, key, value):
+        pickle.dump(value, self._open(key, 'wb'))
+
+    def cache(self):
+        def decorator(func):
+            if self._dummy:
+                return lambda: value
+            elif func.__name__ in self:
+                return lambda: self[func.__name__]
+            else:
+                value = func()
+                self[func.__name__] = value
+                return lambda: value
+        return decorator
+
+
+if __name__ == "__main__":
+    c = Cacher(".cache-test")
+    c["a"] = [i for i in range(5)]
+    c["b"] = [i ** 2 for i in range(5)]
+    print(c["a"])
+
+    @c.cache()
+    def test():
+        import time
+        return time.ctime(), "kupus"
+
+    print(test())

### 2017-05-19 software/test-grouprepel.py

@@ -2,32 +2,41 @@ from inpladesys.models.feature_transformation import GroupRepelFeatureTransforme
 import numpy as np
 import tensorflow as tf
 
-vectors = np.array(
-    [[-1, 1, 1],
-     [-1, 1, 1],
-     [-1, 1, 1],
-     [1, 2, 0],
-     [1, 0, 2],
-     [5, -2, 5],
-     [6, 2, 4],
-     [3, 0, 3],
-     [3, -3, -2],
-     [4, 2, -2],
-     [0, 2, 0],
-     [0, -5, 0],
-     [0, -2, 0]], dtype=np.float)
-labels = np.array([0, 0, 0, 1, 1, 2, 2, 3, 3, 3, 4, 4, 4])
+vector_arrays = [
+    np.array(
+        [[-1, 1, 1],
+         [-1, 1, 1],
+         [-1, 1, 1],
+         [1, 2, 0],
+         [1, 0, 2],
+         [5, -2, 5],
+         [6, 2, 4],
+         [3, 0, 3],
+         [3, -3, -2],
+         [4, 2, -2],
+         [0, 2, 0],
+         [0, -5, 0],
+         [0, -2, 0]], dtype=np.float),
+    np.array(
+        [[-2, 1, 1],
+         [0, 3, 0],
+         [0, -5, 0],
+         [0, 0, 0]], dtype=np.float)]
 
+label_arrays = [np.array([0, 0, 0, 1, 1, 2, 2, 3, 3, 3, 4, 4, 4]),
+                np.array([0, 1, 1, 1])]
 
 grft = GroupRepelFeatureTransformer(
     3, 2, nonlinear_layer_count=1, iteration_count=50, reinitialize_on_fit=False)
- 
+
 import matplotlib.pyplot as plt
+
 plt.ion()
 
 for i in range(100):
-    grft.fit([vectors], [labels])
-    result = grft.transform(vectors)[0]
+    grft.fit(vector_arrays, label_arrays)
+    result = grft.transform(vector_arrays[0:1])[0]
     plt.clf()
-    plt.scatter(result[:, 0], result[:, 1], c=labels)
+    a = result[:, 0]
+    plt.scatter(result[:, 0], result[:, 1], c=label_arrays[0])
     plt.pause(0.05)

### 2017-05-19 software/test_pipeline.py

@@ -2,7 +2,7 @@ from inpladesys.datasets import Pan16DatasetLoader
 from inpladesys.models.preprocessors.basic_preprocessors import TokenizerPreprocessor
 from inpladesys.models.basic_feature_extraction.basic_feature_extractor import BasicFeatureExtractor
 from inpladesys.models.pipeline_author_diarizer import PipelineAuthorDiarizer
-import numpy as np
+from  inpladesys.util.cacher import Cacher
 
 dataset_dirs = [
     "../data/pan16-author-diarization-training-dataset-problem-a-2016-02-16",
@@ -19,11 +19,11 @@ params = dict()
 # params['dataset'] = dataset
 # params['context_size'] = 100
 params['document_preprocessor'] = TokenizerPreprocessor()
-params['basic_feature_extractor'] = BasicFeatureExtractor(features_file_name, context_size=50)
+params['basic_feature_extractor'] = BasicFeatureExtractor(features_file_name, context_size=30)
 params['feature_transformer'] = None
 # params['model'] = KMeansDiarizer()
 params['model'] = None
-pad = PipelineAuthorDiarizer(params)
+pad = PipelineAuthorDiarizer(params, cache_dir=".pipeline-cache")
 dataset.shuffle(order_determining_number=1337)
-dataset = dataset[0:10]
+dataset = dataset[0:2]
 pad.train(dataset)

### 2017-05-19 software/inpladesys/TODOs.py
learning_pipeline_task_b.py refactored to ...task_x.py and customized for all tasks, other task_a and c files deleted. Other minor changes.

@@ -1,6 +1,7 @@
 # + TODO allow SimpleFixedAuthorDiarizer to adjust number of authors in BASELINE tests
-# TODO implement scorers as parameters for learning pipeline ?
+# + TODO implement scorers as parameters for learning pipeline ?
 # + TODO implement interfacce for models
+# TODO baseline results which use rand should be evaluated on 50 runs
 # TODO fix warnings in training
 # TODO add new features (new "iteration"):
 #   - type-token ratio (vocabulary richness)
@@ -15,4 +16,5 @@
 # TODO finish neural net
 # TODO implement elbow method (or some other ?) for task c
 # TODO implement t-test for all tasks
+# task a: window size is cca. 14-18
 

### 2017-05-19 software/inpladesys/models/clustering/hac_diarizer.py

@@ -48,7 +48,7 @@ class AgglomerativeDiarizer(AbstractDiarizer):
                 segments.append(Segment(offset=offset, length=length, author=author))
 
             segmentations.append(
-                Segmentation(num_authors, segments, maxRepairableError=60, document_length=len(dataset.documents[i])))
+                Segmentation(num_authors, segments, max_repairable_error=60, document_length=len(dataset.documents[i])))
 
             print('Document', i+1, '/', len(documents_features), 'in', time.time()-start_time, 's')
 

### 2017-05-19 software/inpladesys/models/clustering/k_means_diarizer.py

@@ -52,7 +52,7 @@ class KMeansDiarizer(AbstractDiarizer):
                 length = prep_token[2] - prep_token[1]
                 segments.append(Segment(offset=offset, length=length, author=author))
 
-            segmentations.append(Segmentation(num_authors, segments, maxRepairableError=60, document_length=len(dataset.documents[i])))
+            segmentations.append(Segmentation(num_authors, segments, max_repairable_error=60, document_length=len(dataset.documents[i])))
 
         return segmentations
 

### 2017-05-19 software/inpladesys/models/learning_pipeline_task_a.py

@@ -1,98 +1,0 @@
-import time
-import numpy as np
-from inpladesys.datasets import Pan16DatasetLoader
-from inpladesys.models.preprocessors.basic_preprocessors import TokenizerPreprocessor
-from inpladesys.models.basic_feature_extraction.basic_feature_extractor import BasicFeatureExtractor
-from inpladesys.evaluation import *
-from inpladesys.evaluation import get_confusion_matrix
-from inpladesys.models.clustering.k_means_diarizer import KMeansDiarizer
-
-
-class LearningPipeline:
-
-    def __init__(self, parameters: dict):
-        self.dataset = parameters['dataset']
-        self.context_size = parameters['context_size']
-        self.document_preprocessor = parameters['document_preprocessor']
-        self.basic_feature_extractor = parameters['basic_feature_extractor']
-        self.feature_transformer = parameters['feature_transformer']
-        self.model = parameters['model']
-
-    def do_chain(self):
-        documents_features = []
-
-        print('Extracting features...')
-        start_time = time.time()
-
-        preprocessed_docs = []
-
-        for i in range(self.dataset.size):  #self.dataset.size
-            document, segmentation = self.dataset[i]
-            preprocessed_document = self.document_preprocessor.fit_transform(document)
-            self.basic_feature_extractor.fit(document, preprocessed_document)
-            document_features = self.basic_feature_extractor.transform(document, preprocessed_document,
-                                                                       self.context_size)
-            print('Document {}/{}: {}'.format(i+1, self.dataset.size, document_features.shape))
-
-            # TODO postprocess features (transformations etc.)
-
-            documents_features.append(document_features)
-            preprocessed_docs.append(preprocessed_document)
-
-        print('Extraction time (s): ', time.time() - start_time)
-
-        if True:
-
-            print('Running model..')
-            # TODO is it better to use fit and _predict separately ??
-            pred_segmentations = self.model.fit_predict(self.dataset, documents_features, preprocessed_docs)
-
-            # TODO postprocess model results
-
-
-            # TODO evaluate results
-            print('Evaluating...')
-            results = np.array([0, 0, 0], dtype=np.float64)
-            for i in range(self.dataset.size):  #self.dataset.size
-                truth = self.dataset.segmentations[i]
-                pred = pred_segmentations[i]
-
[…]

### 2017-05-19 software/inpladesys/models/learning_pipeline_task_b.py

@@ -1,100 +1,0 @@
-import time
-import numpy as np
-from inpladesys.datasets import Pan16DatasetLoader
-from inpladesys.models.preprocessors.basic_preprocessors import TokenizerPreprocessor
-from inpladesys.models.basic_feature_extraction.basic_feature_extractor import BasicFeatureExtractor
-from inpladesys.evaluation import *
-from inpladesys.evaluation import get_confusion_matrix
-from inpladesys.models.clustering.k_means_diarizer import KMeansDiarizer
-from inpladesys.models.clustering.hac_diarizer import AgglomerativeDiarizer
-
-
-
-class LearningPipeline:
-
-    def __init__(self, parameters: dict):
-        self.dataset = parameters['dataset']
-        self.context_size = parameters['context_size']
-        self.document_preprocessor = parameters['document_preprocessor']
-        self.basic_feature_extractor = parameters['basic_feature_extractor']  # TODO rename to basic
-        self.feature_transformer = parameters['feature_transformer']
-        self.model = parameters['model']
-
-    def do_chain(self):
-        documents_features = []
-
-        print('Extracting features...')
-        start_time = time.time()
-
-        preprocessed_docs = []
-        dataset_size = 6 #self.dataset.size
-
-        for i in range(dataset_size):
-            document, segmentation = self.dataset[i]
-            preprocessed_document = self.document_preprocessor.fit_transform(document)
-            self.basic_feature_extractor.fit(document, preprocessed_document)
-            document_features = self.basic_feature_extractor.transform(document, preprocessed_document,
-                                                                       self.context_size)
-            print('Document {}/{}: {}'.format(i+1, self.dataset.size, document_features.shape))
-
-            # TODO postprocess features (transformations etc.)
-
-            documents_features.append(document_features)
-            preprocessed_docs.append(preprocessed_document)
-
-        print('Extraction time (s): ', time.time() - start_time)
-
-        if True:
-
-            print('Running model..')
-            # TODO is it better to use fit and _predict separately ??
-            pred_segmentations = self.model.fit_predict(preprocessed_docs, documents_features, self.dataset)
-
-            # TODO postprocess model results
-
-            # TODO evaluate results
-            print('Evaluating...')
-            results = np.array([0, 0, 0], dtype=np.float64)
-            for i in range(dataset_size):
[…]

### 2017-05-19 software/inpladesys/models/learning_pipeline_task_c.py

@@ -1,98 +1,0 @@
-import time
-import numpy as np
-from inpladesys.datasets import Pan16DatasetLoader
-from inpladesys.models.preprocessors.basic_preprocessors import TokenizerPreprocessor
-from inpladesys.models.basic_feature_extraction.basic_feature_extractor import BasicFeatureExtractor
-from inpladesys.evaluation import *
-from inpladesys.evaluation import get_confusion_matrix
-from inpladesys.models.clustering.k_means_diarizer import KMeansDiarizer
-
-
-class LearningPipeline:
-
-    def __init__(self, parameters: dict):
-        self.dataset = parameters['dataset']
-        self.context_size = parameters['context_size']
-        self.document_preprocessor = parameters['document_preprocessor']
-        self.basic_feature_extractor = parameters['basic_feature_extractor']  # TODO rename to basic
-        self.feature_transformer = parameters['feature_transformer']
-        self.model = parameters['model']
-
-    def do_chain(self):
-        documents_features = []
-
-        print('Extracting features...')
-        start_time = time.time()
-
-        preprocessed_docs = []
-
-        for i in range(self.dataset.size):  #self.dataset.size
-            document, segmentation = self.dataset[i]
-            preprocessed_document = self.document_preprocessor.fit_transform(document)
-            self.basic_feature_extractor.fit(document, preprocessed_document)
-            document_features = self.basic_feature_extractor.transform(document, preprocessed_document,
-                                                                       self.context_size)
-            print('Document {}/{}: {}'.format(i+1, self.dataset.size, document_features.shape))
-
-            # TODO postprocess features (transformations etc.)
-
-            documents_features.append(document_features)
-            preprocessed_docs.append(preprocessed_document)
-
-        print('Extraction time (s): ', time.time() - start_time)
-
-        if True:
-
-            print('Running model..')
-            # TODO is it better to use fit and _predict separately ??
-            pred_segmentations = self.model.fit_predict(self.dataset, documents_features, preprocessed_docs)
-
-            # TODO postprocess model results
-
-
-            # TODO evaluate results
-            print('Evaluating...')
-            results = np.array([0, 0, 0], dtype=np.float64)
-            for i in range(self.dataset.size):  #self.dataset.size
-                truth = self.dataset.segmentations[i]
-                pred = pred_segmentations[i]
-
[…]

### 2017-05-19 software/inpladesys/models/learning_pipeline_task_x.py

@@ -1,0 +1,137 @@
+import time
+import numpy as np
+from inpladesys.datasets import Pan16DatasetLoader
+from inpladesys.models.preprocessors.basic_preprocessors import TokenizerPreprocessor
+from inpladesys.models.basic_feature_extraction.basic_feature_extractor import BasicFeatureExtractor
+from inpladesys.evaluation import *
+from inpladesys.evaluation import get_confusion_matrix
+from inpladesys.models.clustering.k_means_diarizer import KMeansDiarizer
+from inpladesys.models.clustering.hac_diarizer import AgglomerativeDiarizer
+
+
+
+class LearningPipeline:
+
+    def __init__(self, parameters: dict):
+        self.dataset = parameters['dataset']
+        self.context_size = parameters['context_size']
+        self.document_preprocessor = parameters['document_preprocessor']
+        self.basic_feature_extractor = parameters['basic_feature_extractor']
+        self.feature_transformer = parameters['feature_transformer']
+        self.model = parameters['model']
+        self.scorer_1 = parameters['scorer_class_1']
+        self.scorer_2 = parameters['scorer_class_2']
+
+    def do_chain(self):
+        documents_features = []
+
+        print('Extracting features...')
+        start_time = time.time()
+
+        preprocessed_docs = []
+        dataset_size = self.dataset.size
+
+        for i in range(dataset_size):
+            document, segmentation = self.dataset[i]
+            preprocessed_document = self.document_preprocessor.fit_transform(document)
+            self.basic_feature_extractor.fit(document, preprocessed_document)
+            document_features = self.basic_feature_extractor.transform(document, preprocessed_document,
+                                                                       self.context_size)
+            print('Document {}/{}: {}'.format(i+1, dataset_size, document_features.shape))
+
+            # TODO postprocess features (transformations etc.)
+
+            documents_features.append(document_features)
+            preprocessed_docs.append(preprocessed_document)
+
+        print('Extraction time (s): ', time.time() - start_time)
+
+        if True:
+
+            print('Running model..')
+            # TODO is it better to use fit and _predict separately ??
+            pred_segmentations = self.model.fit_predict(preprocessed_docs, documents_features, self.dataset)
+
+            # TODO postprocess model results
+
+            # Evaluation
[…]

### 2017-05-19 software/inpladesys/models/clustering/hac_diarizer.py
Generation of segments in diarizer models replaced with generate_segmentation from misc. Other minor changes.

@@ -5,6 +5,8 @@ from inpladesys.datatypes import *
 from sklearn import preprocessing
 from sklearn.cluster import AgglomerativeClustering
 import time
+from inpladesys.models.misc.misc import generate_segmentation
+
 
 class AgglomerativeDiarizer(AbstractDiarizer):
 
@@ -13,7 +15,7 @@ class AgglomerativeDiarizer(AbstractDiarizer):
 
         assert len(documents_features) == len(preprocessed_documents)
 
-        segmentations = []
+        document_label_lists = []
 
         for i in range(len(documents_features)):
             start_time = time.time()
@@ -37,19 +39,9 @@ class AgglomerativeDiarizer(AbstractDiarizer):
                                                linkage='average')
 
             labels = diarizer.fit_predict(x_scaled)
-
-            segments = []
-
-            for k in range(doc_features.shape[0]):
-                author = labels[k]
-                prep_token = preprocessed_doc_tokens[k]
-                offset = prep_token[1]
-                length = prep_token[2] - prep_token[1]
-                segments.append(Segment(offset=offset, length=length, author=author))
-
-            segmentations.append(
-                Segmentation(num_authors, segments, max_repairable_error=60, document_length=len(dataset.documents[i])))
+            document_label_lists.append(labels)
 
             print('Document', i+1, '/', len(documents_features), 'in', time.time()-start_time, 's')
 
-        return segmentations
+        return generate_segmentation(preprocessed_documents, documents_features,
+                                     document_label_lists, dataset.documents)

### 2017-05-19 software/inpladesys/models/clustering/k_means_diarizer.py

@@ -7,6 +7,8 @@ from sklearn.preprocessing import Normalizer
 from inpladesys.datatypes import *
 from typing import List
 import numpy as np
+import time
+from inpladesys.models.misc.misc import generate_segmentation
 
 
 class KMeansDiarizer(AbstractDiarizer):
@@ -17,9 +19,11 @@ class KMeansDiarizer(AbstractDiarizer):
 
         assert len(documents_features) == len(preprocessed_documents)
 
-        segmentations = []
+        document_label_lists = []
 
         for i in range(len(documents_features)):
+            start_time = time.time()
+
             preprocessed_doc_tokens = preprocessed_documents[i]
             doc_features = documents_features[i]
             num_authors = dataset.segmentations[i].author_count
@@ -42,18 +46,11 @@ class KMeansDiarizer(AbstractDiarizer):
                             verbose=0)  # “auto” chooses “elkan” for dense data and “full” (EM style) for sparse data.
 
             labels = diarizer.fit_predict(x_scaled)
+            document_label_lists.append(labels)
 
-            segments = []
+            print('Document', i + 1, '/', len(documents_features), 'in', time.time() - start_time, 's')
 
-            for k in range(doc_features.shape[0]):
-                author = labels[k]
-                prep_token = preprocessed_doc_tokens[k]
-                offset = prep_token[1]
-                length = prep_token[2] - prep_token[1]
-                segments.append(Segment(offset=offset, length=length, author=author))
-
-            segmentations.append(Segmentation(num_authors, segments, max_repairable_error=60, document_length=len(dataset.documents[i])))
-
-        return segmentations
+        return generate_segmentation(preprocessed_documents, documents_features,
+                                     document_label_lists, dataset.documents)
 
 

### 2017-05-19 software/inpladesys/models/learning_pipeline_task_x.py

@@ -95,7 +95,7 @@ if True:
     task = 'a'
 
     if task == 'a':
-        print("Loading dataset...")
+        print("Loading dataset for task ", task, "...")
         params['dataset'] = Pan16DatasetLoader(dataset_dirs[0]).load_dataset()
         params['context_size'] = 16
         params['document_preprocessor'] = TokenizerPreprocessor()
@@ -106,7 +106,7 @@ if True:
         params['scorer_class_2'] = MacroScorer
 
     elif task == 'b':
-        print("Loading dataset...")
+        print("Loading dataset for task ", task, "...")
         params['dataset'] = Pan16DatasetLoader(dataset_dirs[1]).load_dataset()
         params['context_size'] = 140  # 140 for kmeans
         params['document_preprocessor'] = TokenizerPreprocessor()
@@ -117,7 +117,7 @@ if True:
         params['scorer_class_2'] = None
 
     elif task == 'c':
-        print("Loading dataset...")
+        print("Loading dataset for task ", task, "...")
         params['dataset'] = Pan16DatasetLoader(dataset_dirs[2]).load_dataset()
         params['context_size'] = 100
         params['document_preprocessor'] = TokenizerPreprocessor()

### 2017-05-19 software/inpladesys/util/cacher.py
Added support for multiple arguments to Cacher, modified PipelineAuthorDiarizer

@@ -27,16 +27,26 @@ class Cacher:
     def __setitem__(self, key, value):
         pickle.dump(value, self._open(key, 'wb'))
 
-    def cache(self):
+    def __call__(self, name=None):
+        """
+        :param name: name of the file to store the result in - set to function name if not stated
+        """
         def decorator(func):
+            nonlocal name
+            if name is None:
+                name = func.__name__
             if self._dummy:
-                return lambda: value
-            elif func.__name__ in self:
-                return lambda: self[func.__name__]
+                return func
+            elif name in self:
+                def wrapper(*args, **kwargs):
+                    return self[name]
+                return wrapper
             else:
-                value = func()
-                self[func.__name__] = value
-                return lambda: value
+                def wrapper(*args, **kwargs):
+                    value = func(*args, **kwargs)
+                    self[name] = value
+                    return value
+                return wrapper
         return decorator
 
 
@@ -46,9 +56,11 @@ if __name__ == "__main__":
     c["b"] = [i ** 2 for i in range(5)]
     print(c["a"])
 
+
     @c.cache()
     def test():
         import time
         return time.ctime(), "kupus"
+
 
     print(test())

### 2017-05-19 software/test_pipeline.py

@@ -31,6 +31,6 @@ params['clusterer'] = KMeans()
 
 pad = PipelineAuthorDiarizer(params, cache_dir=".pipeline-cache")
 dataset.shuffle(order_determining_number=1337)
-train_data, test_data = dataset.split(0, int(0.7 * dataset.size))
+train_data, test_data = dataset.split(0, 2+0*int(0.7 * dataset.size))
 # train_data, validation_data = train_data.split(0, int(0.7*train_data.size))
 pad.train(train_data)

### 2017-05-19 software/inpladesys/util/cacher.py
Updated Cacher usage example in cacher.py

@@ -57,10 +57,10 @@ if __name__ == "__main__":
     print(c["a"])
 
 
-    @c.cache()
+    @c()
     def test():
         import time
-        return time.ctime(), "kupus"
+        return time.ctime(), "foo"
 
 
     print(test())

### 2017-05-19 software/inpladesys/models/basic_feature_extraction/features/simple/pos_tag_char_ngrams.py
Added type-token ratio and char n-grams of POS tags features.

@@ -1,0 +1,24 @@
+from inpladesys.models.basic_feature_extraction.features.abstract_single_feature_extractor import AbstractSingleFeatureExtractor
+from sklearn.feature_extraction.text import CountVectorizer
+from inpladesys.models.basic_feature_extraction.sliding_window import SlidingWindow
+
+
+class CharNGramsOfPOSTagsExtractor(AbstractSingleFeatureExtractor):
+
+    def __init__(self, params=None):
+        super().__init__(params)
+        self.cv = CountVectorizer(analyzer='char',
+                                  lowercase=False,
+                                  #max_features=params['max_features'],  # TODO should we use max_features arg ?
+                                  ngram_range=(params['min_ngram_range'], params['max_ngram_range']),
+                                  )
+
+    def fit(self, document, preprocessed_document=None, tokens=None):
+        pos_document = " ".join([t[3] for t in preprocessed_document])
+        self.cv.fit([pos_document])
+
+    def transform(self, sliding_window: SlidingWindow):
+        data = sliding_window.data
+        return self.cv.transform([" ".join(data['left_context_pos_tags'])]) + \
+               self.cv.transform([" ".join(data['right_context_pos_tags'])])
+

### 2017-05-19 software/inpladesys/models/basic_feature_extraction/features/simple/type_token_ratio.py

@@ -1,0 +1,22 @@
+from inpladesys.models.basic_feature_extraction.features.abstract_single_feature_extractor import AbstractSingleFeatureExtractor
+from sklearn.feature_extraction.text import CountVectorizer
+from inpladesys.models.basic_feature_extraction.sliding_window import SlidingWindow
+
+
+class TypeTokenRatioExtractor(AbstractSingleFeatureExtractor):
+
+    def __init__(self, params=None):
+        super().__init__(params)
+        self.cv = CountVectorizer(lowercase=True,
+                                  ngram_range=(1, 1),
+                                  binary=True,
+                                  token_pattern=params['token_pattern'])
+
+    def fit(self, document, preprocessed_document=None, tokens=None):
+        self.cv.fit(tokens)
+
+    def transform(self, sliding_window: SlidingWindow):
+        data = sliding_window.data
+        tokens = data['left_context_tokens'] + data['right_context_tokens']
+        return len(self.cv.vocabulary_) / len(tokens)
+

### 2017-05-19 software/inpladesys/models/pipeline_author_diarizer.py
Improved Cacher, added dummy Cacher factory method, implemented predict in PipelineAuthorDiarizer

@@ -1,73 +1,93 @@
 from inpladesys.datatypes import Document, Segment, Segmentation, Dataset
 from .abstract_author_diarizer import AbstractAuthorDiarizer
-from inpladesys.models.feature_transformation import GroupRepelFeatureTransformer
+from inpladesys.models.misc import generate_segmentation
+from inpladesys.models.preprocessors.basic_preprocessors import TokenizerPreprocessor
 from inpladesys.util.cacher import Cacher
 from sklearn import preprocessing
-import numpy as np
 
 
 class PipelineAuthorDiarizer(AbstractAuthorDiarizer):
-    def __init__(self, parameters: dict, cache_dir=None, random_state=-1):
-        self.preprocessor = parameters['document_preprocessor']
+    def __init__(self, parameters: dict, cacher=None, random_state=-1):
+        self.preprocessor = TokenizerPreprocessor()
         self.bfe = parameters['basic_feature_extractor']
-        # TODO: move to bfe constructor
-        # self.bfe.context_size = parameters['context_size']
-        self.ft = parameters['feature_transformer']
+        self.feature_transformer = parameters['feature_transformer']
         self.clusterer = parameters['clusterer']
-        self.cacher = Cacher(cache_dir, dummy=cache_dir is None)
+        self.cacher = Cacher.dummy() if cacher is None else cacher
+        self.bfe_trained = False
 
     def train(self, dataset: Dataset):
-        docs, segmentations = dataset.documents, dataset.segmentations
-
-        print("(1/5) Training basic feature extractor...")
-        corpus = "\n\n".join(doc for doc, _ in dataset)
-        preprocessed_corpus = self.preprocessor.fit_transform(corpus)
-        self.bfe.fit(corpus, preprocessed_corpus)
-
         @self.cacher("preprocessed-training-datapoints")
-        def get_preprocessed_data(documents):
-            documents_tokens = []
-            documents_tokens_features = []  # [document index][token index]
-            for i in range(dataset.size):
-                doc = documents[i]
-                tokens = self.preprocessor.fit_transform(docs[i])
-                documents_tokens.append(tokens)
-                documents_tokens_features.append(
-                    preprocessing.scale(self.bfe.transform(doc, tokens)))
-                print('Document {}/{}'.format(i + 1, dataset.size))
-            return documents_tokens, documents_tokens_features
+        def _preprocess_documents(documents):
[…]

### 2017-05-19 software/inpladesys/util/cacher.py

@@ -13,7 +13,15 @@ class Cacher:
         if not os.path.exists(dir):
             os.makedirs(dir)
         self._files = set(path.splitext(file)[0] for file in os.listdir(dir))
-        pass
+
+    @staticmethod
+    def dummy():
+        return Cacher(dir=None, dummy=True)
+
+    def clear(self):
+        for f in self._files:
+            os.remove(f)
+        self._files = set()
 
     def _open(self, name, mode):
         return open(path.join(self._dir, name + ".p"), mode)

### 2017-05-19 software/test_pipeline.py

@@ -18,18 +18,16 @@ dataset = Pan16DatasetLoader(dataset_dirs[2]).load_dataset()
 features_file_name = 'inpladesys/models/basic_feature_extraction/features_files/features1m.json'
 
 params = dict()
-
-params['document_preprocessor'] = TokenizerPreprocessor()
 params['basic_feature_extractor'] = BasicFeatureExtractor(features_file_name, context_size=30)
 params['feature_transformer'] = GroupRepelFeatureTransformer(
     output_dimension=2,
     reinitialize_on_fit=False,
     nonlinear_layer_count=0,
     iteration_count=10,
-    learning_rate=2e-3)  # params['model'] = KMeansDiarizer()
-params['clusterer'] = KMeans()
+    learning_rate=1e-3)  # params['model'] = KMeansDiarizer()
+params['clusterer'] = KMeans(n_clusters=5)
 
-pad = PipelineAuthorDiarizer(params, cache_dir=".pipeline-cache")
+pad = PipelineAuthorDiarizer(params, cacher=Cacher(".pipeline-cache"))
 dataset.shuffle(order_determining_number=1337)
 train_data, test_data = dataset.split(0, 2+0*int(0.7 * dataset.size))
 # train_data, validation_data = train_data.split(0, int(0.7*train_data.size))

### 2017-05-19 software/inpladesys/TODOs.py
Previous commit updated.

@@ -9,6 +9,8 @@
 #   + char n-grams of POS tags
 #   - chunks (phrases)
 #   - synonyms ?
+#   - lexical density: the ratio of content words to grammatical words
+#   - LSA/LSI/word2vec udaljenosti trenutnog tokena od ostalih u windowu
 # TODO try other algorithms: DBSCAN, OPTICS, HAC, Spectral, EM
 # TODO add writing of test results to a file
 # TODO experiment with params (what combs ?)

### 2017-05-19 software/inpladesys/models/clustering/dbscan_diarizer.py

@@ -1,0 +1,61 @@
+from inpladesys.models.abstract_diarizer import AbstractDiarizer
+from inpladesys.models.misc.misc import generate_segmentation
+from sklearn.preprocessing import StandardScaler
+from typing import List
+import numpy as np
+from inpladesys.datatypes import *
+from sklearn import preprocessing
+from sklearn.cluster import DBSCAN
+import time
+
+
+class DBSCANDiarizer(AbstractDiarizer):
+
+    def fit_predict(self, preprocessed_documents: List[List[tuple]], documents_features: List[np.ndarray],
+                    dataset: Dataset) -> List[Segmentation]:
+
+        assert len(documents_features) == len(preprocessed_documents)
+
+        predicted_label_lists = []
+
+        for i in range(len(documents_features)):
+            start_time = time.time()
+
+            preprocessed_doc_tokens = preprocessed_documents[i]
+            doc_features = documents_features[i]
+            true_n_clusters = dataset.segmentations[i].author_count
+
+            assert doc_features.shape[0] == len(preprocessed_doc_tokens)
+
+            # svd = TruncatedSVD(n_components=50)
+            # normalizer = Normalizer(copy=False)
+            # lsa = make_pipeline(svd, normalizer)
+            # x_scaled = lsa.fit_transform(doc_features)
+
+            x_scaled = StandardScaler().fit_transform(doc_features)  #preprocessing.scale(doc_features, axis=0)
+            # x_scaled = doc_features
+
+            diarizer = DBSCAN(eps=6.1,
+                              min_samples=5,
+                              metric='manhattan',
+                              algorithm='auto',  # The algorithm to be used by the NearestNeighbors module to compute pointwise distances and find nearest neighbors.
+                              leaf_size=30)  # Leaf size passed to BallTree or cKDTree.
+
+            labels = diarizer.fit_predict(x_scaled)
+            predicted_label_lists.append(labels)
+
+            estimated_n_clusters = len(set(labels)) - (1 if -1 in labels else 0)
+
+            noisy = 0
+            for l_i in range(len(labels)):
+                if labels[l_i] == -1:
+                    labels[l_i] = 0  # TODO fix this !!!!
+                    noisy += 1
+
+            print('Document', i+1, '/', len(documents_features), 'in', time.time()-start_time, 's',)
+            print('Real author count = {}, estimated = {}, noisy = '.format(true_n_clusters,
+                                                                            estimated_n_clusters), noisy)
+            print()
+
[…]

### 2017-05-19 software/inpladesys/models/learning_pipeline_task_x.py

@@ -7,7 +7,7 @@ from inpladesys.evaluation import *
 from inpladesys.evaluation import get_confusion_matrix
 from inpladesys.models.clustering.k_means_diarizer import KMeansDiarizer
 from inpladesys.models.clustering.hac_diarizer import AgglomerativeDiarizer
-
+from inpladesys.models.clustering.dbscan_diarizer import DBSCANDiarizer
 
 
 class LearningPipeline:
@@ -29,7 +29,7 @@ class LearningPipeline:
         start_time = time.time()
 
         preprocessed_docs = []
-        dataset_size = 10 #self.dataset.size
+        dataset_size = 1 #self.dataset.size
 
         for i in range(dataset_size):
             document, segmentation = self.dataset[i]
@@ -92,7 +92,7 @@ if True:
     params = dict()
 
     # Change the task here
-    task = 'a'
+    task = 'c'
 
     if task == 'a':
         print("Loading dataset for task ", task, "...")
@@ -119,11 +119,11 @@ if True:
     elif task == 'c':
         print("Loading dataset for task ", task, "...")
         params['dataset'] = Pan16DatasetLoader(dataset_dirs[2]).load_dataset()
-        params['context_size'] = 100
+        params['context_size'] = 140
         params['document_preprocessor'] = TokenizerPreprocessor()
         params['basic_feature_extractor'] = BasicFeatureExtractor(features_file_name)
         params['feature_transformer'] = None
-        params['model'] = AgglomerativeDiarizer()  # AgglomerativeDiarizer()  #KMeansDiarizer()
+        params['model'] = DBSCANDiarizer()  # AgglomerativeDiarizer()  #KMeansDiarizer()
         params['scorer_class_1'] = BCubedScorer
         params['scorer_class_2'] = None
 

### 2017-05-19 software/inpladesys/models/misc/dataset_splitter.py

@@ -1,0 +1,32 @@
+import numpy as np
+from typing import List
+from inpladesys.datatypes.dataset import Dataset
+from sklearn.model_selection import train_test_split
+
+
+def custom_train_test_split(preprocessed_documents: List[List[tuple]], documents_features: List[np.ndarray],
+                            dataset: Dataset, train_size, random_state):
+
+    # indices of every document
+    indices_of_docs = [i for i in range(len(preprocessed_documents))]
+
+    i_train, i_test = train_test_split(indices_of_docs, train_size=train_size, random_state=random_state)
+
+    prep_docs_train = [preprocessed_documents[i] for i in i_train]
+    prep_docs_test = [preprocessed_documents[i] for i in i_test]
+
+    doc_features_train = [documents_features[i] for i in i_train]
+    doc_features_test = [documents_features[i] for i in i_test]
+
+    author_counts_train = [dataset.segmentations[i].author_count for i in i_train]
+    author_counts_test = [dataset.segmentations[i].author_count for i in i_test]
+
+    documents_train = [dataset.documents[i] for i in i_train]
+    documents_test = [dataset.documents[i] for i in i_test]
+
+    return prep_docs_train, prep_docs_test, \
+           doc_features_train, doc_features_test, \
+           author_counts_train, author_counts_test, \
+           documents_train, documents_test
+
+

### 2017-05-19 software/inpladesys/models/misc/misc.py
Custom dataset splitter moved to misc.py.

@@ -1,6 +1,8 @@
 from inpladesys.datatypes import Segment, Segmentation
 from typing import List
 import numpy as np
+from inpladesys.datatypes.dataset import Dataset
+from sklearn.model_selection import train_test_split
 
 
 def generate_segmentation(preprocessed_documents: List[List[tuple]], documents_features: List[np.ndarray],
@@ -23,3 +25,29 @@ def generate_segmentation(preprocessed_documents: List[List[tuple]], documents_f
                                           max_repairable_error=60,
                                           document_length=len(documents[i])))
     return segmentations
+
+
+def custom_train_test_split(preprocessed_documents: List[List[tuple]], documents_features: List[np.ndarray],
+                            dataset: Dataset, train_size, random_state):
+
+    # indices of every document
+    indices_of_docs = [i for i in range(len(preprocessed_documents))]
+
+    i_train, i_test = train_test_split(indices_of_docs, train_size=train_size, random_state=random_state)
+
+    prep_docs_train = [preprocessed_documents[i] for i in i_train]
+    prep_docs_test = [preprocessed_documents[i] for i in i_test]
+
+    doc_features_train = [documents_features[i] for i in i_train]
+    doc_features_test = [documents_features[i] for i in i_test]
+
+    author_counts_train = [dataset.segmentations[i].author_count for i in i_train]
+    author_counts_test = [dataset.segmentations[i].author_count for i in i_test]
+
+    documents_train = [dataset.documents[i] for i in i_train]
+    documents_test = [dataset.documents[i] for i in i_test]
+
+    return prep_docs_train, prep_docs_test, \
+           doc_features_train, doc_features_test, \
+           author_counts_train, author_counts_test, \
+           documents_train, documents_test

### 2017-05-20 software/inpladesys/models/abstract_diarizer.py
Added cluster model selection, NOT TESTED yet.

@@ -3,6 +3,7 @@ from abc import abstractmethod
 from typing import List
 import numpy as np
 from inpladesys.datatypes import *
+from inpladesys.models.model_selection.abstract_model_selector import AbstractModelSelector
 
 
 class AbstractDiarizer(ABC):
@@ -10,7 +11,7 @@ class AbstractDiarizer(ABC):
     @abstractmethod
     def fit_predict(self, preprocessed_documents: List[List[tuple]],
                     documents_features: List[np.ndarray],
-                    dataset: Dataset) -> List[Segmentation]:
+                    dataset: Dataset, hyperparams=None) -> List[Segmentation]:
         """
         sklearn compatible fit_predict method. Override for model implementation.
         :param preprocessed_documents: List of lists of tuples. Each list of tuples represents
@@ -21,3 +22,7 @@ class AbstractDiarizer(ABC):
         :return: List of Segmentations obtained by the implemented model
         """
         raise NotImplementedError
+
+    @abstractmethod
+    def get_model_selector(self) -> AbstractModelSelector:
+        return None

### 2017-05-20 software/inpladesys/models/clustering/dbscan_diarizer.py

@@ -1,6 +1,8 @@
 from inpladesys.models.abstract_diarizer import AbstractDiarizer
 from inpladesys.models.misc.misc import generate_segmentation
 from sklearn.preprocessing import StandardScaler
+from inpladesys.models.model_selection.abstract_model_selector import AbstractModelSelector
+from inpladesys.models.model_selection.DBSCAN_model_selector import DBSCANModelSelector
 from typing import List
 import numpy as np
 from inpladesys.datatypes import *
@@ -12,7 +14,7 @@ import time
 class DBSCANDiarizer(AbstractDiarizer):
 
     def fit_predict(self, preprocessed_documents: List[List[tuple]], documents_features: List[np.ndarray],
-                    dataset: Dataset) -> List[Segmentation]:
+                    dataset: Dataset, hyperparams=None) -> List[Segmentation]:
 
         assert len(documents_features) == len(preprocessed_documents)
 
@@ -35,9 +37,9 @@ class DBSCANDiarizer(AbstractDiarizer):
             x_scaled = StandardScaler().fit_transform(doc_features)  #preprocessing.scale(doc_features, axis=0)
             # x_scaled = doc_features
 
-            diarizer = DBSCAN(eps=6.1,
-                              min_samples=5,
-                              metric='manhattan',
+            diarizer = DBSCAN(eps=hyperparams['eps'],
+                              min_samples=hyperparams['min_samples'],
+                              metric=hyperparams['metric'],
                               algorithm='auto',  # The algorithm to be used by the NearestNeighbors module to compute pointwise distances and find nearest neighbors.
                               leaf_size=30)  # Leaf size passed to BallTree or cKDTree.
 
@@ -46,10 +48,12 @@ class DBSCANDiarizer(AbstractDiarizer):
 
             estimated_n_clusters = len(set(labels)) - (1 if -1 in labels else 0)
 
+            # TODO what with this ?
             noisy = 0
-            for l_i in range(len(labels)):
-                if labels[l_i] == -1:
-                    labels[l_i] = 0  # TODO fix this !!!!
+            non_clustered_label = max(labels) + 1
+            for l in range(len(labels)):
+                if labels[l] == -1:
+                    labels[l] = non_clustered_label
                     noisy += 1
 
             print('Document', i+1, '/', len(documents_features), 'in', time.time()-start_time, 's',)
@@ -59,3 +63,11 @@ class DBSCANDiarizer(AbstractDiarizer):
 
[…]

### 2017-05-20 software/inpladesys/models/learning_pipeline_task_x.py

@@ -8,6 +8,7 @@ from inpladesys.evaluation import get_confusion_matrix
 from inpladesys.models.clustering.k_means_diarizer import KMeansDiarizer
 from inpladesys.models.clustering.hac_diarizer import AgglomerativeDiarizer
 from inpladesys.models.clustering.dbscan_diarizer import DBSCANDiarizer
+from inpladesys.models.misc.misc import custom_train_test_split
 
 
 class LearningPipeline:
@@ -29,7 +30,7 @@ class LearningPipeline:
         start_time = time.time()
 
         preprocessed_docs = []
-        dataset_size = 1 #self.dataset.size
+        dataset_size = self.dataset.size
 
         for i in range(dataset_size):
             document, segmentation = self.dataset[i]
@@ -48,9 +49,22 @@ class LearningPipeline:
 
         if True:
 
+            print('Selecting model...')
+            model_selector = self.model.get_model_selector()
+
+            prep_docs_train, prep_docs_test, \
+                doc_features_train, doc_features_test, \
+                author_counts_train, author_counts_test, \
+                dataset_train, dataset_test = custom_train_test_split(preprocessed_docs, documents_features, self.dataset,
+                                                                      train_size=0.1, random_state=7)
+
+            optimal_hyperparams = model_selector.select_model(prep_docs_train, doc_features_train,
+                                                              dataset_train.documents, dataset_train.segmentations)
+
             print('Running model..')
             # TODO is it better to use fit and _predict separately ??
-            pred_segmentations = self.model.fit_predict(preprocessed_docs, documents_features, self.dataset)
+            pred_segmentations = self.model.fit_predict(prep_docs_test, doc_features_test,
+                                                        dataset_test, optimal_hyperparams)
 
             # TODO postprocess model results
 
@@ -59,8 +73,8 @@ class LearningPipeline:
             results_1 = np.array([0, 0, 0], dtype=np.float64)
             results_2 = np.array([0, 0, 0], dtype=np.float64)
 
-            for i in range(dataset_size):
-                truth = self.dataset.segmentations[i]
+            for i in range(len(pred_segmentations)):
+                truth = dataset_test.segmentations[i]
                 pred = pred_segmentations[i]
 
                 scorer_1 = self.scorer_1(get_confusion_matrix(truth, pred))

### 2017-05-20 software/inpladesys/models/misc/misc.py

@@ -44,10 +44,13 @@ def custom_train_test_split(preprocessed_documents: List[List[tuple]], documents
     author_counts_train = [dataset.segmentations[i].author_count for i in i_train]
     author_counts_test = [dataset.segmentations[i].author_count for i in i_test]
 
-    documents_train = [dataset.documents[i] for i in i_train]
-    documents_test = [dataset.documents[i] for i in i_test]
+    dataset_train = Dataset([dataset.documents[i] for i in i_train],
+                            [dataset.segmentations[i] for i in i_train])
+
+    dataset_test = Dataset([dataset.documents[i] for i in i_test],
+                           [dataset.segmentations[i] for i in i_test])
 
     return prep_docs_train, prep_docs_test, \
-           doc_features_train, doc_features_test, \
-           author_counts_train, author_counts_test, \
-           documents_train, documents_test
+        doc_features_train, doc_features_test, \
+        author_counts_train, author_counts_test, \
+        dataset_train, dataset_test

### 2017-05-20 software/inpladesys/models/model_selection/DBSCAN_model_selector.py

@@ -1,0 +1,71 @@
+from inpladesys.models.model_selection.abstract_model_selector import AbstractModelSelector
+from inpladesys.models.misc.misc import generate_segmentation
+from sklearn.cluster import DBSCAN
+from inpladesys.evaluation import *
+
+import time
+
+class DBSCANModelSelector(AbstractModelSelector):
+
+    def select_optimal_hyperparams(self, preprocessed_documents, documents_features, documents,
+                                   true_segmentations, author_labels=None, author_counts=None):
+        x_scaled = []
+
+        for doc_features in documents_features:
+            x_scaled.append(self.scaler.fit_transform(doc_features))
+
+        #true_labels = train_set['']
+
+        results = []
+
+        start_time = time.time()
+        for metric in self.hyperparams['metric']:
+            for eps in self.hyperparams['eps']:
+                for min_samples in self.hyperparams['min_samples']:
+
+                    predicted_label_lists = []
+                    model = DBSCAN(eps=eps, min_samples=min_samples, metric=metric)
+
+                    for i in range(len(x_scaled)):
+                        x = x_scaled[i]
+                        labels = model.fit_predict(x)
+
+                        # TODO what with this ?
+                        non_clustered_label = max(labels) + 1
+                        for l in range(len(labels)):
+                            if labels[l] == -1:
+                                labels[l] = non_clustered_label
+
+                        predicted_label_lists.append(labels)
+
+                    predicted_segmentations = generate_segmentation(preprocessed_documents, documents_features,
+                                                         predicted_label_lists, documents)
+
+                    score = self.get_bcubed_f1(true_segmentations, predicted_segmentations)
+
+                    results.append({'eps': eps, 'min_samples': min_samples,
+                                    'metric': metric, 'score': score})
+
+        sorted_results = sorted(results, key=lambda r: r['score'], reverse=True)
+        print('The best hyperparams found:', sorted_results[0], 'in {} s.'.format(time.time()-start_time))
+
+    def get_bcubed_f1(self, true_segmentations, predicted_segmentations):
+        assert len(true_segmentations) == len(predicted_segmentations)
+        result = 0
+
+        for i in len(true_segmentations):
+            truth = true_segmentations[i]
+            pred = predicted_segmentations[i]
+            result += BCubedScorer(get_confusion_matrix(truth, pred)).f1_score()
+
+        return result / len(true_segmentations)
+
+
+
+
+
+
+
+
+
+

### 2017-05-20 software/inpladesys/models/model_selection/abstract_model_selector.py

@@ -1,0 +1,15 @@
+from abc import ABC
+from abc import abstractmethod
+
+class AbstractModelSelector(ABC):
+
+    def __init__(self, hyperparams, model=None, scorer=None, scaler=None):
+        self.model = model
+        self.hyperparams = hyperparams
+        self.scorer = scorer
+        self.scaler = scaler
+
+    @abstractmethod
+    def select_optimal_hyperparams(self, preprocessed_documents, documents_features, documents,
+                                   true_segmentations, author_labels=None, author_counts=None):
+        return None

### 2017-05-20 software/inpladesys/models/clustering/dbscan_diarizer.py
Finished initial model selection code for task c.

@@ -1,5 +1,5 @@
 from inpladesys.models.abstract_diarizer import AbstractDiarizer
-from inpladesys.models.misc.misc import generate_segmentation
+from inpladesys.models.misc.misc import generate_segmentation, find_cluster_for_noisy_samples
 from sklearn.preprocessing import StandardScaler
 from inpladesys.models.model_selection.abstract_model_selector import AbstractModelSelector
 from inpladesys.models.model_selection.DBSCAN_model_selector import DBSCANModelSelector
@@ -7,6 +7,7 @@ from typing import List
 import numpy as np
 from inpladesys.datatypes import *
 from sklearn import preprocessing
+from scipy.sparse import issparse
 from sklearn.cluster import DBSCAN
 import time
 
@@ -34,27 +35,19 @@ class DBSCANDiarizer(AbstractDiarizer):
             # lsa = make_pipeline(svd, normalizer)
             # x_scaled = lsa.fit_transform(doc_features)
 
-            x_scaled = StandardScaler().fit_transform(doc_features)  #preprocessing.scale(doc_features, axis=0)
+            x_scaled = StandardScaler(with_mean=not issparse(doc_features)).fit_transform(doc_features)  #preprocessing.scale(doc_features, axis=0)
             # x_scaled = doc_features
 
             diarizer = DBSCAN(eps=hyperparams['eps'],
                               min_samples=hyperparams['min_samples'],
                               metric=hyperparams['metric'],
-                              algorithm='auto',  # The algorithm to be used by the NearestNeighbors module to compute pointwise distances and find nearest neighbors.
-                              leaf_size=30)  # Leaf size passed to BallTree or cKDTree.
+                              algorithm='brute')  # The algorithm to be used by the NearestNeighbors module to compute pointwise distances and find nearest neighbors.
+
 
             labels = diarizer.fit_predict(x_scaled)
-            predicted_label_lists.append(labels)
-
             estimated_n_clusters = len(set(labels)) - (1 if -1 in labels else 0)
-
-            # TODO what with this ?
-            noisy = 0
-            non_clustered_label = max(labels) + 1
-            for l in range(len(labels)):
-                if labels[l] == -1:
-                    labels[l] = non_clustered_label
-                    noisy += 1
+            noisy = find_cluster_for_noisy_samples(labels)
+            predicted_label_lists.append(labels)
 
[…]

### 2017-05-20 software/inpladesys/models/learning_pipeline_task_x.py

@@ -9,6 +9,7 @@ from inpladesys.models.clustering.k_means_diarizer import KMeansDiarizer
 from inpladesys.models.clustering.hac_diarizer import AgglomerativeDiarizer
 from inpladesys.models.clustering.dbscan_diarizer import DBSCANDiarizer
 from inpladesys.models.misc.misc import custom_train_test_split
+from  inpladesys.util.cacher import Cacher
 
 
 class LearningPipeline:
@@ -22,30 +23,38 @@ class LearningPipeline:
         self.model = parameters['model']
         self.scorer_1 = parameters['scorer_class_1']
         self.scorer_2 = parameters['scorer_class_2']
+        self.cacher = parameters['cacher']
+
+        self.dataset_size = self.dataset.size
+
+    def extract_features(self):
+        @self.cacher('doc-features-prep-docs')
+        def extract(self):
+            print('Extracting features...')
+            start_time = time.time()
+
+            documents_features = []
+            preprocessed_docs = []
+
+            for i in range(self.dataset_size):
+                document, segmentation = self.dataset[i]
+                preprocessed_document = self.document_preprocessor.fit_transform(document)
+                self.basic_feature_extractor.fit(document, preprocessed_document)
+                document_features = self.basic_feature_extractor.transform(document, preprocessed_document,
+                                                                           self.context_size)
+                print('Document {}/{}: {}'.format(i + 1, self.dataset_size, document_features.shape))
+
+                # TODO postprocess features (transformations etc.)
+
+                documents_features.append(document_features)
+                preprocessed_docs.append(preprocessed_document)
+
+            print('Extraction time (s): ', time.time() - start_time)
+            return documents_features, preprocessed_docs
+        return extract(self)
 
     def do_chain(self):
-        documents_features = []
-
-        print('Extracting features...')
-        start_time = time.time()
-
-        preprocessed_docs = []
-        dataset_size = self.dataset.size
-
-        for i in range(dataset_size):
-            document, segmentation = self.dataset[i]
-            preprocessed_document = self.document_preprocessor.fit_transform(document)
-            self.basic_feature_extractor.fit(document, preprocessed_document)
-            document_features = self.basic_feature_extractor.transform(document, preprocessed_document,
-                                                                       self.context_size)
[…]

### 2017-05-20 software/inpladesys/models/misc/misc.py

@@ -2,6 +2,7 @@ from inpladesys.datatypes import Segment, Segmentation
 from typing import List
 import numpy as np
 from inpladesys.datatypes.dataset import Dataset
+from collections import Counter
 from sklearn.model_selection import train_test_split
 
 
@@ -54,3 +55,23 @@ def custom_train_test_split(preprocessed_documents: List[List[tuple]], documents
         doc_features_train, doc_features_test, \
         author_counts_train, author_counts_test, \
         dataset_train, dataset_test
+
+
+def find_cluster_for_noisy_samples(predicted_labels, context_size=10):
+    noisy = 0
+    len_ = len(predicted_labels)
+    for i in range(len_):
+        if predicted_labels[i] == -1:
+            noisy += 1
+            left_diff = i-context_size
+            left = left_diff if left_diff >= 0 else 0
+            right_diff = i+context_size
+            right = right_diff if right_diff < len_ else len_-1
+            counter = Counter(predicted_labels[left:right+1])
+            found, curr = 0, 0
+            while found == 0:
+                if counter.most_common()[curr][0] != -1:
+                    predicted_labels[i] = counter.most_common()[curr][0]
+                    found = 1
+                curr += 1
+    return noisy

### 2017-05-20 software/inpladesys/models/model_selection/DBSCAN_model_selector.py

@@ -1,28 +1,30 @@
 from inpladesys.models.model_selection.abstract_model_selector import AbstractModelSelector
-from inpladesys.models.misc.misc import generate_segmentation
+from inpladesys.models.misc.misc import generate_segmentation, find_cluster_for_noisy_samples
 from sklearn.cluster import DBSCAN
 from inpladesys.evaluation import *
-
+from scipy.sparse import issparse
 import time
+
 
 class DBSCANModelSelector(AbstractModelSelector):
 
     def select_optimal_hyperparams(self, preprocessed_documents, documents_features, documents,
                                    true_segmentations, author_labels=None, author_counts=None):
         x_scaled = []
-
         for doc_features in documents_features:
-            x_scaled.append(self.scaler.fit_transform(doc_features))
+            x_scaled.append(self.scaler(with_mean=not issparse(doc_features)).fit_transform(doc_features))
 
         #true_labels = train_set['']
 
         results = []
-
+        total_hyperparams = len(self.hyperparams['metric']) * len(self.hyperparams['eps']) * len(self.hyperparams['min_samples'])
+        current_comb = 1
         start_time = time.time()
         for metric in self.hyperparams['metric']:
             for eps in self.hyperparams['eps']:
                 for min_samples in self.hyperparams['min_samples']:
 
+                    print('Combination {}/{}'.format(current_comb, total_hyperparams))
                     predicted_label_lists = []
                     model = DBSCAN(eps=eps, min_samples=min_samples, metric=metric)
 
@@ -30,13 +32,11 @@ class DBSCANModelSelector(AbstractModelSelector):
                         x = x_scaled[i]
                         labels = model.fit_predict(x)
 
-                        # TODO what with this ?
-                        non_clustered_label = max(labels) + 1
-                        for l in range(len(labels)):
-                            if labels[l] == -1:
-                                labels[l] = non_clustered_label
+                        find_cluster_for_noisy_samples(labels)
 
                         predicted_label_lists.append(labels)
+
+                    current_comb += 1
 
                     predicted_segmentations = generate_segmentation(preprocessed_documents, documents_features,
                                                          predicted_label_lists, documents)
@@ -47,13 +47,15 @@ class DBSCANModelSelector(AbstractModelSelector):
                                     'metric': metric, 'score': score})
 
         sorted_results = sorted(results, key=lambda r: r['score'], reverse=True)
[…]

### 2017-05-24 software/inpladesys/models/abstract_diarizer.py
Update in diarizers.

@@ -26,5 +26,5 @@ class AbstractDiarizer(ABC):
     def get_model_selector(self) -> AbstractModelSelector:
         return None
 
-    def get_optimal_hyperparams(self):
+    def get_optimal_hyperparams(self, task=None):
         return None

### 2017-05-24 software/inpladesys/models/clustering/affinity_prop_diarizer.py

@@ -54,7 +54,7 @@ class AffinityPropDiarizer(AbstractDiarizer):
         }
         return AffinityPropModelSelector(hyperparams=hyperparams, scaler=StandardScaler)
 
-    def get_optimal_hyperparams(self):
+    def get_optimal_hyperparams(self, task=None):
         return {'damping': 0.97, 'preference': 28800}
 
 

### 2017-05-24 software/inpladesys/models/clustering/dbscan_diarizer.py

@@ -64,7 +64,7 @@ class DBSCANDiarizer(AbstractDiarizer):
         }
         return DBSCANModelSelector(hyperparams=hyperparams, scaler=StandardScaler)
 
-    def get_optimal_hyperparams(self):
+    def get_optimal_hyperparams(self, task=None):
         return {'eps': 0.23,
                 'min_samples': 64,
                 'metric': 'cosine'}

### 2017-05-24 software/inpladesys/models/clustering/hac_diarizer.py

@@ -48,15 +48,21 @@ class AgglomerativeDiarizer(AbstractDiarizer):
         return generate_segmentation(preprocessed_documents, documents_features,
                                      document_label_lists, dataset.documents, task=task)
 
-    def get_optimal_hyperparams(self):
-        return {
-            'affinity': 'cosine',
-            'linkage': 'average',
-        }
+    def get_optimal_hyperparams(self, task=None):
+        if task == 'a':
+            return {
+                'affinity': 'cosine',
+                'linkage': 'average',
+            }
+        if task == 'b':
+            return {
+                'affinity': 'euclidean',
+                'linkage': 'average'
+            }
 
     def get_model_selector(self) -> AbstractModelSelector:
         hyperparams = {
-            'affinity': ['euclidean', 'manhattan', 'cosine'],  #['euclidean', 'manhattan', 'cosine'], ['euclidean']
+            'affinity': ['euclidean', 'manhattan', 'cosine'],  # ['euclidean', 'manhattan', 'cosine'], ['euclidean']
             'linkage': ['complete', 'average']  # ['complete', 'average'] ['ward']
         }
         return AgglomerativeModelSelector(hyperparams, scaler=StandardScaler)

### 2017-05-24 software/inpladesys/models/learning_pipeline_task_x.py

@@ -65,60 +65,58 @@ class LearningPipeline:
     def do_chain(self):
         documents_features, preprocessed_docs = self.extract_features()
 
-        if True:
+        prep_docs_train, prep_docs_test, \
+            doc_features_train, doc_features_test, \
+            author_counts_train, author_counts_test, \
+            dataset_train, dataset_test = custom_train_test_split(preprocessed_docs, documents_features, self.dataset,
+                                                                  train_size=self.train_size, random_state=self.random_state)
 
-            prep_docs_train, prep_docs_test, \
-                doc_features_train, doc_features_test, \
-                author_counts_train, author_counts_test, \
-                dataset_train, dataset_test = custom_train_test_split(preprocessed_docs, documents_features, self.dataset,
-                                                                      train_size=self.train_size, random_state=self.random_state)
+        print('Train set size: {}'.format(len(doc_features_train)))
 
-            print('Train set size: {}'.format(len(doc_features_train)))
+        if self.select_model:
+            print('Selecting model...')
+            model_selector = self.model.get_model_selector()
+            optimal_hyperparams = model_selector.select_optimal_hyperparams(prep_docs_train,
+                                                                            doc_features_train,
+                                                                            dataset_train.documents,
+                                                                            dataset_train.segmentations,
+                                                                            author_counts=author_counts_train,
+                                                                            task=self.task)
+        else:
+            optimal_hyperparams = self.model.get_optimal_hyperparams(task=self.task)
 
-            if self.select_model:
-                print('Selecting model...')
-                model_selector = self.model.get_model_selector()
-                optimal_hyperparams = model_selector.select_optimal_hyperparams(prep_docs_train,
-                                                                                doc_features_train,
-                                                                                dataset_train.documents,
-                                                                                dataset_train.segmentations,
-                                                                                author_counts=author_counts_train,
-                                                                                task=self.task)
-            else:
-                optimal_hyperparams = self.model.get_optimal_hyperparams()
[…]

### 2017-05-24 software/inpladesys/models/misc/misc.py

@@ -5,7 +5,7 @@ from inpladesys.datatypes.dataset import Dataset
 from collections import Counter
 from sklearn.model_selection import train_test_split
 import time
-
+import scipy.stats as st
 
 def generate_segmentation(preprocessed_documents: List[List[tuple]], documents_features: List[np.ndarray],
                           document_label_lists, documents, task=None) -> List[Segmentation]:
@@ -107,3 +107,30 @@ def find_cluster_for_noisy_samples(predicted_labels, context_size=10):
                                 curr += 1
     # print('Noisy labels reclustered in {}'.format(time.time()-start))
     return noisy
+
+
+#  https://stackoverflow.com/questions/15033511/compute-a-confidence-interval-from-sample-data/34474255#34474255
+def perform_confidence_interval_test(samples: List, c_interval=0.95, p_normal_threshold=0.05):
+    n = len(samples)
+    if n >= 30:
+        sem = st.sem(samples)
+        mean = np.mean(samples)
+        interval = st.t.interval(c_interval, n-1, loc=mean, scale=sem)
+        print('Mean:', mean)
+        print('Standard error:', sem)
+        print('{}% confidence interval: {}'.format(c_interval*100, interval))
+    else:
+        #  https://docs.scipy.org/doc/scipy-0.19.0/reference/generated/scipy.stats.normaltest.html
+        #  https://stackoverflow.com/questions/12838993/scipy-normaltest-how-is-it-used
+        z, p_val = st.normaltest(samples, nan_policy='raise')
+        if p_val < p_normal_threshold:
+            print('A given sample is not from normal distribution: '
+                  'p_val = {} < threshold = {}'.format(p_val, p_normal_threshold))
+            print('The confidence intervals cannot be calculated.')
+        else:
+            sem = st.sem(samples)
+            mean = np.mean(samples)
+            interval = st.t.interval(c_interval, n - 1, loc=mean, scale=sem)
+            print('Mean:', mean)
+            print('Standard error:', sem)
+            print('{}% confidence interval: {}'.format(c_interval * 100, interval))

### 2017-05-24 software/inpladesys/models/learning_pipeline_task_x.py
Confidence intervals calculated. Final results file added.

@@ -12,7 +12,7 @@ from inpladesys.models.clustering.gmm_diarizer import GaussianMixtureDiarizer
 from inpladesys.models.clustering.mean_shift_diarizer import MeanShiftDiarizer
 from inpladesys.models.clustering.affinity_prop_diarizer import AffinityPropDiarizer
 from inpladesys.models.outlier_detection.isolation_forest_diarizer import IsolationForestDiarizer
-from inpladesys.models.misc.misc import custom_train_test_split
+from inpladesys.models.misc.misc import custom_train_test_split, perform_confidence_interval_test
 from inpladesys.util.cacher import Cacher
 from sklearn import preprocessing as prep
 
@@ -93,6 +93,9 @@ class LearningPipeline:
 
         # Evaluation
         print('Evaluating...')
+        test_samples_1 = []
+        test_samples_2 = []
+
         results_1 = np.array([0, 0, 0], dtype=np.float64)
         results_2 = np.array([0, 0, 0], dtype=np.float64)
         test_set_size = len(dataset_test)
@@ -104,17 +107,22 @@ class LearningPipeline:
 
             scorer_1 = self.scorer_1(truth, pred)
             results_1 += np.array([scorer_1.precision(), scorer_1.recall(), scorer_1.f1_score()])
+            test_samples_1.append(scorer_1.f1_score())
 
             if self.scorer_2 is not None:  # Task a
                 scorer_2 = self.scorer_2(truth, pred)
                 results_2 += np.array([scorer_2.precision(), scorer_2.recall(), scorer_2.f1_score()])
+                test_samples_2.append(scorer_2.f1_score())
 
         results_1 /= test_set_size
         print(self.scorer_1, ':', results_1)
+        perform_confidence_interval_test(test_samples_1, c_interval=0.95, p_normal_threshold=0.05)
 
         if self.scorer_2 is not None:
             results_2 /= test_set_size
             print(self.scorer_2, ':', results_2)
+            perform_confidence_interval_test(test_samples_2, c_interval=0.95, p_normal_threshold=0.05)
+
 
     # TODO write all necessary params to log file
 
@@ -129,7 +137,7 @@ if __name__ == "__main__":
     params = dict()
 
     # Change the task here
-    task = 'b'
+    task = 'c'
 
     if task == 'a':
         print("Loading dataset for task ", task, "...")
@@ -159,7 +167,7 @@ if __name__ == "__main__":
         params['scorer_class_1'] = BCubedScorer
[…]

### 2017-05-24 software/inpladesys/models/misc/misc.py

@@ -118,7 +118,7 @@ def perform_confidence_interval_test(samples: List, c_interval=0.95, p_normal_th
         interval = st.t.interval(c_interval, n-1, loc=mean, scale=sem)
         print('Mean:', mean)
         print('Standard error:', sem)
-        print('{}% confidence interval: {}'.format(c_interval*100, interval))
+        print('{}% confidence interval: {}\n'.format(c_interval*100, interval))
     else:
         #  https://docs.scipy.org/doc/scipy-0.19.0/reference/generated/scipy.stats.normaltest.html
         #  https://stackoverflow.com/questions/12838993/scipy-normaltest-how-is-it-used
@@ -133,4 +133,4 @@ def perform_confidence_interval_test(samples: List, c_interval=0.95, p_normal_th
             interval = st.t.interval(c_interval, n - 1, loc=mean, scale=sem)
             print('Mean:', mean)
             print('Standard error:', sem)
-            print('{}% confidence interval: {}'.format(c_interval * 100, interval))
+            print('{}% confidence interval: {}\n'.format(c_interval * 100, interval))

### 2017-05-25 software/inpladesys/models/learning_pipeline_task_x.py
Updated perform_confidence_interval_test function, cacher error fixed.

@@ -137,7 +137,7 @@ if __name__ == "__main__":
     params = dict()
 
     # Change the task here
-    task = 'c'
+    task = 'b'
 
     if task == 'a':
         print("Loading dataset for task ", task, "...")

### 2017-05-25 software/inpladesys/models/misc/misc.py

@@ -109,28 +109,19 @@ def find_cluster_for_noisy_samples(predicted_labels, context_size=10):
     return noisy
 
 
-#  https://stackoverflow.com/questions/15033511/compute-a-confidence-interval-from-sample-data/34474255#34474255
 def perform_confidence_interval_test(samples: List, c_interval=0.95, p_normal_threshold=0.05):
     n = len(samples)
-    if n >= 30:
+    #  https://docs.scipy.org/doc/scipy-0.19.0/reference/generated/scipy.stats.normaltest.html
+    #  https://stackoverflow.com/questions/12838993/scipy-normaltest-how-is-it-used
+    z, p_val = st.normaltest(samples, nan_policy='raise')
+    if p_val < p_normal_threshold:
+        print('A given sample is not from normal distribution: '
+              'p_val = {} < threshold = {}'.format(p_val, p_normal_threshold))
+        print('The confidence intervals cannot be calculated.')
+    else:
         sem = st.sem(samples)
         mean = np.mean(samples)
-        interval = st.t.interval(c_interval, n-1, loc=mean, scale=sem)
+        interval = st.t.interval(c_interval, n-1, loc=mean, scale=sem)  #  https://stackoverflow.com/questions/15033511/compute-a-confidence-interval-from-sample-data/34474255#34474255
         print('Mean:', mean)
         print('Standard error:', sem)
-        print('{}% confidence interval: {}\n'.format(c_interval*100, interval))
-    else:
-        #  https://docs.scipy.org/doc/scipy-0.19.0/reference/generated/scipy.stats.normaltest.html
-        #  https://stackoverflow.com/questions/12838993/scipy-normaltest-how-is-it-used
-        z, p_val = st.normaltest(samples, nan_policy='raise')
-        if p_val < p_normal_threshold:
-            print('A given sample is not from normal distribution: '
-                  'p_val = {} < threshold = {}'.format(p_val, p_normal_threshold))
-            print('The confidence intervals cannot be calculated.')
-        else:
-            sem = st.sem(samples)
-            mean = np.mean(samples)
-            interval = st.t.interval(c_interval, n - 1, loc=mean, scale=sem)
-            print('Mean:', mean)
-            print('Standard error:', sem)
-            print('{}% confidence interval: {}\n'.format(c_interval * 100, interval))
+        print('{}% confidence interval: {}\n'.format(c_interval * 100, interval))

### 2017-05-25 software/inpladesys/util/cacher.py

@@ -84,7 +84,7 @@ if __name__ == "__main__":
     for j in range(10):
         for i in range(100):
             @cach("{}-of-100".format(i))  # memoizes files ".cache-test.p/*-of-100.p" where * in {0..99}
-            def one_of_100()
+            def one_of_100():
                 return (i, str(i))
             one_of_100()
     

### 2017-05-25 software/inpladesys/models/clustering/deoutliizer.py
Various things

@@ -1,0 +1,19 @@
+from sklearn.cluster import KMeans
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+class Deoutliizer():
+    def __init__(self, outlier_proportion):
+        self.outlier_proportion = outlier_proportion
+
+    def fit_predict(self, X):
+        X = X[:]
+        m = X.shape[0]
+        n = m * (1 - self.outlier_proportion)
+        keep = np.ones(n)
+        while m > n:
+            center = np.average(X, axis=0)
+            distances = np.sum((X - center) ** 2, axis=1)
+            keep[np.argmax(distances)] = 0
+            m -= 1

### 2017-05-25 software/inpladesys/models/feature_transformation/simple_grouprepel_feature_transformer.py

@@ -1,0 +1,203 @@
+import numpy as np
+import tensorflow as tf
+from inpladesys.models.feature_transformation.abstract_feature_transformer import \
+    AbstractFeatureTransformer
+from typing import List
+from inpladesys.datatypes import Dataset
+
+
+class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
+    def __init__(self,
+                 output_dimension,
+                 reinitialize_on_fit,
+                 input_dimension=None,
+                 nonlinear_layer_count=0,
+                 nonlinearity=tf.nn.tanh,
+                 learning_rate=1e-3,
+                 iteration_count=10000,
+                 regularization=1,
+                 verbose=False,
+                 random_state=None):
+        self.iteration_count = iteration_count
+        self.reinitialize_on_fit = reinitialize_on_fit
+        self.initialized = False
+
+        self.x, self.labels, self.y = [None] * 3
+        self.train_step_nd, self.loss_nd = [None] * 2
+
+        def initialize(input_dimension):
+            self.graph = tf.Graph()
+            with self.graph.as_default():
+                if random_state is not None:
+                    tf.set_random_seed(random_state)
+                self.sess = tf.Session()
+                self._build_graph(input_dimension, output_dimension,
+                                  nonlinear_layer_count, nonlinearity,
+                                  learning_rate, regularization)
+            self._build_graph_if_not_built = lambda x: None
+
+        self._build_graph_if_not_built = lambda input_dim: initialize(input_dim)
+
+        if input_dimension is not None:
+            initialize(input_dimension)
+
+        self.verbose = verbose
+
+    def fit(self, X: List[np.ndarray], G: List[np.ndarray]):
+        self._build_graph_if_not_built(X[0].shape[1])
+        assert (len(X) == len(G))
+        with self.graph.as_default():
+            if self.reinitialize_on_fit or not self.initialized:
+                self.sess.run(tf.global_variables_initializer())
+                self.initialized = True
+            ds = Dataset(X[:], G[:])
+            ravg_cost = 0.0;
+            a = 10
+            for i in range(self.iteration_count):
+                ds.shuffle()
+                costs = []
[…]

### 2017-05-25 paper/paper.tex
Improved Cacher, added dummy Cacher factory method, implemented predict in PipelineAuthorDiarizer
Added SimpleGroupRepelTransformer

@@
 
-\title{Template for writing TAR project papers}
+\title{TAR System Description Paper Template}
 
@@
 \abstract{ 
-This document provides the instructions on formatting the TAR project paper in \LaTeX{}.
-This is where you write the abstract (i.e., summary) of the work you carried out.
+This document provides the instructions on formatting the TAR system description paper in \LaTeX{}.
+This is where you write the abstract (i.e., summary) of the work you carried out within the project.
 The abstract is a paragraph of text ranging between 70 and 150 words.
@@
 
-This section is the introduction to your paper. Introduction should not be too elaborate, that is what other sections are for (the Introduction should definitely not spill over to the second page).
+This section is the introduction to your paper. Introduction should not be too elaborate, as that is what other sections are for (the Introduction should definitely not spill over to the second page).
 
@@
 
-In scientific papers, this section usually (but not necessarily) briefly describes the related research.
+In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.
 
@@
 
-This is the second subsection of the second section. Referencing the (sub)sections in text is performed as follows: ``in Section \ref{sec:first} we have shown \dots''.
+This is the second subsection of the second section. Referencing the (sub)sections in text is performed as follows: ``in Section~\ref{sec:first} we have shown \dots''.
 
@@
 
-The paper should have a minimum of 3 and a maximum of 5 pages, plus an additional page for references.
+The paper should have a minimum of 3 and a maximum of 4 pages, plus an additional page for references.
 
@@
 
-Table~\ref{tab:narrow-table} is an example of a narrow table. Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive.
+Table~\ref{tab:narrow-table} is an example of a narrow table.
+Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive.
+We recommend using \textit{booktabs} package for nicer tables.
 
@@
 1 & \text{if 
-    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|$}\\
+    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|,$}\\
 0 & \text{otherwise}

### 2017-05-25 software/inpladesys/models/clustering/deoutliizer.py

@@ -10,10 +10,11 @@ class Deoutliizer():
     def fit_predict(self, X):
         X = X[:]
         m = X.shape[0]
-        n = m * (1 - self.outlier_proportion)
-        keep = np.ones(n)
+        n = int(m * (1 - self.outlier_proportion))
+        keep = np.ones(m, dtype=np.int32)
         while m > n:
-            center = np.average(X, axis=0)
+            center = np.average(X, axis=0, weights=keep)
             distances = np.sum((X - center) ** 2, axis=1)
             keep[np.argmax(distances)] = 0
             m -= 1
+        return keep

### 2017-05-25 software/inpladesys/models/feature_transformation/__init__.py

@@ -2,3 +2,4 @@ from .abstract_feature_transformer import AbstractFeatureTransformer
 
 # Implementations
 from .grouprepel_feature_transformer import GroupRepelFeatureTransformer
+from .simple_grouprepel_feature_transformer import SimpleGroupRepelFeatureTransformer

### 2017-05-25 software/inpladesys/models/feature_transformation/grouprepel_feature_transformer.py

@@ -68,7 +68,8 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
                     ravg_cost = cavg_cost
                 else:
                     ravg_cost = (a - 1) / a * ravg_cost + 1 / a * cavg_cost
-                print("\r{}/{}, ~error: {:.3f} ({:.3f})".format(i + 1, self.iteration_count, ravg_cost, cavg_cost), end='')
+                print("\r{}/{}, ~error: {:.3f} ({:.3f})".format(i + 1, self.iteration_count, ravg_cost, cavg_cost),
+                      end='')
             print('')
 
     def transform(self, X: List[np.ndarray]) -> List[np.ndarray]:
@@ -76,6 +77,12 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
         return [self.sess.run([self.y], {self.x: x})[0] for x in X]
 
     def _build_graph(self, x_dim, y_dim, nonlinear_layer_count, nonlinearity, learning_rate, regularization):
+        def distance(a, b):
+            return (a - b) ** 2
+
+        #def cdistance(a, b):
+        #    return a*b
+
         def fc(in_size: int, out_size: int):
             w = tf.Variable(tf.truncated_normal([in_size, out_size], 0, 0.1))
             r_params.append(w)
@@ -88,16 +95,17 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
 
         def transform(x):
             nlc = nonlinear_layer_count
+            h = 1
             if nlc == 0:
                 x = tf.matmul(x, fc(x_dim, y_dim))
             else:
-                w = [fc(x_dim, 2 * x_dim)]
-                w += [fc(2 * x_dim, 2 * x_dim) for i in range(nlc - 1)]
-                b = [bias(2 * x_dim)]
-                b += [bias(2 * x_dim) for i in range(nlc - 1)]
+                w = [fc(x_dim, h * x_dim)]
+                w += [fc(h * x_dim, h * x_dim) for i in range(nlc - 1)]
+                b = [bias(h * x_dim)]
+                b += [bias(h * x_dim) for i in range(nlc - 1)]
                 for wi, bi in zip(w, b):
                     x = nonlinearity(tf.matmul(x, wi) + bi)
-                x = tf.matmul(x, fc(2 * x_dim, y_dim))
+                x = tf.matmul(x, fc(h * x_dim, y_dim))
             return x
 
[…]

### 2017-05-25 software/inpladesys/models/feature_transformation/simple_grouprepel_feature_transformer.py

@@ -6,16 +6,13 @@ from typing import List
 from inpladesys.datatypes import Dataset
 
 
-class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
+class SimpleGroupRepelFeatureTransformer(AbstractFeatureTransformer):
     def __init__(self,
-                 output_dimension,
                  reinitialize_on_fit,
                  input_dimension=None,
-                 nonlinear_layer_count=0,
                  nonlinearity=tf.nn.tanh,
                  learning_rate=1e-3,
                  iteration_count=10000,
-                 regularization=1,
                  verbose=False,
                  random_state=None):
         self.iteration_count = iteration_count
@@ -31,9 +28,7 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
                 if random_state is not None:
                     tf.set_random_seed(random_state)
                 self.sess = tf.Session()
-                self._build_graph(input_dimension, output_dimension,
-                                  nonlinear_layer_count, nonlinearity,
-                                  learning_rate, regularization)
+                self._build_graph(input_dimension, nonlinearity, learning_rate)
             self._build_graph_if_not_built = lambda x: None
 
         self._build_graph_if_not_built = lambda input_dim: initialize(input_dim)
@@ -68,38 +63,21 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
                     ravg_cost = cavg_cost
                 else:
                     ravg_cost = (a - 1) / a * ravg_cost + 1 / a * cavg_cost
-                print("\r{}/{}, ~error: {:.3f} ({:.3f})".format(i + 1, self.iteration_count, ravg_cost, cavg_cost), end='')
+                print("\r{}/{}, ~error: {:.3f} ({:.3f})".format(i + 1, self.iteration_count, ravg_cost, cavg_cost),
+                      end='')
             print('')
 
     def transform(self, X: List[np.ndarray]) -> List[np.ndarray]:
         self._build_graph_if_not_built(X[0].shape[1])
         return [self.sess.run([self.y], {self.x: x})[0] for x in X]
 
-    def _build_graph(self, x_dim, y_dim, nonlinear_layer_count, nonlinearity, learning_rate, regularization):
-        def fc(in_size: int, out_size: int):
[…]

### 2017-05-25 software/inpladesys/models/pipeline_author_diarizer.py

@@ -10,7 +10,8 @@ import numpy as np
 class PipelineAuthorDiarizer():
     def __init__(self, parameters: dict, cacher=None):
         self.preprocessor = TokenizerPreprocessor()
-        self.bfe = parameters['basic_feature_extractor']
+        self.bfextr = parameters['basic_feature_extractor']
+        self.bf_extender = parameters['basic_feature_extender']
         self.feature_transformer = parameters['feature_transformer']
         self.clusterer = parameters['clusterer']
         self.cacher = Cacher.dummy() if cacher is None else cacher
@@ -26,13 +27,13 @@ class PipelineAuthorDiarizer():
         def fit_bfe(documents):
             corpus = "\n\n".join(doc for doc in documents)
             corpus_tokens = self.preprocessor.fit_transform(corpus)
-            self.bfe.fit(corpus, corpus_tokens)
-            return self.bfe
+            self.bfextr.fit(corpus, corpus_tokens)
+            return self.bfextr
 
         documents, segmentations = dataset.documents, dataset.segmentations
 
         print("(1/4) Training basic feature extractor...")
-        self.bfe = fit_bfe(documents)  # TODO: load bfe in predict if not loaded
+        self.bfextr = fit_bfe(documents)  # TODO: load bfe in predict if not loaded
 
         print("(2/4) Preprocessing training data: extracting tokens and basic features...")
         bydoc_tokens, bydoc_features = self._preprocess_documents(documents)
@@ -58,11 +59,17 @@ class PipelineAuthorDiarizer():
                 plt.scatter(h[:, 0], h[:, 1], c=y1[0])
                 plt.pause(0.05)
 
-    def predict(self, documents):
+    def predict(self, documents, author_counts=None):
         assert (len(documents) > 0)
         bydoc_tokens, bydoc_features = self._preprocess_documents(documents)
         bydoc_transformed_features = self.feature_transformer.transform(bydoc_features)
-        bydoc_labels_h = [self.clusterer.fit_predict(tf) for tf in bydoc_transformed_features]
+        bydoc_labels_h = []
+        if author_counts is None:
+            bydoc_labels_h = [self.clusterer.fit_predict(tf) for tf in bydoc_transformed_features]
+        else:
+            for i, tf in enumerate(bydoc_transformed_features):
+                bydoc_labels_h.append(self.clusterer.fit_predict(tf, cluster_count=author_counts[i]))
+
[…]

### 2017-05-25 software/test-grouprepel.py

@@ -26,8 +26,7 @@ vector_arrays = [
 label_arrays = [np.array([0, 0, 0, 1, 1, 2, 2, 3, 3, 3, 4, 4, 4]),
                 np.array([0, 1, 1, 1])]
 
-grft = GroupRepelFeatureTransformer(
-    3, 2, nonlinear_layer_count=1, iteration_count=50, reinitialize_on_fit=False)
+grft = GroupRepelFeatureTransformer(2, reinitialize_on_fit=False, nonlinear_layer_count=0, iteration_count=50)
 
 import matplotlib.pyplot as plt
 

### 2017-05-25 software/test-pipeline.py

@@ -4,6 +4,7 @@ from inpladesys.models.basic_feature_extraction.basic_feature_extractor import B
 from inpladesys.models.feature_transformation import GroupRepelFeatureTransformer
 from inpladesys.models.pipeline_author_diarizer import PipelineAuthorDiarizer
 from inpladesys.models.clustering.auto_k_means import AutoKMeans
+from inpladesys.models.clustering.deoutliizer import Deoutliizer
 from inpladesys.util.cacher import Cacher
 from sklearn.cluster import KMeans
 from inpladesys.evaluation import get_confusion_matrix, BCubedScorer, MicroScorer, MacroScorer
@@ -16,28 +17,40 @@ dataset_dirs = [
 ]
 
 
-def evaluate(params: dict, dataset_index: int):
-    # features_file_name = 'inpladesys/models/basic_feature_extraction/features_files/char-n-grams.json'
+def evaluate(params: dict, dataset_index: int, cache_dir=None):
     features_file_name = 'inpladesys/models/basic_feature_extraction/features_files/cng-sw-bow.json'
     random_state = 0xBeeFeed
     pl_params = dict()
     pl_params['basic_feature_extractor'] = BasicFeatureExtractor(
         features_file_name=features_file_name,
         context_size=params['context_size'])
-    pl_params['feature_transformer'] = GroupRepelFeatureTransformer(
+    from inpladesys.models.feature_transformation import SimpleGroupRepelFeatureTransformer
+    pl_params['feature_transformer'] = SimpleGroupRepelFeatureTransformer(
+        reinitialize_on_fit=False,
+        iteration_count=params['gr-iteration_count'],
+        learning_rate=8e-4,
+        random_state=random_state)
+    """pl_params['feature_transformer'] = GroupRepelFeatureTransformer(
         output_dimension=params['gr_output_dimension'],
         reinitialize_on_fit=False,
         nonlinear_layer_count=params['gr-nonlinear_layer_count'],
         iteration_count=params['gr-iteration_count'],
         learning_rate=8e-4,
-        random_state=random_state)  # params['model'] = KMeansDiarizer()
[…]

### 2017-05-26 paper/paper.tex
no message

@@
 
-This section is the introduction to your paper. Introduction should not be too elaborate, as that is what other sections are for (the Introduction should definitely not spill over to the second page).
+Author diarization is the problem of segmenting text within a document into classes each corresponding to an author, i.e.
+assignment of each part of a text to an author.
+The analyzed document can be a result of collaborative work or plagiarism by a single author.
+The problem is in more detail described here.
+The problem can be divided into 3 subproblems:
+% reference
+% authorship analysis, 
+% intrinsic plagiarism detection, author diarization
+% PAN 2016 author diarization task
+% dataset
 
-This is the second paragraph of the introduction.
-In \LaTeX , paragraphs are separated by inserting an empty line in between them.
-Avoid very large paragraphs (larger than half of the page height), but also avoid tiny paragraphs (e.g., one-sentence paragraphs).
+\section{Related work}
 
-\section{Second section}
+% Kuznetsov, Sittar, Brooke
 
-In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.
+\section{The proposed approaches}
+clustering, sliding window
+pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
 
-\subsection{First subsection}
-\label{sec:first}
+clustering metric
 
-This is a subsection of the second section.
+\begin{itemize}
+\item a
+\item b
+\end{itemize}
 
-\subsection{Second subsection}
+features
 
-This is the second subsection of the second section. Referencing the (sub)sections in text is performed as follows: ``in Section~\ref{sec:first} we have shown \dots''.
+differences: fixed features + transformation vs document-dependent features
 
-\subsubsection{Sub-subsection example}
+\section{Experimantal results}
 
-This is a sub-subsection. If possible, it is better to avoid sub-subsections.
+1
+baselines
 
-\section{Extent of the paper}
+\subsection{Intrinsic plagiarism detection}
 
-The paper should have a minimum of 3 and a maximum of 4 pages, plus an additional page for references.
+setup
 
-\section{Figures and tables}
+\subsection{Author diarization with known numbers of authors}
 
-\subsection{Figures}
+setup
 
-Here is an example on how to include figures in the paper.
-Figures are included in \LaTeX{} code immediately \textit{after} the text in which these figures are referenced.
-Allow \LaTeX{} to place the figure where it believes is best (usually on top of the page of at the position where you would not place the figure).
-Figures are referenced as follows: ``Figure~\ref{fig:figure1} shows \dots''.
-Use tilde (\verb.~.) to prevent separation between the word ``Figure'' and its enumeration.
+\subsection{Author diarization with unknown numbers of authors}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=\columnwidth]{drawing.pdf}
-\caption{This is the figure caption.
-Full sentences should be followed with a dot.
-The caption should be placed \textit{below} the figure.
-Caption should be short; details should be explained in the text.}
-\label{fig:figure1}
-\end{center}
-\end{figure}
-
-\subsection{Tables}
-
-There are two types of tables: narrow tables that fit into one column and a wide table that spreads over both columns.
-
-\subsubsection{Narrow tables}
-
-Table~\ref{tab:narrow-table} is an example of a narrow table.
-Do not use vertical lines in tables -- vertical tables have no effect and they make tables visually less attractive.
-We recommend using \textit{booktabs} package for nicer tables.
-
-\begin{table}
-\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
-\label{tab:narrow-table}
-\begin{center}
-\begin{tabular}{ll}
-\toprule
-Heading1 & Heading2 \\
-\midrule
-One & First row text \\
-Two   & Second row text \\
-Three   & Third row text \\
-      & Fourth row text \\
-\bottomrule
-\end{tabular}
-\end{center}
-\end{table}
-
-\subsection{Wide tables}
-
-Table~\ref{tab:wide-table} is an example of a wide table that spreads across both columns. The same can be done for wide figures that should spread across the whole width of the page.
-
-\begin{table*}
-\caption{Wide-table caption}
-\label{tab:wide-table}
-\begin{center}
-\begin{tabular}{llr}
-\toprule
-Heading1 & Heading2 & Heading3\\
-\midrule
-A & A very long text, longer that the width of a single column & $128$\\
-B & A very long text, longer that the width of a single column & $3123$\\
-C & A very long text, longer that the width of a single column & $-32$\\
-\bottomrule
-\end{tabular}
-\end{center}
-\end{table*}
-
-\section{Math expressions and formulas}
-
-Math expressions and formulas that appear within the sentence should be written inside the so-called \emph{inline} math environment: $2+3$, $\sqrt{16}$, $h(x)=\mathbf{1}(\theta_1 x_1 + \theta_0>0)$.
-Larger expressions and formulas (e.g., equations) should be written in the so-called \emph{displayed} math environment:
-
-\[
-b^{(i)}_k = \begin{cases}
-1 & \text{if 
-    $k = \text{argmin}_j \| \mathbf{x}^{(i)} - \mathbf{\mu}_j \|,$}\\
-0 & \text{otherwise}
-\end{cases}
-\]
-
-Math expressions which you reference in the text should be written inside the \textit{equation} environment:
-
-\begin{equation}\label{eq:kmeans-error}
-J = \sum_{i=1}^N \sum_{k=1}^K 
-b^{(i)}_k \| \mathbf{x}^{(i)} - \mathbf{\mu}_k \|^2
-\end{equation}
-
-Now you can reference equation \eqref{eq:kmeans-error}. If the paragraph continues right after the formula
-
-\begin{equation}
-f(x) = x^2 + \varepsilon
-\end{equation}
-
-\noindent like this one does, use the command \emph{noindent} after the equation to remove the indentation of the row.
-
-Multi-letter words in the math environment should be written inside the command \emph{mathit}, otherwise \LaTeX{} will insert spacing between the letters to denote the multiplication of values denoted by symbols.
-For example, compare
-$\mathit{Consistent}(h,\mathcal{D})$ and\\
-$Consistent(h,\mathcal{D})$.
-
-If you need a math symbol, but you don't know the corresponding \LaTeX{} command that generates it, try
-\emph{Detexify}.\footnote{\texttt{http://detexify.kirelabs.org/}}
-
-\section{Referencing literature}
-
-References to other publications should be written in brackets with the last name of the first author and the year of publication, e.g., \citep{chomsky-73}.
-Multiple references are written in sequence, one after another, separated by semicolon and without whitespaces in between, e.g., \citep{chomsky-73,chave-64,feigl-58}.
-References are typically written at the end of the sentence and necessarily before the sentence punctuation.
-
-If the publication is authored by more than one author, only the name of the first author is written, after which abbreviation \emph{et al.}, meaning \emph{et alia}, i.e.,~and others is written as in \citep{johnson-etc}.
-If the publication is authored by only two authors, then the last names of both authors are written \citep{johnson-howells}.
-
-If the name of the author is incorporated into the text of the sentence, it should not be in the brackets (only the year should be there). E.g.,~``\citet{chomsky-73}
-suggested that \dots''. The difference is whether you reference the publication or the author who wrote it.
-
-The list of all literature references is given alphabetically at the end of the paper. The form of the reference depends on the type of the bibliographic unit: conference papers,
-\citep{chave-64}, books \citep{butcher-81}, journal articles
-\citep{howells-51}, doctoral dissertations \citep{croft-78}, and book chapters \citep{feigl-58}.
-
-All of this is automatically produced when using BibTeX. Insert all the BibTeX entries into the file \texttt{tar2016.bib}, and then reference them via their symbolic names.
+setup
 

### 2017-05-26 software/inpladesys/models/feature_transformation/simple_grouprepel_feature_transformer.py

@@ -76,8 +76,8 @@ class SimpleGroupRepelFeatureTransformer(AbstractFeatureTransformer):
 
         def transform(x):
             w = tf.Variable(tf.truncated_normal([x_dim], 0, 0.1))
-            # b = tf.Variable(tf.truncated_normal([x_dim], 0, 0.1))
-            return x * w
+            b = tf.Variable(tf.truncated_normal([x_dim], 0, 0.1))
+            return x * w+b
 
         def fori(istart, istop, body, body_var, shape_invar=None):
             if type(istart) == int:

### 2017-05-26 software/inpladesys/models/pipeline_author_diarizer.py

@@ -1,3 +1,5 @@
+from numpy.ctypeslib import prep_array
+
 from inpladesys.datatypes import Document, Segment, Segmentation, Dataset
 from .abstract_author_diarizer import AbstractAuthorDiarizer
 from inpladesys.models.misc import generate_segmentation, fix_segmentation_labels_for_plagiarism_detection
@@ -42,6 +44,8 @@ class PipelineAuthorDiarizer():
         bydoc_labels = get_bydoc_labels(bydoc_tokens, segmentations)
 
         print("(4/4) Training feature transformer...")
+        bydoc_features = [preprocessing.scale(f) for f in bydoc_features]
+        #bydoc_features=preprocessing.scale(np.array(bydoc_features))
         x, y = bydoc_features[:], bydoc_labels[:]
         if True:
             self.feature_transformer.fit(x, y)
@@ -88,9 +92,10 @@ class PipelineAuthorDiarizer():
             def prepr():
                 return self._preprocess_document(doc)
 
-            tokens, tokens_features = prepr()
+            tokens, token_features = prepr()
+            token_features = np.array(token_features)
             bydoc_tokens.append(tokens)
-            bydoc_token_features.append(tokens_features)
+            bydoc_token_features.append(token_features)
             print("\r{}/{}".format(i + 1, len(documents)), end='')
         print('')
         return bydoc_tokens, bydoc_token_features
@@ -99,4 +104,4 @@ class PipelineAuthorDiarizer():
         tokens = self.preprocessor.fit_transform(document)
         features = self.bfextr.transform(document, tokens)
         features = [np.concatenate((f, f ** 2), axis=0) for f in features]  # move scaling to corpus level
-        return tokens, preprocessing.scale(features)  # scaling beneficial
+        return tokens, features #preprocessing.scale(features)  # scaling beneficial

### 2017-05-26 software/test-pipeline.py

@@ -9,6 +9,7 @@ from inpladesys.util.cacher import Cacher
 from sklearn.cluster import KMeans
 from inpladesys.evaluation import get_confusion_matrix, BCubedScorer, MicroScorer, MacroScorer
 import numpy as np
+from inpladesys.models.misc import perform_confidence_interval_test
 
 dataset_dirs = [
     "../data/pan16-author-diarization-training-dataset-problem-a-2016-02-16",
@@ -25,18 +26,19 @@ def evaluate(params: dict, dataset_index: int, cache_dir=None):
         features_file_name=features_file_name,
         context_size=params['context_size'])
     from inpladesys.models.feature_transformation import SimpleGroupRepelFeatureTransformer
-    pl_params['feature_transformer'] = SimpleGroupRepelFeatureTransformer(
+    """pl_params['feature_transformer'] = SimpleGroupRepelFeatureTransformer(
         reinitialize_on_fit=False,
         iteration_count=params['gr-iteration_count'],
-        learning_rate=8e-4,
+        learning_rate=5e-4,
         random_state=random_state)
-    """pl_params['feature_transformer'] = GroupRepelFeatureTransformer(
+    """
+    pl_params['feature_transformer'] = GroupRepelFeatureTransformer(
         output_dimension=params['gr_output_dimension'],
         reinitialize_on_fit=False,
         nonlinear_layer_count=params['gr-nonlinear_layer_count'],
         iteration_count=params['gr-iteration_count'],
-        learning_rate=8e-4,
-        random_state=random_state)"""
+        learning_rate=5e-4,
+        random_state=random_state)
     pl_params['clusterer'] = AutoKMeans(min_clusters=2, max_clusters=2)
     #pl_params['clusterer'] = Deoutliizer(0.3)
     if params['basic_feature_extender'] == 'f**2':
@@ -74,7 +76,9 @@ def evaluate(params: dict, dataset_index: int, cache_dir=None):
 
     scorer_factories = [MicroScorer, MacroScorer, BCubedScorer] if dataset_index == 0 else [BCubedScorer]
     for sf in scorer_factories:
-        scores = np.stack([get_scores(sf, y, h) for y, h in zip(ys, hs)], axis=0)
+        score_list = [get_scores(sf, y, h) for y, h in zip(ys, hs)]
+        #print(perform_confidence_interval_test(score_list))
[…]

### 2017-05-26 software/inpladesys/models/learning_pipeline_task_x.py
Minor changes.

@@ -137,7 +137,7 @@ if __name__ == "__main__":
     params = dict()
 
     # Change the task here
-    task = 'b'
+    task = 'a'
 
     if task == 'a':
         print("Loading dataset for task ", task, "...")
@@ -168,7 +168,7 @@ if __name__ == "__main__":
         params['scorer_class_2'] = None
         params['cacher'] = Cacher(dir='.cache-task-b')
         params['select-model'] = False
-        params['train_size'] = 0.5  # 0 za agg iz a
+        params['train_size'] = 0.5  # 0 za agg iz a, 0.5 za hip
         params['random_state'] = 8
 
     elif task == 'c':

### 2017-05-27 paper/paper.tex
tar2017.bib added.

@@
 \section{Introduction}
-
+What is the problem ? 
+\citep{stein-2011}
 Author diarization is the problem of segmenting text within a document into classes each corresponding to an author, i.e.
@@
 The problem can be divided into 3 subproblems:
+
 % reference
@@
 
+\begin{table}
+	\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
+	\label{tab:narrow-table}
+	\begin{center}
+		\begin{tabular}{cccc}
+			\toprule
+			Model & $R$ & $P$ & $F_1$\\
+			\midrule
+			Dummy & 0 & 1 & 2 \\
+			One & 0 & 1 & 2 \\
+			One & 0 & 1 & 2 \\
+			\midrule
+			One & 0 & 1 & 2 \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+\end{table}
+
+Mention cofidences.
+
 \subsection{Intrinsic plagiarism detection}
@@
 setup
+results
 
@@
 \bibliographystyle{tar2016}
-\bibliography{tar2016}
+\bibliography{tar2017}
 

### 2017-05-28 paper/paper.tex
Init version of paper introduction finished.

@@
 \usepackage{amssymb}
+\usepackage{makecell}
 
@@
 
-\name{Author1, Author2, Author3}
+\name{Ivan Grubišić, Milan Pavlović, Author3}
 
@@
 The abstract is a paragraph of text ranging between 70 and 150 words.
+This document provides the instructions on formatting the TAR system description paper in \LaTeX{}.
+This is where you write the abstract (i.e., summary) of the work you carried out within the project.
+The abstract is a paragraph of text ranging between 70 and 150 words.
 }
@@
 \section{Introduction}
-What is the problem ? 
-\citep{stein-2011}
-Author diarization is the problem of segmenting text within a document into classes each corresponding to an author, i.e.
-assignment of each part of a text to an author.
-The analyzed document can be a result of collaborative work or plagiarism by a single author.
-The problem is in more detail described here.
-The problem can be divided into 3 subproblems:
+The simplest variant of authorship attribution problem consists of determinig a true author for a given document of unknown authorship, where decision is based on a set of other documents whose authors are known \citep{stein-2011,ding-2016}.
+Such descirbed problem can be tackeled with supervised machine learning techniques as a single-label multiclass text classification problem, where one class represents one author \citep{stamatatos-2009a}.
+
+Authorship attribution problem is also known as authorship identification and it is a part of authorship analysis \citep{stamatatos-2009a,ding-2016}.
+Authorship analysis is a field of stylometry which studies information about the authorship of a document, based on features derived from that document \citep{layton-2013}.
+
+In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\texttt{http://pan.webis.de/clef16/pan16-web/author-identification.html}}.
+The aim of this task is to decompose a document into its authorial parts, i.e.
+to split a text into segments and assign an author to every segment \citep{koppel-2011,aldebei-2015}.
+This is one of the unsupervised variants of authorship attribution problem since text samples of known authorship are not available \citep{rosso-2016}.
+As we will describe, in two out of three subtasks of this task only a correct number of authors for a given document is known.
+
+\citet{rosso-2016} divided PAN 2016 author diarization task into three subtasks.
+First subtask is traditionally called intrinsic plagiarism detection.
+The goal of this task is to find plagiariarized parts of a document in which 70\% of text is written by main author and the rest by one or more other authors.
+The term \textit{intrinsic} means that a decision whether plagiarized parts exist or not has to be made only by analysing a given document, without any comparisons with external sources.
+In the rest of the paper we refer to this subtask as a task \textit{a}.
+
+\begin{table}
+	\caption{Basic characteristics of train datasets}
+	\label{table-1}
+	\begin{center}
+		\begin{tabular}{cccc}
+			\toprule
+			Task & \thead{Number of \\ documents} & \thead{Average \\ length (in tokens)} & \thead{(min, max)\\authors} \\
+			\midrule
+			Task \textit{a} & 71 & 1679 & (2, 2)\\
+			Task \textit{b} & 55 & 3767 & (2, 10)\\
+			Task \textit{c} & 54 & 3298 & (2, 10)\\
+		\end{tabular}
+	\end{center}
+\end{table}
+
+Other two subtasks are more related to the general task of author diarization.
+In the second subtask we need to segment a given document and group identified segments by author.
+In the rest of the paper we refer to the second subtask as a task \textit{b}.
+Third subtask differs from the second one in the fact that exact number of authors is unkown.
+In the rest of the paper we refer to the third subtask as a task \textit{c}.
+
+For all tasks a different training datasets are publicly available [footnote].
+\citet{rosso-2016} explain that they are collections of various documents which are part of Webis-TRC-12 dataset \citep{potthast-2013}.
+Every document in that dataset is constructed from texts of various search results (i.e.
+authors) for one of the 150 topics in total.
+By varying different parameters such as the number and proportion of the authors, places in a document where an author switch occurs (between words, sentences or paragraphs), three training and test datasets were generated \citep{rosso-2016}.
+Test datasets are currently not publicly available and we could not use them for evaluation of our approach.
+Some basic characterisics of training datasets are shown in table \ref{table-1}.
+
+- writing style, stylistic segmentation, multi-authored work, plagiarism
+- a, b, c
 

### 2017-05-28 software/inpladesys/models/learning_pipeline_task_x.py

@@ -64,6 +64,14 @@ class LearningPipeline:
 
     def do_chain(self):
         documents_features, preprocessed_docs = self.extract_features()
+        avg = 0
+        aut = []
+        for i in range(len(preprocessed_docs)):
+            avg += documents_features[i].shape[0]
+            aut.append(self.dataset.segmentations[i].author_count)
+        avg /= len(preprocessed_docs)
+        print('avg len:', avg)
+        print(min(aut), max(aut))
 
         prep_docs_train, prep_docs_test, \
             doc_features_train, doc_features_test, \
@@ -137,7 +145,7 @@ if __name__ == "__main__":
     params = dict()
 
     # Change the task here
-    task = 'a'
+    task = 'c'
 
     if task == 'a':
         print("Loading dataset for task ", task, "...")

### 2017-05-28 software/inpladesys/models/clustering/old_auto_k_means.py
Improved AutoKMeans

@@ -1,0 +1,34 @@
+from sklearn.cluster import KMeans
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+class AutoKMeans():
+    def __init__(self, min_clusters=1, max_clusters=8, tol_sel=1e-3, tol=1e-4,
+                 n_init_sel=5, n_init=10, max_iter_sel=100, max_iter=300,
+                 verbose=False):
+        self.min_clusters, self.max_clusters = min_clusters, max_clusters
+        self.tol_sel, self.tol = tol_sel, tol
+        self.n_init_sel, self.n_init = n_init_sel, n_init
+        self.max_iter_sel, self.max_iter = max_iter_sel, max_iter
+        self.verbose = verbose
+        self.k_ = 1
+
+    def fit_predict(self, X, cluster_count=None):
+        if cluster_count is not None:
+            km = KMeans(n_clusters=cluster_count).fit(X)
+            return km.labels_
+        ks = np.arange(self.min_clusters, self.max_clusters + 1)
+        js = np.zeros(len(ks))
+        labs = []
+        for i in range(len(ks)):
+            km = KMeans(n_clusters=ks[i]).fit(X)
+            js[i] = km.inertia_
+            labs += [km.labels_]
+        jsks = js * ks
+        #print(jsks)
+        #plt.plot(ks, js)
+        self.k_ = np.argmin(jsks)
+        print(self.k_)
+        if self.verbose: print("The best k is " + str(self.k_) + ".")
+        return labs[self.k_]

### 2017-05-28 software/inpladesys/models/feature_transformation/grouprepel_feature_transformer.py

@@ -89,15 +89,17 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
             return w
 
         def bias(size: int):
-            return tf.Variable(tf.truncated_normal([size], 0, 0.1))
+            return tf.Variable(tf.truncated_normal([size], 0, 0.0))
 
         r_params = []
 
         def transform(x):
             nlc = nonlinear_layer_count
             h = 1
+            w=[]
             if nlc == 0:
-                x = tf.matmul(x, fc(x_dim, y_dim))
+                w = [fc(x_dim, y_dim)]
+                x = tf.matmul(x, w[0])
             else:
                 w = [fc(x_dim, h * x_dim)]
                 w += [fc(h * x_dim, h * x_dim) for i in range(nlc - 1)]
@@ -106,13 +108,15 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
                 for wi, bi in zip(w, b):
                     x = nonlinearity(tf.matmul(x, wi) + bi)
                 x = tf.matmul(x, fc(h * x_dim, y_dim))
+            nonlocal r_params
+            r_params = w
             return x
 
         def fori(istart, istop, body, body_var, shape_invar=None):
-            if type(istart) == int:
-                istart = tf.constant(istart)
-            if type(istop) == int:
-                imax = tf.constant(istop)
+            #if type(istart) == int:
+            #    istart = tf.constant(istart)
+            #if type(istop) == int:
+            #    istop = tf.constant(istop)
             if shape_invar is not None:
                 shape_invar = [tf.TensorShape([]), shape_invar]
             return tf.while_loop(
@@ -162,12 +166,12 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
 
         group_loss = get_group_loss(y, labels, centroids, centroid_count)
         centroid_loss = get_centroid_loss(centroids, centroid_count)
-        # r_loss = sum(tf.reduce_mean(p ** 2) for p in r_params)
+        r_loss = sum(tf.reduce_mean(p ** 2) for p in r_params)
 
         a = 0.5
         group_loss = a * group_loss + 1e-6
         centroid_loss = (1 - a) * centroid_loss + 1e-6
-        loss = centroid_loss + group_loss  # + r_loss  # +
+        loss = centroid_loss + group_loss #+ 0.5*r_loss  # +
[…]

### 2017-05-29 paper/paper.tex
Second chapter finished.

@@
 
-\title{TAR System Description Paper Template}
+\title{Token-level author diarization using clustering of stylistic contexts}
 
@@
 Unska 3, 10000 Zagreb, Croatia\\ 
-\texttt{autor1@xxx.hr}, \texttt{\{autor2,autor3\}@zz.com}\\
+\texttt{\{ivan.grubisic, milan.pavlovic, \}@fer.hr}\\
 }
@@
 \section{Introduction}
-The simplest variant of authorship attribution problem consists of determinig a true author for a given document of unknown authorship, where decision is based on a set of other documents whose authors are known \citep{stein-2011,ding-2016}.
+In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\texttt{https://tinyurl.com/y9m4zntm}}.
+The aim of this task is to decompose a document into its authorial parts, i.e.
+to split a text into segments and assign an author to every segment \citep{koppel-2011,aldebei-2015}.
+This is one of the unsupervised variants of a well known authorship attribution problem since text samples of known authorship are not available \citep{rosso-2016}.
+As we will describe, in two out of three subtasks of this task only a correct number of authors for a given document is known.
+
+The simplest variant of authorship attribution problem is about finding the most likely author for a given document, from a set of candidate authors whose authentic writing examples are available \citep{stamatatos-2009a,stein-2011,ding-2016}.
 Such descirbed problem can be tackeled with supervised machine learning techniques as a single-label multiclass text classification problem, where one class represents one author \citep{stamatatos-2009a}.
@@
 Authorship attribution problem is also known as authorship identification and it is a part of authorship analysis \citep{stamatatos-2009a,ding-2016}.
-Authorship analysis is a field of stylometry which studies information about the authorship of a document, based on features derived from that document \citep{layton-2013}.
-
-In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\texttt{http://pan.webis.de/clef16/pan16-web/author-identification.html}}.
-The aim of this task is to decompose a document into its authorial parts, i.e.
-to split a text into segments and assign an author to every segment \citep{koppel-2011,aldebei-2015}.
-This is one of the unsupervised variants of authorship attribution problem since text samples of known authorship are not available \citep{rosso-2016}.
-As we will describe, in two out of three subtasks of this task only a correct number of authors for a given document is known.
+Authorship analysis is a field of stylometry and studies information about the authorship of a document, based on features derived from that document \citep{layton-2013}.
+Moreover, stylometry analyzes literary style with statistical methods \citep{stein-2011}.
 
 \citet{rosso-2016} divided PAN 2016 author diarization task into three subtasks.
-First subtask is traditionally called intrinsic plagiarism detection.
+First subtask is traditionally called intrinsic plagiarism detection (IPD).
 The goal of this task is to find plagiariarized parts of a document in which 70\% of text is written by main author and the rest by one or more other authors.
@@
 			Task \textit{c} & 54 & 3298 & (2, 10)\\
+			\bottomrule
 		\end{tabular}
@@
 
-For all tasks a different training datasets are publicly available [footnote].
+For all three subtasks a different training datasets are publicly available\footnotemark[1].
 \citet{rosso-2016} explain that they are collections of various documents which are part of Webis-TRC-12 dataset \citep{potthast-2013}.
@@
 Test datasets are currently not publicly available and we could not use them for evaluation of our approach.
-Some basic characterisics of training datasets are shown in table \ref{table-1}.
+Some basic characterisics of training datasets are shown in Table \ref{table-1}.
 
-- writing style, stylistic segmentation, multi-authored work, plagiarism
-- a, b, c
-
-% reference
-% authorship analysis, 
-% intrinsic plagiarism detection, author diarization
-% PAN 2016 author diarization task
-% dataset
+% reference+
+% authorship analysis+, 
+% intrinsic plagiarism detection, author diarization+
+% PAN 2016 author diarization task+
+% dataset+
 
 \section{Related work}
+The basic assumption in authorship analysis is that texts of different authors are mutualy separable because each author has more or less unique writing style \citep{stamatatos-2009a,ding-2016}.
+More precisely, \citet{koppel-2009} explain that methods used in authorship analysis must be able to distinguish writing styles, but also tolerate shallow differences inside the same style because an author's stylistic habbits can conciously or unconciously vary over time.
+Therefore, most of related work tries to find the better features and methods which writing style will be quantified and measured with.
 
-% Kuznetsov, Sittar, Brooke
+\citet{zu-2006} manually created a labeled corpus of plagiarized documents and used it for intrinsic plagiarism detection task.
+They used average sentence length, part of speech tags, average stopword number and the averaged word frequency class as input features for their linear discriminant analysis and suport vector machine (SVM) models.
+They approached that task in a supervised fashion.
+
+\citet{stamatatos-2009b} created a feature vector of normalized occurence of character tri-grams in the whole document.
+That vector represented a document's profile.
+Using a sliding window of fixed length he created same profiles for every window and compared them with the profile of the whole document.
+Result of comparison was an output from a style change function whose peaks were indicators of place in a document where style change occurs.
+All values above the predefined passage criterion were considered a result of plagiarism.
+That approach was unsupervised.
+
+\citet{rahman-2015} classified sections of documents from PAN 2011 dataset with the help of SVM.
+Those sections were again obtanined by sliding a window of fixed length over the document.
+He also proposed new kind of information theoretical features - entropy, relative entropy, correlation coefficient and n-gram frequency class calculated from character tri-gram frequency profiles of each window and the whole document.
+He also used function word bi-gram and tri-gram frequency profiles with 1, 2, 3 and 4 skips.
+The value of style change function introduced by \citet{stamatatos-2009b} was also incorporated in feature vectors.
+
+\citet{stein-2011} defined IPD as the one class classification problem where the text of main author belongs to a one target class and the rest are outliers.
+To find them, they estimated probability distributions of various stylistic features for the target class and outliers.
+Then a naive Bayes' algorithm was applied to feature vectors whose values lie outside the predefined uncertainity intervals.
+An additional outlier post-processing methods were also tested.
+The most successful was the unmasking technique described by \citet{koppel-2009}.
+The main sense of unmasking is to iteratively remove the best features that distinguish two classes and observe the speed with which cross-validation accuracy of again trained classifier drops.
+If the drop is slow and smooth, the outliers are indeed outliers because after \textit{n} iterations of removing discriminative features they are still separable from the main auhor's work.
+
+ \citet{koppel-2011} used two staged approach in clustering of pre-segmented mixed biblical text written by two authors.
+First they used normalized cuts algorithm with cosine similarity to obtain initial clusters of segments which were represented only by normalized counts of synonymes from Hebrew synsets.
+Samples from initial clusers were separated in core and non-core samples via an iterative procedure, and core ones were labeled.
+SVM classifier was used to classify non-core samples, but now a bag-of-words feature vectors were used.
+The whole approach resulted with very good clusters.
+They also tried this method on an unsegmented case.
+Text was first splitted in a way that minimizes doubly-represented synonyms in segments and the same procedure was repeated.
+The clustering performance was lower than in pre-segmented case.
+
+\citet{brooke-2013} concluded that a very good initial segmentation of text, at least in poems written by T.
+S.
+Elliot, is needed for a good performance of their modified k-means algorithm in clustering of voices.
+Except often character, lexical and syntactic features, they used features such as average frequency in a large  external corpus \citep{brants-2006}.
+One of the most promising feature they considered is the centroid of 20 dimensional distributional vectors obtained by applying latent semantic analysis on a large web corpus \cite{landauer-1997}.
+
+The works by \citet{kuznetsov-2016} and \citet{sittar-2016} were submitted on the PAN 2016 competition for three aforementioned tasks.
+For the task \textit{a}, \citet{kuznetsov-2016} trained a Gradient Boosting Regression Trees (GBRT) model on PAN 2011 dataset as a style change function used for threshold based outlier detection.
+Every sentence was vectorized using word frequencies, n-gram frequencies, punctuaiton symbols and the universal POS tags count, sentence length and mean length of sentence words.
+The final input to the model was concatenation of center sentence vector and ones from context of size $\pm2$.
+In task \textit{b} they used a Hidden Markov Model with Gaussian Emissions for document segmentation over the same sentence scores from task \textit{a}.
+To estimate the unknown number of authors \textit{n} in task \textit{c}, they chose \textit{n} from 2 to 20 which maximizes their cluster discrepancy measure $Q(n)$.
+
+\citet{sittar-2016} used k-means algorthm to cluster \textit{ClustDist} scores of each sentence, where the number of groups was equal to the known number of authors in tasks \textit{a} and \textit{b}.
+In task \textit{c}, a number of groups was generated randomly.
+Although they defined a \textit{ClustDist} score for a single sentence as an average distance between current and every other sentence vector, which is again a similar concept like a style change function, in provided example they used only a sum of unknown distance measures.
+Fifteen features in total were used for sentence vectorization, including average word and sentence lengths, count and ratios of characters, digits upperpase letters, spaces and tabs.
+
+The most of described approaches combine supervised and usupervised methods and operate on the level of longer text segments or sentences.
+We were inspired by \citet{brooke-2013} who said that a more radical approach would not separate those tasks in segmentation and clustering steps, but rather build an authorial segments that would also form good clusters.
+Since the style change in our tasks can occur even between two tokens in a same sentence, we wanted our model should be able to work on the token level.
+Instead of clustering tokens directly, we decided to cluster their vectorized stylistic contexts because they obviously contain more valuable sylistic information than tokens alone.
 
@@
 baselines
-
-\begin{table}
-	\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
-	\label{tab:narrow-table}
-	\begin{center}
-		\begin{tabular}{cccc}
-			\toprule
-			Model & $R$ & $P$ & $F_1$\\
-			\midrule
-			Dummy & 0 & 1 & 2 \\
-			One & 0 & 1 & 2 \\
-			One & 0 & 1 & 2 \\
-			\midrule
-			One & 0 & 1 & 2 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-\end{table}
 
@@
 
+\begin{table}
+	\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
+	\label{tab:narrow-table}
+	\begin{center}
+		\begin{tabular}{cccc}
+			\toprule
+			Model & $R$ & $P$ & $F_1$\\
+			\midrule
+			Dummy & 0 & 1 & 2 \\
+			One & 0 & 1 & 2 \\
+			One & 0 & 1 & 2 \\
+			\midrule
+			One & 0 & 1 & 2 \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+\end{table}
+
 \bibliographystyle{tar2016}

### 2017-05-29 paper/paper.tex
Added some text

--- 2017-05-28 paper/paper.tex
@@
 \usepackage{amssymb}
+
 \usepackage{makecell}
+\usepackage[hyphens]{url}
 
@@
 
-In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\texttt{http://pan.webis.de/clef16/pan16-web/author-identification.html}}.
+In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\url{http://pan.webis.de/clef16/pan16-web/author-identification.html}}.
 The aim of this task is to decompose a document into its authorial parts, i.e.
@@
 
-\section{The proposed approaches}
-clustering, sliding window
-pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
+\section{Author Diarization?}
+% describe the problem
+% define formally: document, segmentation, segment, author assignement (label)
+% define evaluation metrics
 
-clustering metric
+Let $D$ be the domain of documents. We define a document $d\in D$ as a finite sequence of tokens $t_i$, i.e. $d = (t_1, \dots, t_n)$ and $n$ can differ among documents.
+
+For each document, there is a corresponding mapping to a sequence of labels $(a_1, \dots, a_n)$, that are representing groupings of tokens by authors.
+The labels $a_i$ are indices of authors of the document, and they range from $1$ to $m$, where $m$ is the number of authors of the document.
+Each token $t\in d$ is assigned a document-level label associating it to an author.
+Equivalently, the codomain of the mapping can also be defined as a set of segments $S$.
+A segment $s$ is a set of tokens where each is assigned the same label and the following applies:
+\begin{equation}
+	t_{i_1}\in s\ \wedge t_{i_2}\in s \wedge  i_1<i_3<i_2 \Rightarrow t_{i_3} \in s.
+\end{equation}
+Also, for a set of segments to be valid, the segments must cover all terms in the document and not overlap:
+\begin{equation}
+	\bigcup_{s\in S}s = T_d  \wedge \bigcap_{s\in S}s = \{\},
+\end{equation}
+where $T_d$ is the set of all terms in document $d$.
+
+Let $\mathcal{D}$ be a
+
+%\section{The proposed approach}
+% clustering, sliding window
+% pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
+% define the pipeline formally P = (f_p: d\times->t, f_b: t->\phi, f_t: \phi->\phi', c: \phi'->labels, f_s: labels\times d->s)
+% describe GroupRepel loss, describe AutoKMeans, 
+% clustering metric
 
@@
 
-\section{Experimantal results}
+\section{Experimental results}
 
@@
 
+\section{Further work}
+% more systematic parameter choice, model development
+% mention possible applicability to author clustering and extrinsic plagiarism detections
+
 \section*{Acknowledgements}

### 2017-05-30 paper/paper.tex
Small changes.

--- 2017-05-29 paper/paper.tex
@@
 The goal of this task is to find plagiariarized parts of a document in which 70\% of text is written by main author and the rest by one or more other authors.
-The term \textit{intrinsic} means that a decision whether plagiarized parts exist or not has to be made only by analysing a given document, without any comparisons with external sources.
+The term \textit{intrinsic} means that a decision whether plagiarized parts exist has to be made only by analysing a given document, without any comparisons with external sources.
 In the rest of the paper we refer to this subtask as a task \textit{a}.
@@
 
-\section{The proposed approaches}
-clustering, sliding window
-pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
+\section{Author diarization and intrinsic plagiarism detetion ()}
+% describe the problem
+% define formally: document, segmentation, segment, author assignement (label)
+% define evaluation metrics
 
-clustering metric
+Let $\Delta$ be the domain of documents.
+We define a document $D\in \Delta$ as a finite sequence of tokens $(t_i)_{i=1}^n$, where $n$ can differ among documents.
+Given a document, each of its tokens is unique and defined by its character sequence and position in the document.
+Therefore, a document can be equivalently represented by its set of tokens $T_D=\{t_i\}_{i=1}^n$.
+
+For each document, there is a corresponding mapping to a sequence of labels $(a_i)_{i=1}^n$ that are representing groupings of tokens by authors.
+The labels $a_i$ are indices of authors of the document.
+Each token $t_i\in T_D$ is assigned a document-level label $a_i \in \{1..m\}$ associating it to one of $m$ authors.
+The exact value of the label is not important.
+It is only required that all tokens corresponding to the same author have the same label.
+Therefore, there are $m!$ equivalent such mappings given a document.
+
+In the case of intrinsic plagiarism detection, there are only $2$ labels: $0$ representing the main author, and $1$ representing plagiarized text.
+
+Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$.
+A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ represents a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each is assigned the same label.
+For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
+\begin{equation}
+	\bigcup_{s\in S}s = T_D  \wedge \bigcap_{s\in S}s = \{\}.
+\end{equation}
+The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$.
+
+Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations., i.e.
+$\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$.
+Our goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e.
+makes good predictions given unseen documents.
+
+\subsection{Evaluation measures}
+
+For evaluation of intrinsic plagiarism detection, \citet{stein-2010} define multiple measures for different aspects of a system's perfromance.
+The main measures are binary macro-averaged nad micro-averaged precision ($P$), recall (R) and $F_1$-score.
+For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$ measures proposed by \citet{rosales-mendez-2013}, which are specialized for evaluation of clustering results.
+
+Let $l$ be a function that associates lengths in characters to segments.
+Specially, $l(\{\}) = 0$.
+For notational convenience, we also use $l$ to denote the sum of lengths of all segments in a set of segments: $l(S) = \sum_{s\in S} l(s),$ where $S$ is as set of segments.
+Given a document $D$, let $S_\mathrm{p} \subseteq \sigma(D)$ be a set of all true plagiarism segments of the document and $\hat{S}_\mathrm{p} \subseteq \hat{\sigma}(D)$ the segments predicted as plagiarism by the  model.
+With ${S_\mathrm{tp} = \bigcup_{(s,\hat{s})\in S_\mathrm{p}\times\hat{S}_\mathrm{p}} l(s\cap\hat{s})}$, the micro-averaged evaluation measures for intrinsic plagiarism detection are defined as follows:
+\begin{align}
+P_\mu &= \frac{l(\hat{S}_\mathrm{tp})}{l(\hat{S}_\mathrm{p})}, \\
+R_\mu &= \frac{l(\hat{S}_\mathrm{tp})}{l(S_\mathrm{p})}, \\
+F_\mu &= \frac{2}{P_\mu^{-1}+R_\mu^{-1}}.
+\end{align}
+The macro-average evaluation measures treat all plagiarism segments as equally important and are not affected by their lengths:
+\begin{align}
+P_M &= \frac{1}{|\hat{S}_\mathrm{p}|}
+	\sum_{\hat{s}\in\hat{S}_\mathrm{p}}
+		\frac{{\sum_{s\in S_\mathrm{p}} l(s\cap\hat{s})}}{l(\hat{s})}, \\
+R_M &= \frac{1}{|S_\mathrm{p}|}
+	\sum_{\hat{s}\in S_\mathrm{p}}
+		\frac{{\sum_{s\in \hat{S}_\mathrm{p}} l(s\cap\hat{s})}}{l(s)}, \\
+F_M &= \frac{2}{P_M^{-1}+R_M^{-1}}.
+\end{align}
+
+\section{The proposed approach}
+% clustering, sliding window
+% pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
+% define the pipeline formally P = (f_p: d\times->t, f_b: t->\phi, f_t: \phi->\phi', c: \phi'->labels, f_s: labels\times d->s)
+% describe GroupRepel loss, describe AutoKMeans, 
+% clustering metric
 
@@
 No new information should be presented in the conclusion; this section only summarizes and concludes the paper.
+
+\section{Further work}
+% more systematic parameter choice, model development
+% mention possible applicability to author clustering and extrinsic plagiarism detections
 

### 2017-05-30 paper/paper.tex
Comment added.
Hopefully resolved all conflicts.

@@
 
+\citet{rosso-2016} divided PAN 2016 author diarization task into three subtasks.
+First subtask is traditionally called intrinsic plagiarism detection (IPD).
+The goal of this task is to find plagiariarized parts of a document in which at least $70\%$ of text is written by main author and the rest by one or more other authors.
+The term \textit{intrinsic} means that a decision whether plagiarized parts exist or not has to be made only by analysing a given document, without any comparisons with external sources.
+In the rest of the paper we refer to this subtask as a task \textit{a}.
+
 \begin{table}
-	\caption{Basic characteristics of train datasets}
+	\caption{Basic characteristics of train datasets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
 	\label{table-1}
@@
 			\midrule
-			Task \textit{a} & 71 & 1679 & (2, 2)\\
+			Task \textit{a} & 71 & 1679 & (2, 2)*\\
 			Task \textit{b} & 55 & 3767 & (2, 10)\\
@@
 
-\section{Author diarization and intrinsic plagiarism detetion ()}
+\section{Author diarization and intrinsic plagiarism detetion}
 % describe the problem
@@
 The labels $a_i$ are indices of authors of the document.
-Each token $t_i\in T_D$ is assigned a document-level label $a_i \in \{1..m\}$ associating it to one of $m$ authors.
+Each token $t_i\in T_D$ is assigned a document-level label $a_i \in \{1..c\}$ associating it to one of $c$ authors.
 The exact value of the label is not important.
@@
 Therefore, there are $m!$ equivalent such mappings given a document.
-
 In the case of intrinsic plagiarism detection, there are only $2$ labels: $0$ representing the main author, and $1$ representing plagiarized text.
@@
 $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$.
-Our goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e.
+The goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e.
 makes good predictions given unseen documents.
@@
 The main measures are binary macro-averaged nad micro-averaged precision ($P$), recall (R) and $F_1$-score.
-For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$ measures proposed by \citet{rosales-mendez-2013}, which are specialized for evaluation of clustering results.
+For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$ measures described by \citet{amigo-2009}, which are specialized for evaluation of clustering results.
+The same measures were used for evaluation on the PAN 2016 competition \citep{rosso-2016}.
 
@@
 \begin{align}
-P_\mu &= \frac{l(\hat{S}_\mathrm{tp})}{l(\hat{S}_\mathrm{p})}, \\
-R_\mu &= \frac{l(\hat{S}_\mathrm{tp})}{l(S_\mathrm{p})}, \\
-F_\mu &= \frac{2}{P_\mu^{-1}+R_\mu^{-1}}.
+P_\mathrm{\mu} &= \frac{l(\hat{S}_\mathrm{tp})}{l(\hat{S}_\mathrm{p})}, \\
+R_\mathrm{\mu} &= \frac{l(\hat{S}_\mathrm{tp})}{l(S_\mathrm{p})}, \\
+F_\mathrm{\mu} &= \frac{2}{P_\mathrm{\mu}^{-1}+R_\mathrm{\mu}^{-1}}.
 \end{align}
@@
 \begin{align}
-P_M &= \frac{1}{|\hat{S}_\mathrm{p}|}
+P_\mathrm{M} &= \frac{1}{|\hat{S}_\mathrm{p}|}
 	\sum_{\hat{s}\in\hat{S}_\mathrm{p}}
 		\frac{{\sum_{s\in S_\mathrm{p}} l(s\cap\hat{s})}}{l(\hat{s})}, \\
-R_M &= \frac{1}{|S_\mathrm{p}|}
+R_\mathrm{M} &= \frac{1}{|S_\mathrm{p}|}
 	\sum_{\hat{s}\in S_\mathrm{p}}
 		\frac{{\sum_{s\in \hat{S}_\mathrm{p}} l(s\cap\hat{s})}}{l(s)}, \\
-F_M &= \frac{2}{P_M^{-1}+R_M^{-1}}.
+F_\mathrm{M} &= \frac{2}{P_\mathrm{M}^{-1}+R_\mathrm{M}^{-1}}.
+\end{align}
+
+In author diarization document segments have to be clustered into $c$ clusters, where $c$ is the number of authors that may or may not be known to the system.
+We divide the segments from the true segmentation $S$ and the predicted segmentation $\hat{S}$ each into sets of segments $S_i$, $i=1..c$ and $\hat{S}_j, j=1..\hat{c}$, where $c$ is the true number of authors, and $\hat{c}$ the predicted number of authors.
+We use the following \emph{BCubed} measures for evaluation:
+\begin{align}
+P_\mathrm{B^3} &= \sum_{i=1}^c \frac{1}{l(S_i)}\sum_{j=1}^{\hat{c}}
+	\sum_{(s,\hat{s})\in S_i\times \hat{S}_j} l(s\cap \hat{s})^2 \\
+R_\mathrm{B^3} &= \sum_{j=1}^{\hat{c}} \frac{1}{l(\hat{S}_j)}\sum_{i=1}^{c}
+	\sum_{(s,\hat{s})\in S_i\times \hat{S}_j} l(s\cap \hat{s})^2 \\
+F_\mathrm{B^3} &= \frac{2}{P_\mathrm{B^3}^{-1}+R_\mathrm{B^3}^{-1}}.
 \end{align}
@@
 
-\begin{itemize}
-\item a
-\item b
-\end{itemize}
+Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_b}, f_\mathrm{t}:\Phi_{n_b}\rightarrow \Phi_{n_t}, f_\mathrm{c}:\Phi_{n_t}\rightarrow C)$.
+Here $\Delta$ is the tokenized document domain as defined in section ((((((($\circ$))))))).
+$\Phi_{n_b}$ and $\Phi_{n_t}$ are sets of variable-length sequences of feature vectors with dimension $n_b$ and $n_t$ respectively.
+$n_b$ and $n_d$ can either be fixed or depend on the document being processed.
+$C$ is the set of all sequences of length $n$ (the number of tokens in the document) with elements being indices of authors/clusters.
+
+The basic feature extractor denoted with $f_\mathrm{b}$ is used to extract stylistic features from the contexts of all tokens.
+If $D$ is a document with $n$ tokens, the basic feature extractor outputs a sequence of $n$ feature vectors, each vector representing the context of one token.
+$n_\mathrm{b}$ denotes the dimension of those vectors.
+The next step in the pipeline is the feature transformation $f_\mathrm{t}$ that maps the basic features to a space that they can be better clustered in.
+The dimension of the new feature space $n_\mathrm{t}$ generally doesn't equal $n_\mathrm{b}$.
+The final step in the pipeline is clustering denoted with $f_\mathrm{c}$.
+The clustering algorithm clusters tokens, each cluster representing an author.
+Depending on the task, The clustering algorithm can either be given a known number of authors, or try to predict it.
+
+The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D\in\Delta$, (2) features are extracted for all tokens and their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (\mathbf{t}_i)_{i=1}^n = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n=|T_D|$, and (4) a segmentation $\hat{S}$ is generated based on the document $D$ and the sequence of predicted author labels.
+
+% details for each component
+\paragraph{Tokenization.} Tokenization.
+
+\paragraph{Basic feature extraction.} Differences between the 2 model variants.
+
+basic features
+
+\paragraph{Feature transformation.} Differences between the 2 model variants. Training.
+
+identity
+
+scaling
+
+concatenation with squared features
+
+transformation trained via SGD
+
+Let $(\mathbf{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be the sequence of basic feature vectors with elements from $\mathbb{R}^{n_b}$.
+Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$.
+We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$.
+Let $(\mathbf{t}_i)_{i=1}^n =  f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n) = (T(\mathbf{b}_i))_{i=1}^n$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
+
+\paragraph{Clustering.}
+
+clustering algorithms
+
+k-means HAC DBSCAN auto-k-means
+
+\paragraph{Segmentation generation.} something short
 
@@
 results
+don't forget to describe tolerance
 
@@
 	\begin{center}
-		\begin{tabular}{cccc}
+		\begin{tabular}{c|ccc|ccc}
 			\toprule
-			Model & $R$ & $P$ & $F_1$\\
+			Model & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
 			\midrule

### 2017-05-30 paper/paper.tex
gitignore

@@
 We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$.
-Let $(\mathbf{t}_i)_{i=1}^n =  f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n) = (T(\mathbf{b}_i))_{i=1}^n$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
+Let $(\mathbf{t}_i)_{i=1}^n = (T(\mathbf{b}_i))_{i=1}^n = f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
 

### 2017-05-30 paper/paper.tex
gitignore test
Compiled paper.

--- 2017-05-30 paper/paper.tex
@@
 The term \textit{intrinsic} means that a decision whether plagiarized parts exist has to be made only by analysing a given document, without any comparisons with external sources.
-In the rest of the paper we refer to this subtask as a task \textit{a}.
-
-\citet{rosso-2016} divided PAN 2016 author diarization task into three subtasks.
-First subtask is traditionally called intrinsic plagiarism detection (IPD).
-The goal of this task is to find plagiariarized parts of a document in which at least $70\%$ of text is written by main author and the rest by one or more other authors.
-The term \textit{intrinsic} means that a decision whether plagiarized parts exist or not has to be made only by analysing a given document, without any comparisons with external sources.
 In the rest of the paper we refer to this subtask as a task \textit{a}.

### 2017-05-30 paper/paper.tex

--- 2017-05-30 paper/paper.tex
@@
 
-identity
+id
 

### 2017-05-31 paper/paper.tex
Tokenization and part of bfe.

@@
 
+\usepackage{enumitem}
 \usepackage{makecell}
@@
 The most of described approaches combine supervised and usupervised methods and operate on the level of longer text segments or sentences.
-We were inspired by \citet{brooke-2013} who said that a more radical approach would not separate those tasks in segmentation and clustering steps, but rather build an authorial segments that would also form good clusters.
 Since the style change in our tasks can occur even between two tokens in a same sentence, we wanted our model should be able to work on the token level.
+We were also inspired by \citet{brooke-2013} who said that a more radical approach would not separate described tasks in segmentation and clustering steps, but rather build an authorial segments that would also form good clusters.
 Instead of clustering tokens directly, we decided to cluster their vectorized stylistic contexts because they obviously contain more valuable sylistic information than tokens alone.
 
-\section{Author diarization and intrinsic plagiarism detetion}
+\section{Author diarization and intrinsic plagiarism detection}
 % describe the problem
@@
 For evaluation of intrinsic plagiarism detection, \citet{stein-2010} define multiple measures for different aspects of a system's perfromance.
-The main measures are binary macro-averaged nad micro-averaged precision ($P$), recall (R) and $F_1$-score.
+The main measures are binary macro-averaged nad micro-averaged precision ($P$), recall ($R$) and $F_1$-score.
 For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$ measures described by \citet{amigo-2009}, which are specialized for evaluation of clustering results.
@@
 $\Phi_{n_b}$ and $\Phi_{n_t}$ are sets of variable-length sequences of feature vectors with dimension $n_b$ and $n_t$ respectively.
-$n_b$ and $n_d$ can either be fixed or depend on the document being processed.
+$n_b$ and $n_t$ can either be fixed or depend on the document being processed.
 $C$ is the set of all sequences of length $n$ (the number of tokens in the document) with elements being indices of authors/clusters.
@@
 The final step in the pipeline is clustering denoted with $f_\mathrm{c}$.
-The clustering algorithm clusters tokens, each cluster representing an author.
-Depending on the task, The clustering algorithm can either be given a known number of authors, or try to predict it.
+The clustering algorithm implicitly clusters tokens because it actually clusters their stylistic contexts, each cluster representing an author.
+Depending on the task, the clustering algorithm can either be given a known number of authors, or try to predict it.
 
@@
 % details for each component
-\paragraph{Tokenization.} Tokenization.
+\paragraph{Tokenization.} As a preprocessing step, we tokenized each document $D$ with \texttt{nltk}\footnote{\texttt{http://www.nltk.org}} toolkit, to obtain a set of tokens $T_D$.
+We also performed Part of Speech tagging with the same tool, to speed up a basic feature extraction which we describe below.
+We didn't use other preprocessing techniques such as lemmatization, stemming and stop word removal because they would take away a lot of stylometric data from text \cite{stamatatos-2009a}.
+The final output from tokenization step was a finite sequence $\{(t_i, o_i, l(t_i), POS_i)\}_{i=1}^n$ where $o_i$ is the offset of token $t_i$, $l(t_i)$ its length in characters and $POS_i$ its POS tag.
 
-\paragraph{Basic feature extraction.} Differences between the 2 model variants.
+\paragraph{Basic feature extraction.} 
+We defined the stylistic context of a token $t_i$ as a set of tokens [SYMBOL] where [SYMBOL] is a context size.
+From each context we extracted the most used stylometric features which we found in previous work of ():
+\begin{itemize}
+	\item \textit{Character tri-grams}.
+Frequencies of \textit{n}-grams on character level have been very useful in quantifying the writing style \citep{stamatatos-2009b}.
+They are able to capture lexical and contextual information, use of punctuation and errors which can be an author's  "fingerprints".
+This feature is also tolerant to noise.
+Based on work by \cite{stamatatos-2009a} and \citet{rahman-2015}, we choose $n=3$.
+Maximal dimension of this feature vector was set to 200.
+	\item \textit{Stop words}.
+According to \cite{stamatatos-2009a}, sometimes also called \textit{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
+Authors use them mainly unconciously and are found to be one of the most discriminative in authorship attribution since they represent pure stylistic choices of authors' \cite{burrows-1987,argamon-2005}.
+	\item \textit{Special characters}.
+	\item \textit{POS tag counts}.
+	\item \textit{Average token length}.
+	\item \textit{Bag of Words}.
+	\item \textit{Type-token ratio}.
+\end{itemize}
+
+Differences between the 2 model variants....
 
@@
 baselines
-
+repo link
 Mention cofidences.

### 2017-05-31 paper/paper.tex
no message

--- 2017-05-30 paper/paper.tex
@@
 
-\section{Author diarization and intrinsic plagiarism detetion}
+\section{Author diarization and intrinsic plagiarism detetion} \label{sec:author-diraization}
 % describe the problem
@@
 Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_b}, f_\mathrm{t}:\Phi_{n_b}\rightarrow \Phi_{n_t}, f_\mathrm{c}:\Phi_{n_t}\rightarrow C)$.
-Here $\Delta$ is the tokenized document domain as defined in section ((((((($\circ$))))))).
+Here $\Delta$ is the tokenized document domain as defined in section \ref{sec:author-diraization}.
 $\Phi_{n_b}$ and $\Phi_{n_t}$ are sets of variable-length sequences of feature vectors with dimension $n_b$ and $n_t$ respectively.
-$n_b$ and $n_d$ can either be fixed or depend on the document being processed.
+$n_b$ and $n_t$ can either be fixed or depend on the document being processed.
 $C$ is the set of all sequences of length $n$ (the number of tokens in the document) with elements being indices of authors/clusters.
@@
 
-The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D\in\Delta$, (2) features are extracted for all tokens and their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (\mathbf{t}_i)_{i=1}^n = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n=|T_D|$, and (4) a segmentation $\hat{S}$ is generated based on the document $D$ and the sequence of predicted author labels.
+The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D\in\Delta$, (2) for all tokens, features are extracted from their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (\mathbf{t}_i)_{i=1}^n = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n=|T_D|$, and (4) a segmentation $\hat{S}$ is generated based on the document $D$ and the sequence of predicted author labels.
 
@@
 Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$.
-We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$.
+We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$, i.e.
+we want to maximize segregation and compactness of clusters consisting of transformed feature vectors labeled with their true author labels.
 Let $(\mathbf{t}_i)_{i=1}^n = (T(\mathbf{b}_i))_{i=1}^n = f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
+We define the following loss in order to optimize the transformation $T$ for clusterability:
+\begin{equation}
+	L = L_\mathrm{c} + L_\mathrm{s},
+\end{equation}
+where $L_\mathrm{c}$ is the \emph{compactness loss} which is proportional to the average variance of groups and $L_\mathrm{s}$ the \emph{segregation loss}.
+\begin{align}
+	L_\mathrm{c} &= \\
+	L_\mathrm{s} &= 
+\end{align}
 

### 2017-05-31 paper/paper.tex
Initial feature extraction described.

--- 2017-05-31 paper/paper.tex
@@
 \paragraph{Basic feature extraction.} 
-We defined the stylistic context of a token $t_i$ as a set of tokens [SYMBOL] where [SYMBOL] is a context size.
-From each context we extracted the most used stylometric features which we found in previous work of ():
+We defined the stylistic context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-c}^{i-1} \cup \{t_k\}_{k=i+1}^{i+c}$ where $c$ is a context size.
+From each context we extracted the most used stylometric features which we found in previous work.
 \begin{itemize}
@@
 Frequencies of \textit{n}-grams on character level have been very useful in quantifying the writing style \citep{stamatatos-2009b}.
-They are able to capture lexical and contextual information, use of punctuation and errors which can be an author's  "fingerprints".
+They are able to capture lexical and contextual information, use of punctuation and errors which can be an author's  "fingerprint".
 This feature is also tolerant to noise.
-Based on work by \cite{stamatatos-2009a} and \citet{rahman-2015}, we choose $n=3$.
+Based on work by \citet{stamatatos-2009a} and \citet{rahman-2015}, we choose $n=3$.
 Maximal dimension of this feature vector was set to 200.
 	\item \textit{Stop words}.
-According to \cite{stamatatos-2009a}, sometimes also called \textit{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
-Authors use them mainly unconciously and are found to be one of the most discriminative in authorship attribution since they represent pure stylistic choices of authors' \cite{burrows-1987,argamon-2005}.
+According to \citet{stamatatos-2009a}, sometimes also called \textit{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
+They are used unconciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' {burrows-1987,argamon-2005}.
+We used frequencies of 156 english stop words available in \texttt{nltk}.
 	\item \textit{Special characters}.
+We used counts of all character sequences which satisfied a regular expression defined as [REGEX].
+Although character n-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose.
+\citet{koppel-2009} mentioned that authors can have different punctuation habbits.
 	\item \textit{POS tag counts}.
+This is syntactic feature which \citet{koppel-2009} and \citet{stamatatos-2009a} also identified as a discriminative one in authorship analysis and it was used by \citet{kuznetsov-2016}.
+We used all 12 tags from the universal tagset.
 	\item \textit{Average token length}.
+Used by \citet{kuznetsov-2016}, \citet{sittar-2016},  \citet{brooke-2012} and \citet{stein-2011}.
+\citet{koppel-2009} characterized this feature as a complexity measure.
 	\item \textit{Bag of Words}.
+Bag of words text representation more captures content, rather than style \citep{stamatatos-2009a}.
+We included this feature because it boosted performance of our initial testing, even without words been previously stemmed or lemmatized (stop words were excluded).
+Vocabulary had a maximum of 100 words.
 	\item \textit{Type-token ratio}.
+We wanted to use that feature to measure the vocabulary richness in a token's context, but after we finished with performance evaluations we realized that there was a bug in implementation and that feature did not contribute to overal results.
+The feature should be calculated as the ratio of vocabulary size and total number of tokens of the text \citep{stamatatos-2009a}.
 \end{itemize}

### 2017-05-31 paper/paper.tex
Fixed some errors, added more text about the feature transformation

--- 2017-05-31 paper/paper.tex
@@
 
+% additional packages
 \usepackage{enumitem}
@@
 \usepackage[hyphens]{url}
+\usepackage{bm}
+\newcommand{\vect}[1]{\bm{#1}}
+\newcommand{\matr}[1]{\vect{#1}}
 
@@
 \section{Introduction}
-In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\texttt{https://tinyurl.com/y9m4zntm}}.
+In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\url{http://pan.webis.de/clef16/pan16-web/author-identification.html}}.
 The aim of this task is to decompose a document into its authorial parts, i.e.
@@
 
-The simplest variant of authorship attribution problem is about finding the most likely author for a given document, from a set of candidate authors whose authentic writing examples are available \citep{stamatatos-2009a,stein-2011,ding-2016}.
-Such descirbed problem can be tackeled with supervised machine learning techniques as a single-label multiclass text classification problem, where one class represents one author \citep{stamatatos-2009a}.
+The simplest variant of the authorship attribution problem is about finding the most likely author for a given document from a set of candidate authors whose authentic writing examples are available \citep{stamatatos-2009a,stein-2011,ding-2016}.
+This problem can be tackled with supervised machine learning techniques as a {{{single-label}}} multiclass text classification problem, where one class represents one author \citep{stamatatos-2009a}.
 
-Authorship attribution problem is also known as authorship identification and it is a part of authorship analysis \citep{stamatatos-2009a,ding-2016}.
+The authorship attribution problem is also known as authorship identification and it is a part of authorship analysis \citep{stamatatos-2009a,ding-2016}.
 Authorship analysis is a field of stylometry and studies information about the authorship of a document, based on features derived from that document \citep{layton-2013}.
-Moreover, stylometry analyzes literary style with statistical methods  \citep{stein-2011}.
+Moreover, stylometry analyses literary style with statistical methods  \citep{stein-2011}.
 
-\citet{rosso-2016} divided PAN 2016 author diarization task into three subtasks.
-First subtask is traditionally called intrinsic plagiarism detection (IPD).
-The goal of this task is to find plagiariarized parts of a document in which 70\% of text is written by main author and the rest by one or more other authors.
+\citet{rosso-2016} divided the PAN 2016 author diarization task into three subtasks.
+The first subtask is traditionally called intrinsic plagiarism detection (IPD).
+The goal of this task is to find plagiarized parts of a document in which at least $70\%$ of text is written by main author and the rest by one or more other authors.
 The term \textit{intrinsic} means that a decision whether plagiarized parts exist has to be made only by analysing a given document, without any comparisons with external sources.
-In the rest of the paper we refer to this subtask as a task \textit{a}.
+In the rest of the paper we refer to this subtask as task \emph{a}.
 
 \begin{table}
-	\caption{Basic characteristics of train datasets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
+	\caption{Basic characteristics of training datasets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
 	\label{table-1}
@@
 			\midrule
-			Task \textit{a} & 71 & 1679 & (2, 2)*\\
-			Task \textit{b} & 55 & 3767 & (2, 10)\\
-			Task \textit{c} & 54 & 3298 & (2, 10)\\
+			Task \emph{a} & 71 & 1679 & (2, 2)*\\
+			Task \emph{b} & 55 & 3767 & (2, 10)\\
+			Task \emph{c} & 54 & 3298 & (2, 10)\\
 			\bottomrule
@@
 In the second subtask we need to segment a given document and group identified segments by author.
-In the rest of the paper we refer to the second subtask as a task \textit{b}.
-Third subtask differs from the second one in the fact that exact number of authors is unkown.
-In the rest of the paper we refer to the third subtask as a task \textit{c}.
+In the rest of the paper we refer to the second subtask as a task \emph{b}.
+The third subtask differs from the second one in the fact that exact number of authors is unknown.
+In the rest of the paper we refer to the third subtask as a task \emph{c}.
 
-For all three subtasks a different training datasets are publicly available\footnotemark[1].
+For each of the three subtasks a training dataset is publicly available\footnotemark[1].
 \citet{rosso-2016} explain that they are collections of various documents which are part of Webis-TRC-12 dataset \citep{potthast-2013}.
@@
 Test datasets are currently not publicly available and we could not use them for evaluation of our approach.
-Some basic characterisics of training datasets are shown in Table \ref{table-1}.
+Some basic characteristics of the training datasets are shown in Table \ref{table-1}.
 
@@
 \section{Related work}
-The basic assumption in authorship analysis is that texts of different authors are mutualy separable because each author has more or less unique writing style \citep{stamatatos-2009a,ding-2016}.
-More precisely, \citet{koppel-2009} explain that methods used in authorship analysis must be able to distinguish writing styles, but also tolerate shallow differences inside the same style because an author's stylistic habbits can conciously or unconciously vary over time.
+The basic assumption in authorship analysis is that texts of different authors are mutually separable because each author has a more or less unique writing style \citep{stamatatos-2009a,ding-2016}.
+More precisely, \citet{koppel-2009} explain that methods used in authorship analysis must be able to distinguish writing styles, but also tolerate shallow differences within the same style because an author's stylistic habits can consciously or unconsciously vary over time.
 Therefore, most of related work tries to find the better features and methods which writing style will be quantified and measured with.
 
-\citet{zu-2006} manually created a labeled corpus of plagiarized documents and used it for intrinsic plagiarism detection task.
-They used average sentence length, part of speech tags, average stopword number and the averaged word frequency class as input features for their linear discriminant analysis and suport vector machine (SVM) models.
+\citet{zu-2006} manually created a labelled corpus of plagiarized documents and used it for intrinsic plagiarism detection task.
+They used average sentence length, part of speech tags, average stop word number and the averaged word frequency class as input features for their linear discriminant analysis and support vector machine (SVM) models.
 They approached that task in a supervised fashion.
 
-\citet{stamatatos-2009b} created a feature vector of normalized occurence of character tri-grams in the whole document.
+\citet{stamatatos-2009b} created a feature vector of normalized occurrence of character tri-grams in the whole document.
 That vector represented a document's profile.
-Using a sliding window of fixed length he created same profiles for every window and compared them with the profile of the whole document.
-Result of comparison was an output from a style change function whose peaks were indicators of place in a document where style change occurs.
+Using a sliding window of fixed length he created same profiles for every window position and compared them with the profile of the whole document.
+The result of the comparison was an output from a style change function whose peaks indicate positions in the document where style changes occur.
 All values above the predefined passage criterion were considered a result of plagiarism.
@@
 \citet{rahman-2015} classified sections of documents from PAN 2011 dataset with the help of SVM.
-Those sections were again obtanined by sliding a window of fixed length over the document.
-He also proposed new kind of information theoretical features - entropy, relative entropy, correlation coefficient and n-gram frequency class calculated from character tri-gram frequency profiles of each window and the whole document.
-He also used function word bi-gram and tri-gram frequency profiles with 1, 2, 3 and 4 skips.
-The value of style change function introduced by \citet{stamatatos-2009b} was also incorporated in feature vectors.
+Those sections were again obtained by sliding a window of fixed length over the document.
+He also proposed a new kind of information theoretical features - entropy, relative entropy, correlation coefficient and $n$-gram frequency class calculated from character tri-gram frequency profiles of each window and the whole document.
+{{{He also used function word bi-gram and tri-gram frequency profiles with $1$, $2$, $3$ and $4$ skips.}}} The value of the style change function introduced by \citet{stamatatos-2009b} was also incorporated into the feature vectors.
 
-\citet{stein-2011} defined IPD as the one class classification problem where the text of main author belongs to a one target class and the rest are outliers.
+\citet{stein-2011} defined IPD as a one class classification problem where the parts of text written by the main author is associated to the target class and the other parts of text are outliers.
 To find them, they estimated probability distributions of various stylistic features for the target class and outliers.
-Then a naive Bayes' algorithm was applied to feature vectors whose values lie outside the predefined uncertainity intervals.
-An additional outlier post-processing methods were also tested.
+Then a naive Bayes' algorithm was applied to feature vectors whose values lied outside the predefined uncertainity intervals.
+Additional outlier post-processing methods were also tested.
 The most successful was the unmasking technique described by \citet{koppel-2009}.
-The main sense of unmasking is to iteratively remove the best features that distinguish two classes and observe the speed with which cross-validation accuracy of again trained classifier drops.
-If the drop is slow and smooth, the outliers are indeed outliers because after \textit{n} iterations of removing discriminative features they are still separable from the main auhor's work.
+The main sense of unmasking is to iteratively remove the best features that distinguish two classes and observe the speed with which cross-validation accuracy of the again trained classifier drops.
+If the drop is slow and smooth, the outliers are indeed outliers because after $n$ iterations of removing discriminative features they are still separable from the main auhor's work.
 
 \citet{koppel-2011} used two staged approach in clustering of pre-segmented mixed biblical text written by two authors.
-First they used normalized cuts algorithm with cosine similarity to obtain initial clusters of segments which were represented only by normalized counts of synonymes from Hebrew synsets.
-Samples from initial clusers were separated in core and non-core samples via an iterative procedure, and core ones were labeled.
-SVM classifier was used to classify non-core samples, but now a bag-of-words feature vectors were used.
+First they used normalized cuts algorithm with cosine similarity to obtain initial clusters of segments which were represented only by normalized counts of synonyms from Hebrew synsets.
+Samples from initial clusers were separated into core and non-core samples via an iterative procedure, and the core ones were labeled.
+A SVM classifier was used to classify non-core samples, but now represented with bag-of-words feature vectors.
 The whole approach resulted with very good clusters.
 They also tried this method on an unsegmented case.
-Text was first splitted in a way that minimizes doubly-represented synonyms in segments and the same procedure was repeated.
+The text was first split in a way that minimizes doubly-represented synonyms in segments and the same procedure was repeated.
 The clustering performance was lower than in pre-segmented case.
@@
 Elliot, is needed for a good performance of their modified k-means algorithm in clustering of voices.
-Except often character, lexical and syntactic features, they used features such as average frequency in a large  external corpus \citep{brants-2006}.
-One of the most promising feature they considered is the centroid of 20 dimensional distributional vectors obtained by applying latent semantic analysis on a large web corpus \cite{landauer-1997}.
+Except common character, lexical and syntactic features, they used features such as average frequency in a large  external corpus \citep{brants-2006}.
+One of the most promising feature they considered is the centroid of $20$ dimensional distributional vectors obtained by applying latent semantic analysis on a large web corpus \cite{landauer-1997}.
 
 The works by \citet{kuznetsov-2016} and \citet{sittar-2016} were submitted on the PAN 2016 competition for three aforementioned tasks.
-For the task \textit{a}, \citet{kuznetsov-2016} trained a Gradient Boosting Regression Trees (GBRT) model on PAN 2011 dataset as a style change function used for threshold based outlier detection.
-Every sentence was vectorized using word frequencies, n-gram frequencies, punctuaiton symbols and the universal POS tags count, sentence length and mean length of sentence words.
+For the task \emph{a}, \citet{kuznetsov-2016} trained a Gradient Boosting Regression Trees (GBRT) model on PAN 2011 dataset as a style change function used for threshold based outlier detection.
+Every sentence was vectorized using word frequencies, $n$-gram frequencies, punctuaiton symbols and the universal POS tags count, sentence length and mean length of sentence words.
 The final input to the model was concatenation of center sentence vector and ones from context of size $\pm2$.
-In task \textit{b} they used a Hidden Markov Model with Gaussian Emissions for document segmentation over the same sentence scores from task \textit{a}.
-To estimate the unknown number of authors \textit{n} in task \textit{c}, they chose \textit{n} from 2 to 20 which maximizes their cluster discrepancy measure $Q(n)$.
+In task \emph{b} they used a Hidden Markov Model with Gaussian Emissions for document segmentation over the same sentence scores from task \emph{a}.
+To estimate the unknown number of authors $n$ in task \emph{c}, they chose $n\in\{2..20\}$ which maximizes their cluster discrepancy measure $Q(n)$.
 
-\citet{sittar-2016} used k-means algorthm to cluster \textit{ClustDist} scores of each sentence, where the number of groups was equal to the known number of authors in tasks \textit{a} and \textit{b}.
-In task \textit{c}, a number of groups was generated randomly.
-Although they defined a \textit{ClustDist} score for a single sentence as an average distance between current and every other sentence vector, which is again a similar concept like a style change function, in provided example they used only a sum of unknown distance measures.
-Fifteen features in total were used for sentence vectorization, including average word and sentence lengths, count and ratios of characters, digits upperpase letters, spaces and tabs.
+\citet{sittar-2016} used k-means algorithm to cluster \textit{ClustDist} scores of each sentence, where the number of groups was equal to the known number of authors in tasks \emph{a} and \emph{b}.
+In task \emph{c}, a number of groups was generated randomly.
+Although they defined a \emph{ClustDist} score for a single sentence as an average distance between current and every other sentence vector, which is again a similar concept like a style change function, in the provided example they used only a sum of unknown distance measures.
+$15$ features in total were used for sentence vectorization, including average word and sentence lengths, count and ratios of characters, digits uppercase letters, spaces and tabs.
 
-The most of described approaches combine supervised and usupervised methods and operate on the level of longer text segments or sentences.
-Since the style change in our tasks can occur even between two tokens in a same sentence, we wanted our model should be able to work on the token level.
-We were also inspired by \citet{brooke-2013} who said that a more radical approach would not separate described tasks in segmentation and clustering steps, but rather build an authorial segments that would also form good clusters.
-Instead of clustering tokens directly, we decided to cluster their vectorized stylistic contexts because they obviously contain more valuable sylistic information than tokens alone.
+The most of the described approaches combine supervised and unsupervised methods and operate on the level of longer text segments or sentences.
+Since the style change in our tasks can occur even between two tokens in the same sentence, we wanted our model to be able to work on the token level.
+We were also inspired by \citet{brooke-2013} who said that a more radical approach would not separate the described tasks in segmentation and clustering steps, but rather build authorial segments that would also form good clusters.
+Instead of clustering tokens directly, we decided to cluster their vectorized stylistic contexts because they obviously contain more valuable stylistic information than tokens alone.
 
-\section{Author diarization and intrinsic plagiarism detection}
+\section{Author diarization and intrinsic plagiarism detetion} \label{sec:author-diraization}
 % describe the problem
@@
 P_\mathrm{B^3} &= \sum_{i=1}^c \frac{1}{l(S_i)}\sum_{j=1}^{\hat{c}}
-	\sum_{(s,\hat{s})\in S_i\times \hat{S}_j} l(s\cap \hat{s})^2 \\
+	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2 \\
 R_\mathrm{B^3} &= \sum_{j=1}^{\hat{c}} \frac{1}{l(\hat{S}_j)}\sum_{i=1}^{c}
-	\sum_{(s,\hat{s})\in S_i\times \hat{S}_j} l(s\cap \hat{s})^2 \\
+	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2 \\
 F_\mathrm{B^3} &= \frac{2}{P_\mathrm{B^3}^{-1}+R_\mathrm{B^3}^{-1}}.
@@
 Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_b}, f_\mathrm{t}:\Phi_{n_b}\rightarrow \Phi_{n_t}, f_\mathrm{c}:\Phi_{n_t}\rightarrow C)$.
-Here $\Delta$ is the tokenized document domain as defined in section ((((((($\circ$))))))).
+Here $\Delta$ is the tokenized document domain as defined in section \ref{sec:author-diraization}.
 $\Phi_{n_b}$ and $\Phi_{n_t}$ are sets of variable-length sequences of feature vectors with dimension $n_b$ and $n_t$ respectively.
@@
 
-The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D\in\Delta$, (2) features are extracted for all tokens and their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (\mathbf{t}_i)_{i=1}^n = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n=|T_D|$, and (4) a segmentation $\hat{S}$ is generated based on the document $D$ and the sequence of predicted author labels.
+The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D\in\Delta$, (2) for all tokens, features are extracted from their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (\vect{t}_i)_{i=1}^n = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n=|T_D|$, and (4) a segmentation $\hat{S}$ is generated based on the document $D$ and the sequence of predicted author labels.
 
@@
 
-Let $(\mathbf{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be the sequence of basic feature vectors with elements from $\mathbb{R}^{n_b}$.
+Let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be the sequence of basic feature vectors with elements from $\mathbb{R}^{n_b}$.
 Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$.
-We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T$.
-Let $(\mathbf{t}_i)_{i=1}^n = (T(\mathbf{b}_i))_{i=1}^n = f_\mathrm{t}((\mathbf{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
+We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_b}\rightarrow\mathbb{R}^{n_t}$ with trainable parameters $\vect{\theta}_T$, i.e.
+we want to maximize segregation and compactness of groups of transformed feature vectors grouped by their target author label.
+Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
+We define the following loss in order to optimize the transformation $T$ for clusterability:
+\begin{equation}
+	L = L_\mathrm{c} + L_\mathrm{s}.
+\end{equation}
+Here $L_\mathrm{c}$ is the \emph{compactness loss} which is proportional to the average variance of groups and $L_\mathrm{s}$ the \emph{segregation loss} which penalizes centroids being too close to each other.
+Let $N_a$ represent the number of tokens associated with author $a$, i.e.
+$N_a = \sum_{i=1}^n[a_i=a]$, where, for $\varphi$ being a logical proposition $[\varphi]$ evaluates to either $1$ if $\varphi$ is true or $0$ otherwise.
+%, the following notation\footnote{It is called \emph{the Iverson bracket}.} is introduced:
+%\begin{equation}
+%[\varphi] = \begin{cases}
+%	1, & \varphi\equiv\top, \\
+%	0, & \varphi\equiv\bot.
+%\end{cases}
+%\end{equation}
+Let $\vect{m}_a$ represent the current centroid of the transformed vectors:
+\begin{equation}
+\vect{m}_a = \frac{1}{N_a}\sum_{i=1}^n T(\vect{b}_i)
+\end{equation}	
+We define the components of the loss: 
+\begin{align}
+	L_\mathrm{c} &= \sum_{a=0}^{c}\frac{1}{N_a} 
+		\sum_{i=1}^{n} \| T(\vect{b}_i)-\vect{m}_{a}\|^2 [a_i=a], \\
+	L_\mathrm{s} &= \frac{2}{c}\sum_{a=0}^{c}\sum_{b=a+1}^{c} \|\vect{m}_a-\vect{m}_b\|^{-2}.
+\end{align}
+The \emph{compactness loss} $L_\mathrm{c}$ is a weighted sum of variances within sets of feature vectors grouped by author.
+The \emph{segregation loss}  $L_\mathrm{s}$ is proportional to the sum of magnitudes (not magnitude of the sum) of forces between $c$ equally charged particles each located at one of the centroids.
+By minimizing the average loss (the error) across all documents in the training dataset with respect to the parameters of the transformation $\vect{\theta}_T$ we hope to benefit the clustering algorithm.
+Instead of squared $L^2$ distance, some other distance measure may be used.
 

### 2017-05-31 software/test-pipeline.py

@@ -16,7 +16,7 @@ dataset_dirs = [
 ]
 
 
-def evaluate(params: dict, dataset_index: int, cache_dir=None):
+def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True):
     features_file_name = 'inpladesys/models/basic_feature_extraction/features_files/cng-sw-bow.json'
     random_state = 0xBeeFeed
     pl_params = dict()
@@ -24,7 +24,7 @@ def evaluate(params: dict, dataset_index: int, cache_dir=None):
         features_file_name=features_file_name,
         context_size=params['context_size'])
     from inpladesys.models.feature_transformation import SimpleGroupRepelFeatureTransformer
-    if False:
+    if not linear:
         pl_params['feature_transformer'] = SimpleGroupRepelFeatureTransformer(
             reinitialize_on_fit=False,
             iteration_count=params['gr-iteration_count'],
@@ -94,9 +94,12 @@ params['gr-iteration_count'] = 40  # 60  #20simple
 params['basic_feature_extender'] = 'f2'
 
 # cache_dir example "ce100-bow100-sw--ctx120--f21"
-evaluate(params, 2, cache_dir="cng120-bow120-sw--ctx{}--f2-s".format(
-    params['context_size'],
-    1 if params['basic_feature_extender'] == 'f2' else 0))
+evaluate(params,
+         2,
+         cache_dir="cng120-bow120-sw--ctx{}--f2-s".format(
+            params['context_size'],
+            1 if params['basic_feature_extender'] == 'f2' else 0),
+         linear=True)
 
 # Task c:
 # 1) output_dimension=16, 2 groups, 100 iter, no f**2 , linear: 0.53

### 2017-05-31 paper/paper.tex
Some small modifications

@@
 Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$.
-A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ represents a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each is assigned the same label.
+A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ represents a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is assigned the same label.
 For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
@@
 % details for each component
-\paragraph{Tokenization.} As a preprocessing step, we tokenized each document $D$ with \texttt{nltk}\footnote{\texttt{http://www.nltk.org}} toolkit, to obtain a set of tokens $T_D$.
-We also performed Part of Speech tagging with the same tool, to speed up a basic feature extraction which we describe below.
+\paragraph{Tokenization.} As a preprocessing step, we tokenized each document $D$ using NLTK\footnote{\url{http://www.nltk.org}} to obtain a set of tokens $T_D$.
+We also performed part-of-speech tagging with the same tool, to speed up basic feature extraction which we describe below.
 We didn't use other preprocessing techniques such as lemmatization, stemming and stop word removal because they would take away a lot of stylometric data from text \cite{stamatatos-2009a}.
-The final output from tokenization step was a finite sequence $\{(t_i, o_i, l(t_i), POS_i)\}_{i=1}^n$ where $o_i$ is the offset of token $t_i$, $l(t_i)$ its length in characters and $POS_i$ its POS tag.
+The final output from the tokenization step was a finite sequence $\{(t_i, o_i, l(t_i), \mathit{POS}_i)\}_{i=1}^n$ where $o_i$ is the offset of token $t_i$, $l(t_i)$ its length in characters and $\mathit{POS}_i$ its POS tag.
 

### 2017-05-31 paper/paper.tex
Initial version of chapter 4.

@@
 \paragraph{Basic feature extraction.} 
-We defined the stylistic context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-c}^{i-1} \cup \{t_k\}_{k=i+1}^{i+c}$ where $c$ is a context size.
+We defined the stylistic context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-cs}^{i-1} \cup \{t_k\}_{k=i+1}^{i+cs}$ where $cs$ is a context size.
 From each context we extracted the most used stylometric features which we found in previous work.
@@
 According to \citet{stamatatos-2009a}, sometimes also called \textit{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
-They are used unconciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' {burrows-1987,argamon-2005}.
-We used frequencies of 156 english stop words available in \texttt{nltk}.
+They are used unconciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' \citep{burrows-1987,argamon-2005}.
+We used frequencies of 156 english stop words available in \texttt{NLTK}.
 	\item \textit{Special characters}.
-We used counts of all character sequences which satisfied a regular expression defined as [REGEX].
-Although character n-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose.
-\citet{koppel-2009} mentioned that authors can have different punctuation habbits.
+We used counts of all character sequences which satisfied a regular expression defined as \verb/[^\\w]{1,4}/.
+Although character $n$-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose since \citet{koppel-2009} mentioned that authors can have different punctuation habbits.
 	\item \textit{POS tag counts}.
@@
 We included this feature because it boosted performance of our initial testing, even without words been previously stemmed or lemmatized (stop words were excluded).
-Vocabulary had a maximum of 100 words.
+Counts of maximum of 100 unigrams were used.
 	\item \textit{Type-token ratio}.
@@
 
-Differences between the 2 model variants....
-
-basic features
+We implemented two variants of our final model, first with only a basic feature extractor $f_\mathrm{b}$ whether in second feature transformation $f_\mathrm{t}$ was used.
+For the first variant, where only a basic feature extractor $f_\mathrm{b}$ was used, we extracted features for each document separately.
+In the variant with both basic extractor $f_\mathrm{b}$ and transformation $f_\mathrm{t}$, all documents were concatenated to a single one from which basic and transformed feature vectors were obtained.
+In both approaches features were extracted from a sliding window which included a context of each token.
 
@@
 
-scaling
+scaling!!!!!!
 
@@
 
-clustering algorithms
+The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens.
+The number of clusters was equal to the number of authors in tasks $a$ and $b$, but in task $c$ it was unknown.
+We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org/stable/}} Python toolkit in all tasks.
+For tasks $a$ and $b$ we propose hierarchical agglomerative clustering, and for task $c$ DBSCAN algorithm which estimates the number clusters automatically.
+The reason of choosing that algorithms is described below.
 
 k-means HAC DBSCAN auto-k-means
-
-\paragraph{Segmentation generation.} something short
-
-features
-
-differences: fixed features + transformation vs document-dependent features
 
@@
 1
+
 baselines
+
 repo link
+
 Mention cofidences.
+
+feature init test
 
@@
 setup
+
+\paragraph{Segmentation generation.} something short
+
+features
+
+differences: fixed features + transformation vs document-dependent features
 

### 2017-06-01 paper/paper.tex
Started intro to chapter 5.

@@
 
-We implemented two variants of our final model, first with only a basic feature extractor $f_\mathrm{b}$ whether in second feature transformation $f_\mathrm{t}$ was used.
+We implemented two variants of our final model.
+First is with only a basic feature extractor $f_\mathrm{b}$, whether in second the feature transformation $f_\mathrm{t}$ was used.
 For the first variant, where only a basic feature extractor $f_\mathrm{b}$ was used, we extracted features for each document separately.
 In the variant with both basic extractor $f_\mathrm{b}$ and transformation $f_\mathrm{t}$, all documents were concatenated to a single one from which basic and transformed feature vectors were obtained.
-In both approaches features were extracted from a sliding window which included a context of each token.
+In both approaches basic features were extracted from a sliding window which moved from token to token and included a context of each token.
+In the rest of the paper we refer to the first variant as model A, and to the second as model B.
 
@@
 The number of clusters was equal to the number of authors in tasks $a$ and $b$, but in task $c$ it was unknown.
-We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org/stable/}} Python toolkit in all tasks.
-For tasks $a$ and $b$ we propose hierarchical agglomerative clustering, and for task $c$ DBSCAN algorithm which estimates the number clusters automatically.
-The reason of choosing that algorithms is described below.
+We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org/stable/}} Python toolkit by \citet{scikit-learn} in all tasks.
+In the first variant of our approach for tasks $a$ and $b$ we propose hierarchical agglomerative clustering, and for task $c$ DBSCAN algorithm which estimates the number of clusters automatically.
+In the second variant we used k-means for clustering in tasks $a$ and $b$, and our modification of k-means, which we called AutoKmeans in task $c$.
+The reason of choosing that algorithms is described in chapter ?????
+5 ????.
 
@@
 feature init test
+
+We performed initial testing of usefulness of all features except accidentally wrong implemented type-token ratio which was added afterwards.
+For testing purposes we used k-means algorithm with default settings available in \texttt{scikit-learn} and all documents from task $b$ dataset.
+As we added feature by feature, BCubed precision was higher so we decided to extract all features in all tasks.
+We don't know the exact impact of wrongly implemented type- token ratio.
+Instead of the context's vocabulary size, we divided the size of document's vocabulary with the context size so this feature had the same value in all vectors.
+
+Five baseline models were defined for evaluation purposes.
+First baseline, \textit{DummySingleAuthorDiarizer} always assigned all tokens to only one cluster, assuming that text is written by a single author.
+As we will later describe, this baseline model behaved very competitive.
+The second baseline was \textit{DummyStohasticAuthorDiarizer} which generated a random number between
 

### 2017-06-01 paper/paper.tex
Added some text about feature transfomation and results

--- 2017-05-31 paper/paper.tex
@@
 \newcommand{\matr}[1]{\vect{#1}}
+\newcommand{\transpose}{\mathsf T}
 
@@
 	\caption{Basic characteristics of training datasets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
-	\label{table-1}
+	\label{tab:dataset-characteristics}
 	\begin{center}
@@
 Test datasets are currently not publicly available and we could not use them for evaluation of our approach.
-Some basic characteristics of the training datasets are shown in Table \ref{table-1}.
+Some basic characteristics of the training datasets are shown in Table \ref{tab:dataset-characteristics}.
 
@@
 Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$.
-A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ represents a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is assigned the same label.
+A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ is a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is associated with the same author label.
 For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
@@
 
-\paragraph{Feature transformation.} Differences between the 2 model variants. Training.
+\paragraph{Feature transformation.} We develop two variants of our model which are mainly differentiated by the application of a trainable feature transformation requiring fixed basic feature space as opposed to variable feature space with features that can be more document-specific.
 
-id
-
-scaling
-
-concatenation with squared features
-
-transformation trained via SGD
-
-Let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be the sequence of basic feature vectors with elements from $\mathbb{R}^{n_b}$.
+Let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be a sequence of basic feature vectors and $(\vect{b}_i')_{i=1}^n$ the corresponding sequence of potentially preprocessed basic feature vectors with elements from $\mathbb{R}^{n_{b}'}$.
 Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$.
-We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_b}\rightarrow\mathbb{R}^{n_t}$ with trainable parameters $\vect{\theta}_T$, i.e.
+We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_b'}\rightarrow\mathbb{R}^{n_t}$ with trainable parameters $\vect{\theta}_T$, i.e.
 we want to maximize segregation and compactness of groups of transformed feature vectors grouped by their target author label.
-Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
-We define the following loss in order to optimize the transformation $T$ for clusterability:
+Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i'))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
+We define the following loss in order to optimize the transformation $T$:
 \begin{equation}
-	L = L_\mathrm{c} + L_\mathrm{s}.
+	L = \alpha L_\mathrm{c} + (1-\alpha)L_\mathrm{s}
 \end{equation}
-Here $L_\mathrm{c}$ is the \emph{compactness loss} which is proportional to the average variance of groups and $L_\mathrm{s}$ the \emph{segregation loss} which penalizes centroids being too close to each other.
+with $\alpha$ chosen to be $0.5$.
+Here $L_\mathrm{c}$ is the \emph{compactness loss} and $L_\mathrm{s}$ the \emph{segregation loss}.
+$L_\mathrm{c}$ is proportional to the average variance of groups, and $L_\mathrm{s}$ penalizes centroids being too close to each other.
 Let $N_a$ represent the number of tokens associated with author $a$, i.e.
@@
 %\end{equation}
-Let $\vect{m}_a$ represent the current centroid of the transformed vectors:
+Let $\vect{\mu}_a$ represent the current centroid of the transformed feature vectors associated with the author label $a$:
 \begin{equation}
-\vect{m}_a = \frac{1}{N_a}\sum_{i=1}^n T(\vect{b}_i)
+\vect{\mu}_a = \frac{1}{N_a}\sum_{i=1}^n T(\vect{b}_i')[a_i=a]
 \end{equation}	
@@
 	L_\mathrm{c} &= \sum_{a=0}^{c}\frac{1}{N_a} 
-		\sum_{i=1}^{n} \| T(\vect{b}_i)-\vect{m}_{a}\|^2 [a_i=a], \\
-	L_\mathrm{s} &= \frac{2}{c}\sum_{a=0}^{c}\sum_{b=a+1}^{c} \|\vect{m}_a-\vect{m}_b\|^{-2}.
+		\sum_{i=1}^{n} \| T(\vect{b}_i')-\vect{\mu}_{a}\|^2 [a_i=a], \\
+	L_\mathrm{s} &= \frac{2}{c}\sum_{a=0}^{c}\sum_{b=a+1}^{c} \|\vect{\mu}_a-\vect{\mu}_b\|^{-2}.
 \end{align}
-The \emph{compactness loss} $L_\mathrm{c}$ is a weighted sum of variances within sets of feature vectors grouped by author.
+The \emph{compactness loss} $L_\mathrm{c}$ is a weighted sum of within-group variances.
 The \emph{segregation loss}  $L_\mathrm{s}$ is proportional to the sum of magnitudes (not magnitude of the sum) of forces between $c$ equally charged particles each located at one of the centroids.
@@
 Instead of squared $L^2$ distance, some other distance measure may be used.
+Also, the way of combining the two losses was somewhat arbitrarily chosen as well as the segregation loss.
+For the transformation $T$ we have tried a nonlinear transformations represented as neural networks with one or more hidden layers.
+We didn't explore it much because it was slower and didn't give as good results as a linear transformation or an elementwise product with a weight vector:
+\begin{align}
+	T_1(\vect{x}) &= \matr{W}\vect{x}, \quad \vect{\theta}_{T_1} = \matr{W}, \\
+	T_2(\vect{x}) &= \vect{w}\odot\vect{x}, \quad \vect{\theta}_{T_2} = \vect{w}.
+\end{align}
+Before applying the transformations, basic feature vectors are preprocessed by concatanating each with the vector of its squared elements:
+\begin{equation}
+	\vect{b_i'} = (\vect{b_i}^\transpose, (\vect{b_i}\odot\vect{b_i})^\transpose)^\transpose, \quad i\in \{1..n\}.
+\end{equation}
+The transformation is implemented using TensorFlow\footnote{TensorFlow link}.
+It is trained on-line (one document per optimization step) using RMSProp\footnote{RMSProp} with default parameters and learning rate.
 
@@
 
-features
+\section{Experimental results}
 
-differences: fixed features + transformation vs document-dependent features
+For experiments, we use the three PAN 2016 training datasets.
+The test datasets used in the competition have not been made publicly available.
+Therefore, our evaluation results might be only moderately comparable to the results of other systems.
 
-\section{Experimental results}
+We have created two blind baselines and a baseline that tries to really predict the authorial parts based on some simple features.
+The first blind baseline predicts the whole document to have been written by a single author or, in the case of intrinsic plagiarism detection, labels the whole document as plagiarism.
+The second blind baseline learns the average lengths of
+
+\subsection{Experimantal setup}
+
+\subsection{Intrinsic plagiarism detection results}
+
+\subsection{Author diarization results}
 

### 2017-06-01 software/inpladesys/models/feature_transformation/grouprepel_feature_transformer.py

@@ -175,6 +175,7 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
         # 0.2 * tf.reduce_mean(tf.reduce_sum(centroids**2, axis=1)) + r_loss
         # loss = 1/(1/group_loss + 1/centroid_loss)
 
+        #optimizer = tf.train.RMSPropOptimizer(learning_rate=learning_rate, decay=0.9)
         optimizer = tf.train.RMSPropOptimizer(learning_rate=learning_rate, decay=0.9)
         train_step = optimizer.minimize(loss)
 

### 2017-06-01 software/inpladesys/models/feature_transformation/simple_grouprepel_feature_transformer.py

@@ -130,9 +130,9 @@ class SimpleGroupRepelFeatureTransformer(AbstractFeatureTransformer):
 
         group_loss = get_group_loss(y, labels, centroids, centroid_count)
         centroid_loss = get_centroid_loss(centroids, centroid_count)
-        #r_loss = sum(tf.reduce_mean(p ** 2) for p in r_params)
+        # r_loss = sum(tf.reduce_mean(p ** 2) for p in r_params)
 
-        loss = centroid_loss + group_loss #+ 0.1 * r_loss  # +
+        loss = centroid_loss + group_loss  # + 0.1 * r_loss  # +
         # 0.2 * tf.reduce_mean(tf.reduce_sum(centroids**2, axis=1)) + r_loss
         # loss = 1/(1/group_loss + 1/centroid_loss)
 

### 2017-06-01 software/test-pipeline.py

@@ -16,7 +16,7 @@ dataset_dirs = [
 ]
 
 
-def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True):
+def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True, test=False):
     features_file_name = 'inpladesys/models/basic_feature_extraction/features_files/cng-sw-bow.json'
     random_state = 0xBeeFeed
     pl_params = dict()
@@ -36,7 +36,7 @@ def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True):
             reinitialize_on_fit=False,
             nonlinear_layer_count=params['gr-nonlinear_layer_count'],
             iteration_count=params['gr-iteration_count'],
-            learning_rate=1e-3,
+            learning_rate=5e-4,
             random_state=random_state)
     print(str(pl_params['feature_transformer']))
     pl_params['clusterer'] = AutoKMeans(min_clusters=2, max_clusters=2) if dataset_index != 1 else AutoKMeans(2, 2)
@@ -58,14 +58,18 @@ def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True):
     print("Loading dataset...")
     dataset = Pan16DatasetLoader(dataset_dirs[dataset_index]).load_dataset()
     dataset.shuffle(random_state=random_state)
-    train_validate_data, _ = dataset.split(0, int(0.7 * dataset.size))
+    train_validate_data, test_data = dataset.split(0, int(0.7 * dataset.size))
     train_data, validate_data = train_validate_data.split(0, int(0.7 * train_validate_data.size))
+
+    if test:
+        train_data = train_validate_data
+        validate_data = test_data
 
     print("Training...")
     pad.train(train_data)
 
     # validate_data = train_data
-    print("Evaluating on validation data...")
+    print("Evaluating on {} data...".format("TEST" if test else "VALIDATION"))
     hs = pad.predict(validate_data.documents,
                      author_counts=[s.author_count for d, s in validate_data] if dataset_index == 1 else None)
     ys = validate_data.segmentations
@@ -90,16 +94,16 @@ params = dict()
 params['context_size'] = 120
 params['gr_output_dimension'] = 40
[…]

### 2017-06-01 paper/paper.tex
Merge

@@
 
-Differences between the 2 model variants....
-
-basic features
+We implemented two variants of our final model.
+First is with only a basic feature extractor $f_\mathrm{b}$, whether in second the feature transformation $f_\mathrm{t}$ was used.
+For the first variant, where only a basic feature extractor $f_\mathrm{b}$ was used, we extracted features for each document separately.
+In the variant with both basic extractor $f_\mathrm{b}$ and transformation $f_\mathrm{t}$, all documents were concatenated to a single one from which basic and transformed feature vectors were obtained.
+In both approaches basic features were extracted from a sliding window which moved from token to token and included a context of each token.
+In the rest of the paper we refer to the first variant as model A, and to the second as model B.
 
@@
 \end{equation}
-The transformation is implemented using TensorFlow\footnote{TensorFlow link}.
-It is trained on-line (one document per optimization step) using RMSProp\footnote{RMSProp} with default parameters and learning rate.
+The transformation is implemented using TensorFlow\footnote{\url{https://www.tensorflow.org}}.
+It is trained on-line (one document per optimization step) using RMSProp \citep{tielman-2012} with default parameters and learning rate $5\times 10^{-4}$.
 
@@
 
-clustering algorithms
+The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens.
+The number of clusters was equal to the number of authors in tasks \emph{a} and \emph{b}, but in task \emph{c} it was unknown.
+We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks.
+In the first variant of our approach for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
+In the second variant we used k-means for clustering in all tasks, and tried our modification of k-means, which we called Auto-k-means in task \emph{c}.
+The reason for choosing those algorithms is described in section \ref{sec:experimental-results}.
 
-k-means HAC DBSCAN auto-k-means
+% TODO k-means HAC DBSCAN auto-k-means
 
-\paragraph{Segmentation generation.} something short
+\section{Experimental results} \label{sec:experimental-results}
 
-\section{Experimental results}
+Mention cofidences.
 
-For experiments, we use the three PAN 2016 training datasets.
+feature init test
+
+repo link
+
+For experiments, we used the three PAN 2016 training datasets.
 The test datasets used in the competition have not been made publicly available.
@@
 
-\subsection{Experimantal setup}
+We performed initial testing of usefulness of all features except accidentally wrongly implemented type-token ratio which was added afterwards.
+For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the datased for task \emph{b}.
+As we were adding feature by feature, BCubed precision was becoming higher so we decided to  all features in all tasks.
+We don't know the exact impact of the wrongly implemented type-token ratio feature.
+Instead of the context's vocabulary size, we divided the size of document's vocabulary with the context size so this feature had the same value in all vectors.
+
+Five baseline models were defined for evaluation purposes.
+The first baseline, \textit{DummySingleAuthorDiarizer} always assigns all tokens to only one cluster, assuming that the text is written by a single author.
+As we will later describe, this baseline model behaved very competitive.
+The second baseline was \textit{DummyStohasticAuthorDiarizer} which generated a random number between
+
+\subsection{Experimental setup}
 
@@
 \subsection{Author diarization results}
-
-1
-baselines
-repo link
-Mention cofidences.
 

### 2017-06-01 paper/paper.tex
Chapter 4 finished.

@@
 % details for each component
-\paragraph{Tokenization.} As a preprocessing step, we tokenized each document $D$ using NLTK\footnote{\url{http://www.nltk.org}} to obtain a set of tokens $T_D$.
+\paragraph{Tokenization.} As a preprocessing step, we tokenized each document $D$ using \texttt{NLTK}\footnote{\url{http://www.nltk.org}} by \citet{bird-2009} to obtain a set of tokens $T_D$.
 We also performed part-of-speech tagging with the same tool, to speed up basic feature extraction which we describe below.
@@
 	\item \textit{Type-token ratio}.
-We wanted to use that feature to measure the vocabulary richness in a token's context, but after we finished with performance evaluations we realized that there was a bug in implementation and that feature did not contribute to overal results.
+We wanted to use that feature to measure the vocabulary richness in a token's context, but after we finished with performance evaluations we realized that there was a bug in implementation and its impact on final results was unknown to us.
 The feature should be calculated as the ratio of vocabulary size and total number of tokens of the text \citep{stamatatos-2009a}.
@@
 
-We implemented two variants of our final model.
-First is with only a basic feature extractor $f_\mathrm{b}$, whether in second the feature transformation $f_\mathrm{t}$ was used.
-For the first variant, where only a basic feature extractor $f_\mathrm{b}$ was used, we extracted features for each document separately.
-In the variant with both basic extractor $f_\mathrm{b}$ and transformation $f_\mathrm{t}$, all documents were concatenated to a single one from which basic and transformed feature vectors were obtained.
-In both approaches basic features were extracted from a sliding window which moved from token to token and included a context of each token.
+\paragraph{Feature transformation.}
+
+ We develop two variants of our model which are mainly differentiated by the application of a trainable feature transformation requiring fixed basic feature space as opposed to variable feature space with features that can be more document-specific.
+
+ First variant uses only a basic feature extractor $f_\mathrm{b}$, whether in second the feature transformation $f_\mathrm{t}$ is used.
+In the first variant we extract features for each document separately and scale features to zero mean and unit variance.
+In the variant with both basic extractor $f_\mathrm{b}$ and transformation $f_\mathrm{t}$, all documents are concatenated to a single one from which basic and transformed feature vectors are obtained, but without standardization.
+In both approaches basic features are extracted from a sliding window which moves from token to token and includes a context of each token.
 In the rest of the paper we refer to the first variant as model A, and to the second as model B.
 
-\paragraph{Feature transformation.} We develop two variants of our model which are mainly differentiated by the application of a trainable feature transformation requiring fixed basic feature space as opposed to variable feature space with features that can be more document-specific.
-
-Let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be a sequence of basic feature vectors and $(\vect{b}_i')_{i=1}^n$ the corresponding sequence of potentially preprocessed basic feature vectors with elements from $\mathbb{R}^{n_{b}'}$.
+In model B, let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be a sequence of basic feature vectors and $(\vect{b}_i')_{i=1}^n$ the corresponding sequence of potentially preprocessed basic feature vectors with elements from $\mathbb{R}^{n_{b}'}$.
 Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$.
@@
 In the second variant we used k-means for clustering in all tasks, and tried our modification of k-means, which we called Auto-k-means in task \emph{c}.
-The reason for choosing those algorithms is described in section \ref{sec:experimental-results}.
+The reason for choosing those algorithms is described in section \ref{sec:experimental-results}
 

### 2017-06-01 paper/paper.tex
Merged results introduction, started making result tables, safety push due to weather

@@
 % additional packages
+\usepackage{multirow}
+\usepackage{makecell}
 \usepackage{enumitem}
-\usepackage{makecell}
 \usepackage[hyphens]{url}
@@
 \begin{align}
-P_\mathrm{B^3} &= \sum_{i=1}^c \frac{1}{l(S_i)}\sum_{j=1}^{\hat{c}}
+P_\mathrm{\mathrm{B}^3} &= \sum_{i=1}^c \frac{1}{l(S_i)}\sum_{j=1}^{\hat{c}}
 	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2 \\
-R_\mathrm{B^3} &= \sum_{j=1}^{\hat{c}} \frac{1}{l(\hat{S}_j)}\sum_{i=1}^{c}
+R_\mathrm{\mathrm{B}^3} &= \sum_{j=1}^{\hat{c}} \frac{1}{l(\hat{S}_j)}\sum_{i=1}^{c}
 	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2 \\
-F_\mathrm{B^3} &= \frac{2}{P_\mathrm{B^3}^{-1}+R_\mathrm{B^3}^{-1}}.
+F_\mathrm{\mathrm{B}^3} &= \frac{2}{P_\mathrm{\mathrm{B}^3}^{-1}+R_\mathrm{\mathrm{B}^3}^{-1}}.
 \end{align}
@@
 \section{The proposed approach}
-% clustering, sliding window
-% pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
-% define the pipeline formally P = (f_p: d\times->t, f_b: t->\phi, f_t: \phi->\phi', c: \phi'->labels, f_s: labels\times d->s)
-% describe GroupRepel loss, describe AutoKMeans, 
-% clustering metric
 
@@
 
-We have created two blind baselines and a baseline that tries to really predict the authorial parts based on some simple features.
-The first blind baseline predicts the whole document to have been written by a single author or, in the case of intrinsic plagiarism detection, labels the whole document as plagiarism.
-The second blind baseline learns the average lengths of
+Three baseline models were defined for evaluation purposes.
+The first baseline, \emph{single-author dummy baseline}, always assigns the whole document a single author label, or, in the case of intrinsic plagiarism detection, it labels the whole document as plagiarism.
+The second baseline, \emph{stochastic dummy baseline}, learns the average total lengths of authorial parts over all documents giving the most common author label $0$ and the least common author the largest label.
+For prediction, by modelling a Markov chain, it generates segmentations with similar label frequencies and predefined expected lengths.
+As we will later describe, these baseline models seem to behaved quite competitively.
 
-We performed initial testing of usefulness of all features except accidentally wrongly implemented type-token ratio which was added afterwards.
-For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the datased for task \emph{b}.
+We performed initial testing of usefulness of all features except for the accidentally wrongly implemented type-token ratio which was added afterwards.
+For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the dataset for task \emph{b}.
 As we were adding feature by feature, BCubed precision was becoming higher so we decided to  all features in all tasks.
@@
 Instead of the context's vocabulary size, we divided the size of document's vocabulary with the context size so this feature had the same value in all vectors.
-
-Five baseline models were defined for evaluation purposes.
-The first baseline, \textit{DummySingleAuthorDiarizer} always assigns all tokens to only one cluster, assuming that the text is written by a single author.
-As we will later describe, this baseline model behaved very competitive.
-The second baseline was \textit{DummyStohasticAuthorDiarizer} which generated a random number between
 
@@
 
+\begin{table*}
+	\caption{Results on the intrinsic plagiarism detection task.}
+	\label{tab:narrow-table}
+	\begin{center}
+		\begin{tabular}{l|ccc|ccc}
+			\toprule
+			Method & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
+			\midrule
+			single-author BL 		& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
+			stochastic BL 			& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
+			simple BL 				& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
+			\midrule
+			\citet{kuznetsov-2016} 	& 0.19 & 0.29 & 0.22 & 0.15 & 0.28 & 0.17 \\
+			\citet{sittar-2016} 	& 0.07 & 0.14 & 0.08 & 0.10 & 0.14 & 0.10 \\
+			\midrule			
+			model A & 0 & 1 & 2 \\			
+			model B (weighting) & 0 & 1 & 2 \\			
+			model B (linear) & 0 & 1 & 2 \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+\end{table*}
+
 \subsection{Author diarization results}
+
+\begin{table*}
+	\caption{Results on the author diarization task with known number of authors.}
+	\label{tab:narrow-table}
+	\begin{center}
+		\begin{tabular}{l|ccc}
+			\toprule
+			Method & $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
+			\midrule
+			single-author baseline & 0 & 1 & 2 \\
+			stochastic baseline & 0 & 1 & 2 \\
+			simple baseline & 0 & 1 & 2 \\
+			\midrule
+			\citet{kuznetsov-2016} \\
+			\citet{sittar-2016} \\
+			\midrule			
+			model A & 0 & 1 & 2 \\			
+			model B (weighting) & 0 & 1 & 2 \\			
+			model B (linear) & 0 & 1 & 2 \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+\end{table*}
 
@@
 
-If suitable, you can include the \textit{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.
-
-\begin{table}
-	\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
-	\label{tab:narrow-table}
-	\begin{center}
-		\begin{tabular}{c|ccc|ccc}
-			\toprule
-			Model & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
-			\midrule
-			Dummy & 0 & 1 & 2 \\
-			One & 0 & 1 & 2 \\
-			One & 0 & 1 & 2 \\
-			\midrule
-			One & 0 & 1 & 2 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-\end{table}
+If suitable, you can include the \emph{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.
 

### 2017-06-01 software/test-pipeline.py

@@ -99,11 +99,11 @@ params['basic_feature_extender'] = 'f2'
 
 # cache_dir example "ce100-bow100-sw--ctx120--f21"
 evaluate(params,
-         1,
+         0,
          cache_dir="cng120-bow120-sw--ctx{}--f2-s".format(
             params['context_size'],
             1 if params['basic_feature_extender'] == 'f2' else 0),
-         linear=True, test=False)
+         linear=False, test=True)
 
 # Task c:
 # 1) output_dimension=16, 2 groups, 100 iter, no f**2 , linear: 0.53

### 2017-06-01 paper/paper.tex
Another safety push

@@
 			\midrule
-			single-author BL 		& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
-			stochastic BL 			& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
-			simple BL 				& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
+			single-author BL 		& 0.13 & 1.00 & 0.22 & 0.13 & 1.00 & 0.22 \\
+			stochastic BL 			& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
+			simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
 			\midrule
@@
 			\midrule			
-			model A & 0 & 1 & 2 \\			
-			model B (weighting) & 0 & 1 & 2 \\			
-			model B (linear) & 0 & 1 & 2 \\
+			model A 				&  &  &  &  &  & \\			
+			model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
+			model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
 			\bottomrule

### 2017-06-01 software/test-pipeline.py

@@ -94,7 +94,7 @@ params = dict()
 params['context_size'] = 120
 params['gr_output_dimension'] = 40
 params['gr-nonlinear_layer_count'] = 0
-params['gr-iteration_count'] = 40  # 40 linear, 20simple
+params['gr-iteration_count'] = 20  # 40 linear, 20simple
 params['basic_feature_extender'] = 'f2'
 
 # cache_dir example "ce100-bow100-sw--ctx120--f21"
@@ -139,7 +139,35 @@ evaluate(params,
 
 
 # TEST a
+""" Linear
+p_val = 0.016663885265493093 < threshold = 0.05
+<class 'inpladesys.evaluation.MicroScorer'>
+[ 0.14527152  0.24281232  0.16747193] +- [ 0.21112588  0.35148086  0.23396387]
 
+p_val = 0.0015490432235609115 < threshold = 0.05
+<class 'inpladesys.evaluation.MacroScorer'>
+[ 0.14157719  0.23100395  0.1554029 ] +- [ 0.21103196  0.33617561  0.2228556 ]
+
+Standard error: 0.0162901797368
+95.0% confidence interval: (0.72104178862354851, 0.78879635525106395)
+<class 'inpladesys.evaluation.BCubedScorer'>
+[ 0.80035133  0.72762716  0.75491907] +- [ 0.07229311  0.1225945   0.07465098]
+"""
+""" Weights
+p_val = 0.017572886789561672 < threshold = 0.05
+<class 'inpladesys.evaluation.MicroScorer'>
+[ 0.1887609   0.31292746  0.21287538] +- [ 0.2447085   0.36239388  0.23431014]
+
+p_val = 0.04968384152747822 < threshold = 0.05
+<class 'inpladesys.evaluation.MacroScorer'>
+[ 0.18741912  0.28540267  0.20263513] +- [ 0.24470063  0.34040655  0.22525467]
+
+Mean: 0.743040770277
+Standard error: 0.0173619164866
+95.0% confidence interval: (0.70693468838061457, 0.7791468521737176)
+<class 'inpladesys.evaluation.BCubedScorer'>
+[ 0.80453731  0.6974933   0.74304077] +- [ 0.06018195  0.11452849  0.0795623 ]
+"""
 
 # TEST b
 """ Linear

### 2017-06-01 paper/paper.tex
Reformatted parts of "The proposed approach"

--- 2017-06-01 paper/paper.tex
@@
 
+% TODO: replace model A with Model A, for B as well
+% TODO: replace $n$-gram and \emph{n}-gram with n-gram, as it is common in literature
+% TODO: suggestion: remove \texttt-s 
+% TODO: convert Related work to present
+% TODO: change \texit-s ti \emph-s
+% TODO: explain BFE training in The proposed approach
+
 \begin{document}
@@
 \section{Introduction}
-In this paper we will focus on the author diarization task proposed on PAN 2016 competition\footnote{\url{http://pan.webis.de/clef16/pan16-web/author-identification.html}}.
+In this paper we will focus on the author diarization task proposed on the PAN 2016 competition\footnote{\url{http://pan.webis.de/clef16/pan16-web/author-identification.html}}.
 The aim of this task is to decompose a document into its authorial parts, i.e.
@@
 The goal of this task is to find plagiarized parts of a document in which at least $70\%$ of text is written by main author and the rest by one or more other authors.
-The term \textit{intrinsic} means that a decision whether plagiarized parts exist has to be made only by analysing a given document, without any comparisons with external sources.
+The term \emph{intrinsic} means that a decision whether a part of the document is plagiarized has to be made only by analysing the given document, without any comparisons with external sources.
 In the rest of the paper we refer to this subtask as task \emph{a}.
@@
 To find them, they estimated probability distributions of various stylistic features for the target class and outliers.
-Then a naive Bayes' algorithm was applied to feature vectors whose values lied outside the predefined uncertainity intervals.
+Then a naive Bayes' algorithm was applied to feature vectors whose values lied outside the predefined uncertainty intervals.
 Additional outlier post-processing methods were also tested.
@@
 The main sense of unmasking is to iteratively remove the best features that distinguish two classes and observe the speed with which cross-validation accuracy of the again trained classifier drops.
-If the drop is slow and smooth, the outliers are indeed outliers because after $n$ iterations of removing discriminative features they are still separable from the main auhor's work.
+If the drop is slow and smooth, the outliers are indeed outliers because after $n$ iterations of removing discriminative features they are still separable from the main author's work.
 
@@
 First they used normalized cuts algorithm with cosine similarity to obtain initial clusters of segments which were represented only by normalized counts of synonyms from Hebrew synsets.
-Samples from initial clusers were separated into core and non-core samples via an iterative procedure, and the core ones were labeled.
-A SVM classifier was used to classify non-core samples, but now represented with bag-of-words feature vectors.
+Samples from initial clusters were separated into core and non-core samples via an iterative procedure, and the core ones were labelled A SVM classifier was used to classify non-core samples, but now represented with bag-of-words feature vectors.
 The whole approach resulted with very good clusters.
@@
 For the task \emph{a}, \citet{kuznetsov-2016} trained a Gradient Boosting Regression Trees (GBRT) model on PAN 2011 dataset as a style change function used for threshold based outlier detection.
-Every sentence was vectorized using word frequencies, $n$-gram frequencies, punctuaiton symbols and the universal POS tags count, sentence length and mean length of sentence words.
-The final input to the model was concatenation of center sentence vector and ones from context of size $\pm2$.
+Every sentence was vectorized using word frequencies, $n$-gram frequencies, punctuation symbols and the universal POS tags count, sentence length and mean length of sentence words.
+The final input to the model was concatenation of the center sentence vector and ones from the context of size $\pm2$.
 In task \emph{b} they used a Hidden Markov Model with Gaussian Emissions for document segmentation over the same sentence scores from task \emph{a}.
@@
 
-\section{Author diarization and intrinsic plagiarism detetion} \label{sec:author-diraization}
+\section{Author diarization and intrinsic plagiarism detection} \label{sec:author-diraization}
 % describe the problem
@@
 
-For evaluation of intrinsic plagiarism detection, \citet{stein-2010} define multiple measures for different aspects of a system's perfromance.
-The main measures are binary macro-averaged nad micro-averaged precision ($P$), recall ($R$) and $F_1$-score.
+For evaluation of intrinsic plagiarism detection, \citet{stein-2010} define multiple measures for different aspects of a system's performance The main measures are binary macro-averaged and micro-averaged precision ($P$), recall ($R$) and $F_1$-score.
 For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$ measures described by \citet{amigo-2009}, which are specialized for evaluation of clustering results.
@@
 
-\section{The proposed approach}
+\section{The proposed approach} \label{sec:the-proposed-approach}
 
@@
 
+We develop two variants of our model which we will refer to as \emph{Model A} and \emph{Model B}.
+They are mainly differentiated by the the training of the basic feature extractor and feature transformation and in the feature transformation.
+Model B utilizes a trainable feature transformation that requires a fixed basic feature space.
+Therefore, the basic feature extractor must be trained on the trained on the whole training dataset.
+Conversely, Model A's basic feature transformation can be trained specifically allowing for use of less more important features, but it can't use a feature transformation trainable on multiple documents.
+In both approaches basic features are extracted from a sliding window which moves from token to token and includes the context of each token.
+
 % details for each component
-\paragraph{Tokenization.} As a preprocessing step, we tokenized each document $D$ using \texttt{NLTK}\footnote{\url{http://www.nltk.org}} by \citet{bird-2009} to obtain a set of tokens $T_D$.
-We also performed part-of-speech tagging with the same tool, to speed up basic feature extraction which we describe below.
+\paragraph{Tokenization.} As a preprocessing step, we tokenize each document using \texttt{NLTK}\footnote{\url{http://www.nltk.org}} by \citet{bird-2009} to obtain a sequence of tokens $D$.
+We also perform part-of-speech tagging with the same tool, to speed up basic feature extraction which we describe below.
 We didn't use other preprocessing techniques such as lemmatization, stemming and stop word removal because they would take away a lot of stylometric data from text \cite{stamatatos-2009a}.
@@
 	\item \textit{Character tri-grams}.
-Frequencies of \textit{n}-grams on character level have been very useful in quantifying the writing style \citep{stamatatos-2009b}.
+Frequencies of $n$-grams on character level have been very useful in quantifying the writing style \citep{stamatatos-2009b}.
 They are able to capture lexical and contextual information, use of punctuation and errors which can be an author's "fingerprint".
@@
 Based on work by \citet{stamatatos-2009a} and \citet{rahman-2015}, we choose $n=3$.
-Maximal dimension of this feature vector was set to 200.
+Maximal dimension of this feature vector was set to $200$.
 	\item \textit{Stop words}.
 According to \citet{stamatatos-2009a}, sometimes also called \textit{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
-They are used unconciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' \citep{burrows-1987,argamon-2005}.
-We used frequencies of 156 english stop words available in \texttt{NLTK}.
+They are used unconsciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' \citep{burrows-1987,argamon-2005}.
+We used frequencies of $156$ English stop words available in \texttt{NLTK}.
 	\item \textit{Special characters}.
@@
 This is syntactic feature which \citet{koppel-2009} and \citet{stamatatos-2009a} also identified as a discriminative one in authorship analysis and it was used by \citet{kuznetsov-2016}.
-We used all 12 tags from the universal tagset.
+We used all $12$ tags from the universal tagset.
 	\item \textit{Average token length}.
@@
 \paragraph{Feature transformation.}
-
- We develop two variants of our model which are mainly differentiated by the application of a trainable feature transformation requiring fixed basic feature space as opposed to variable feature space with features that can be more document-specific.
-
- First variant uses only a basic feature extractor $f_\mathrm{b}$, whether in second the feature transformation $f_\mathrm{t}$ is used.
-In the first variant we extract features for each document separately and scale features to zero mean and unit variance.
-In the variant with both basic extractor $f_\mathrm{b}$ and transformation $f_\mathrm{t}$, all documents are concatenated to a single one from which basic and transformed feature vectors are obtained, but without standardization.
-In both approaches basic features are extracted from a sliding window which moves from token to token and includes a context of each token.
-In the rest of the paper we refer to the first variant as model A, and to the second as model B.
-
-In model B, let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be a sequence of basic feature vectors and $(\vect{b}_i')_{i=1}^n$ the corresponding sequence of potentially preprocessed basic feature vectors with elements from $\mathbb{R}^{n_{b}'}$.
+As its feature transformation $f_\mathrm{t}$, Model A uses feature scaling to zero mean and unit variance for each document separately.
+Model B uses a trainable transformation which requires a fixed basic feature space.
+Let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be a sequence of basic feature vectors and $(\vect{b}_i')_{i=1}^n$ the corresponding sequence of potentially preprocessed basic feature vectors with elements from $\mathbb{R}^{n_{b}'}$.
 Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$.
@@
 \paragraph{Clustering.}
-
 The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens.
@@
 
-Three baseline models were defined for evaluation purposes.
+In addition to the $2$ models from the teams that took part in solving the author diarization problem on the PAN 2016 competition, we defined $3$ baselines for evaluation purposes.
 The first baseline, \emph{single-author dummy baseline}, always assigns the whole document a single author label, or, in the case of intrinsic plagiarism detection, it labels the whole document as plagiarism.
-The second baseline, \emph{stochastic dummy baseline}, learns the average total lengths of authorial parts over all documents giving the most common author label $0$ and the least common author the largest label.
+The second baseline, \emph{stochastic dummy baseline}, learns the average total lengths of authorial parts over all documents ranked by the length of their parts.
 For prediction, by modelling a Markov chain, it generates segmentations with similar label frequencies and predefined expected lengths.
@@
 For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the dataset for task \emph{b}.
-As we were adding feature by feature, BCubed precision was becoming higher so we decided to  all features in all tasks.
+As we were adding feature by feature, BCubed precision was becoming higher so we decided to use all features for model A in all tasks.
 We don't know the exact impact of the wrongly implemented type-token ratio feature.
@@
 			\midrule
-			single-author BL 		& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
-			stochastic BL 			& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
-			simple BL 				& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
+			Single-author dummy BL 	& 0.13 & 1.00 & 0.22 & 0.13 & 1.00 & 0.22 \\
+			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
+			Simple dummy BL 		& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
 			\midrule
@@
 			\midrule			
-			model A & 0 & 1 & 2 \\			
-			model B (weighting) & 0 & 1 & 2 \\			
-			model B (linear) & 0 & 1 & 2 \\
+			Model A 				&  &  &  &  &  & \\			
+			Model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
+			Model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
 			\bottomrule
@@
 	\begin{center}
-		\begin{tabular}{l|ccc}
+		\begin{tabular}{l|ccc|ccc}
 			\toprule
-			Method & $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
+			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
+			\cmidrule{2-7}
+			& $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
 			\midrule
-			single-author baseline & 0 & 1 & 2 \\
-			stochastic baseline & 0 & 1 & 2 \\
-			simple baseline & 0 & 1 & 2 \\
+			Single-author dummy BL 		& 0.33 & 1.00 & 0.47 & 0.37 & 1.00 & 0.52 \\
+			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
+			Simple dummy BL 			& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
 			\midrule
-			\citet{kuznetsov-2016} \\
-			\citet{sittar-2016} \\
+			\citet{kuznetsov-2016}		& 0.46 & 0.64 & 0.52 & 0.42 & 0.64 & 0.48 \\
+			\citet{sittar-2016} 		& 0.47 & 0.28 & 0.32 & 0.47 & 0.31 & 0.35 \\
 			\midrule			
-			model A & 0 & 1 & 2 \\			
-			model B (weighting) & 0 & 1 & 2 \\			
-			model B (linear) & 0 & 1 & 2 \\
+			Model A 					&  &  &  &  &  & \\			
+			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & 0.64 \\
+			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & 0.64 \\
 			\bottomrule

### 2017-06-01 paper/paper.tex
Intro to experimental setup.

--- 2017-06-01 paper/paper.tex
@@
 % additional packages
-\usepackage{multirow}
+\usepackage{enumitem}
 \usepackage{makecell}
-\usepackage{enumitem}
 \usepackage[hyphens]{url}
@@
 \begin{align}
-P_\mathrm{\mathrm{B}^3} &= \sum_{i=1}^c \frac{1}{l(S_i)}\sum_{j=1}^{\hat{c}}
+P_\mathrm{B^3} &= \sum_{i=1}^c \frac{1}{l(S_i)}\sum_{j=1}^{\hat{c}}
 	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2 \\
-R_\mathrm{\mathrm{B}^3} &= \sum_{j=1}^{\hat{c}} \frac{1}{l(\hat{S}_j)}\sum_{i=1}^{c}
+R_\mathrm{B^3} &= \sum_{j=1}^{\hat{c}} \frac{1}{l(\hat{S}_j)}\sum_{i=1}^{c}
 	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2 \\
-F_\mathrm{\mathrm{B}^3} &= \frac{2}{P_\mathrm{\mathrm{B}^3}^{-1}+R_\mathrm{\mathrm{B}^3}^{-1}}.
+F_\mathrm{B^3} &= \frac{2}{P_\mathrm{B^3}^{-1}+R_\mathrm{B^3}^{-1}}.
 \end{align}
@@
 \section{The proposed approach}
+% clustering, sliding window
+% pipeline: preprocessing (tokenization) -> basic features -> transformed features (including scaling) -> clustering
+% define the pipeline formally P = (f_p: d\times->t, f_b: t->\phi, f_t: \phi->\phi', c: \phi'->labels, f_s: labels\times d->s)
+% describe GroupRepel loss, describe AutoKMeans, 
+% clustering metric
 
@@
 
-Three baseline models were defined for evaluation purposes.
-The first baseline, \emph{single-author dummy baseline}, always assigns the whole document a single author label, or, in the case of intrinsic plagiarism detection, it labels the whole document as plagiarism.
-The second baseline, \emph{stochastic dummy baseline}, learns the average total lengths of authorial parts over all documents giving the most common author label $0$ and the least common author the largest label.
-For prediction, by modelling a Markov chain, it generates segmentations with similar label frequencies and predefined expected lengths.
-As we will later describe, these baseline models seem to behaved quite competitively.
+We have created two blind baselines and a baseline that tries to really predict the authorial parts based on some simple features.
+The first blind baseline predicts the whole document to have been written by a single author or, in the case of intrinsic plagiarism detection, labels the whole document as plagiarism.
+The second blind baseline learns the average lengths of
 
-We performed initial testing of usefulness of all features except for the accidentally wrongly implemented type-token ratio which was added afterwards.
-For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the dataset for task \emph{b}.
+We performed initial testing of usefulness of all features except accidentally wrongly implemented type-token ratio which was added afterwards.
+For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the datased for task \emph{b}.
 As we were adding feature by feature, BCubed precision was becoming higher so we decided to  all features in all tasks.
@@
 
+Five baseline models were defined for evaluation purposes.
+The first baseline, \textit{DummySingleAuthorDiarizer} always assigns all tokens to only one cluster, assuming that the text is written by a single author.
+As we will later describe, this baseline model behaved very competitive.
+The second baseline was \textit{DummyStohasticAuthorDiarizer} which generated a random number between
+
 \subsection{Experimental setup}
+In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}.
+Model A covered all three tasks and had a several hyperparameters in each: context size, clustering algorithm and its hyperparameters.
+
+Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
+We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values.
+The best result for task \emph{a} was $cs_a=16$ and for task \emph{b} $cs_b=140$.
+For task \emph{c}, we left $cs_c=140$ as for task \emph{b}.
+This hyperparameter probably depends on document's length to a certain extent.
+If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs.
+$16, 140, 140$).
+Although we tested different context size values again on a train set after optimal clustering algorithm selection and obtained no difference in results on a test set, they are probably biased to a certain extent.
+
+For clustering algorithm selection we used manual search over several algorithms.
+We split the whole dataset into a training and a test set.
+For each algorithm we were examining, a grid search of its hyperparameters was performed on the train set.
+We selected an algorithm and hyperparameters that achieved the best performance on a train set (since this is an unsupervised approach), and reported a final performance on the test set.
 
@@
 
-\begin{table*}
-	\caption{Results on the intrinsic plagiarism detection task.}
-	\label{tab:narrow-table}
-	\begin{center}
-		\begin{tabular}{l|ccc|ccc}
-			\toprule
-			Method & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
-			\midrule
-			single-author BL 		& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
-			stochastic BL 			& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
-			simple BL 				& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
-			\midrule
-			\citet{kuznetsov-2016} 	& 0.19 & 0.29 & 0.22 & 0.15 & 0.28 & 0.17 \\
-			\citet{sittar-2016} 	& 0.07 & 0.14 & 0.08 & 0.10 & 0.14 & 0.10 \\
-			\midrule			
-			model A & 0 & 1 & 2 \\			
-			model B (weighting) & 0 & 1 & 2 \\			
-			model B (linear) & 0 & 1 & 2 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-\end{table*}
-
 \subsection{Author diarization results}
-
-\begin{table*}
-	\caption{Results on the author diarization task with known number of authors.}
-	\label{tab:narrow-table}
-	\begin{center}
-		\begin{tabular}{l|ccc}
-			\toprule
-			Method & $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
-			\midrule
-			single-author baseline & 0 & 1 & 2 \\
-			stochastic baseline & 0 & 1 & 2 \\
-			simple baseline & 0 & 1 & 2 \\
-			\midrule
-			\citet{kuznetsov-2016} \\
-			\citet{sittar-2016} \\
-			\midrule			
-			model A & 0 & 1 & 2 \\			
-			model B (weighting) & 0 & 1 & 2 \\			
-			model B (linear) & 0 & 1 & 2 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-\end{table*}
 
@@
 
-If suitable, you can include the \emph{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.
+If suitable, you can include the \textit{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.
+
+\begin{table}
+	\caption{This is the caption of the table. Table captions should be placed \textit{above} the table.}
+	\label{tab:narrow-table}
+	\begin{center}
+		\begin{tabular}{c|ccc|ccc}
+			\toprule
+			Model & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
+			\midrule
+			Dummy & 0 & 1 & 2 \\
+			One & 0 & 1 & 2 \\
+			One & 0 & 1 & 2 \\
+			\midrule
+			One & 0 & 1 & 2 \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+\end{table}
 

### 2017-06-01 paper/paper.tex

--- 2017-06-01 paper/paper.tex
@@
 \subsection{Experimental setup}
+In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}.
+Model A covered all three tasks and had a several hyperparameters in each: context size, clustering algorithm and its hyperparameters.
+
+Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
+We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values.
+The best result for task \emph{a} was $cs_a=16$ and for task \emph{b} $cs_b=140$.
+For task \emph{c}, we left $cs_c=140$ as for task \emph{b}.
+This hyperparameter probably depends on document's length to a certain extent.
+If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs.
+$16, 140, 140$).
+Although we tested different context size values again on a train set after optimal clustering algorithm selection and obtained no difference in results on a test set, they are probably biased to a certain extent.
+
+For clustering algorithm selection we used manual search over several algorithms.
+We split the whole dataset into a training and a test set.
+For each algorithm we were examining, a grid search of its hyperparameters was performed on the train set.
+We selected an algorithm and hyperparameters that achieved the best performance on a train set (since this is an unsupervised approach), and reported a final performance on the test set.
 

### 2017-06-01 paper/paper.tex
Tables 2 and 3 updated.

@@
 			\toprule
-			Method & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
+			Method & $P_\mathrm{\mu}$ & $R_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $P_\mathrm{M}$ & $R_\mathrm{M}$ & $F_\mathrm{M}$\\
 			\midrule
@@
 			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
-			Simple dummy BL 		& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
+			Simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
 			\midrule
-			\citet{kuznetsov-2016} 	& 0.19 & 0.29 & 0.22 & 0.15 & 0.28 & 0.17 \\
-			\citet{sittar-2016} 	& 0.07 & 0.14 & 0.08 & 0.10 & 0.14 & 0.10 \\
+			\citet{kuznetsov-2016} 	& 0.29 & 0.19 & 0.22 & 0.28 & 0.15 & 0.17 \\
+			\citet{sittar-2016} 	& 0.14 & 0.07 & 0.08 & 0.14 & 0.10 & 0.10 \\
 			\midrule			
@@
 \begin{table*}
-	\caption{Results on the author diarization task with known number of authors.}
+	\caption{Results on the author diarization task.}
 	\label{tab:narrow-table}
@@
 			\cmidrule{2-7}
-			& $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
+			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
 			\midrule
@@
 			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
-			Simple dummy BL 			& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
+			Simple BL 					& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
 			\midrule
-			\citet{kuznetsov-2016}		& 0.46 & 0.64 & 0.52 & 0.42 & 0.64 & 0.48 \\
-			\citet{sittar-2016} 		& 0.47 & 0.28 & 0.32 & 0.47 & 0.31 & 0.35 \\
+			\citet{kuznetsov-2016}		& 0.64 & 0.46 & 0.52 & 0.64 & 0.42 & 0.48 \\
+			\citet{sittar-2016} 		& 0.28 & 0.47 & 0.32 & 0.31 & 0.47 & 0.35 \\
 			\midrule			

### 2017-06-01 paper/paper.tex
Added Model B to Experimental setup

--- 2017-06-01 paper/paper.tex
@@
 % TODO: replace $n$-gram and \emph{n}-gram with n-gram, as it is common in literature
+% TODO: hange bi-grams to bigrams and tri-grams to trigrams
 % TODO: suggestion: remove \texttt-s 
-% TODO: convert Related work to present
 % TODO: change \texit-s ti \emph-s
 % TODO: explain BFE training in The proposed approach
+% TODO: convert Related work to present
 
@@
 
-Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_b}, f_\mathrm{t}:\Phi_{n_b}\rightarrow \Phi_{n_t}, f_\mathrm{c}:\Phi_{n_t}\rightarrow C)$.
+Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_\mathrm{b}}, f_\mathrm{t}:\Phi_{n_\mathrm{b}}\rightarrow \Phi_{n_\mathrm{t}}, f_\mathrm{c}:\Phi_{n_\mathrm{t}}\rightarrow C)$.
 Here $\Delta$ is the tokenized document domain as defined in section \ref{sec:author-diraization}.
-$\Phi_{n_b}$ and $\Phi_{n_t}$ are sets of variable-length sequences of feature vectors with dimension $n_b$ and $n_t$ respectively.
-$n_b$ and $n_t$ can either be fixed or depend on the document being processed.
+$\Phi_{n_\mathrm{b}}$ and $\Phi_{n_\mathrm{t}}$ are sets of variable-length sequences of feature vectors with dimension $n_\mathrm{b}$ and $n_\mathrm{t}$ respectively.
+$n_\mathrm{b}$ and $n_\mathrm{t}$ can either be fixed or depend on the document being processed.
 $C$ is the set of all sequences of length $n$ (the number of tokens in the document) with elements being indices of authors/clusters.
@@
 From each context we extracted the most used stylometric features which we found in previous work.
+The features that we have considered in our models are:
 \begin{itemize}
@@
 Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$.
-We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_b'}\rightarrow\mathbb{R}^{n_t}$ with trainable parameters $\vect{\theta}_T$, i.e.
+We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_\mathrm{b}'}\rightarrow\mathbb{R}^{n_\mathrm{t}}$ with trainable parameters $\vect{\theta}_T$, i.e.
 we want to maximize segregation and compactness of groups of transformed feature vectors grouped by their target author label.
-Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i'))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_t}$.
+Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i'))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_\mathrm{t}}$.
 We define the following loss in order to optimize the transformation $T$:
@@
 For the transformation $T$ we have tried a nonlinear transformations represented as neural networks with one or more hidden layers.
-We didn't explore it much because it was slower and didn't give as good results as a linear transformation or an elementwise product with a weight vector:
+We didn't explore nonlinear transformations much because they were slower and didn't give as good results as a linear transformation or an elementwise linear transformation:
 \begin{align}
-	T_1(\vect{x}) &= \matr{W}\vect{x}, \quad \vect{\theta}_{T_1} = \matr{W}, \\
-	T_2(\vect{x}) &= \vect{w}\odot\vect{x}, \quad \vect{\theta}_{T_2} = \vect{w}.
+	T_\mathrm{1}(\vect{x}) &= \matr{W}\vect{x}, \\
+	T_\mathrm{2}(\vect{x}) &= \vect{w}\odot\vect{x}.
 \end{align}
+Here $\matr{W}\in \mathbb{R}^{n_\mathrm{b}'\times n_\mathrm{t}}$ and $\vect{w}\in \mathbb{R}^{n_\mathrm{b}'}$.
 Before applying the transformations, basic feature vectors are preprocessed by concatanating each with the vector of its squared elements:
@@
 \subsection{Experimental setup}
-In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}.
-Model A covered all three tasks and had a several hyperparameters in each: context size, clustering algorithm and its hyperparameters.
 
-Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
-We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values.
-The best result for task \emph{a} was $cs_a=16$ and for task \emph{b} $cs_b=140$.
-For task \emph{c}, we left $cs_c=140$ as for task \emph{b}.
-This hyperparameter probably depends on document's length to a certain extent.
-If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs.
-$16, 140, 140$).
-Although we tested different context size values again on a train set after optimal clustering algorithm selection and obtained no difference in results on a test set, they are probably biased to a certain extent.
-
-For clustering algorithm selection we used manual search over several algorithms.
-We split the whole dataset into a training and a test set.
-For each algorithm we were examining, a grid search of its hyperparameters was performed on the train set.
-We selected an algorithm and hyperparameters that achieved the best performance on a train set (since this is an unsupervised approach), and reported a final performance on the test set.
+\paragraph{Model B.} For Model B, we have decided to use choose a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).
+The length of the sliding window is set to $120$ characters.
+Model B uses k-means clustering.
+We have chosen two trainable feature transformations: linear and elementwise linear.
+For the both transformations $5\times 10^{-4}$ was chosen for the learning rate.
+All the hyperparameters are selected manually by  experimenting on the development dataset (approximately $70\%$ of the available dataset).
+$70\%$ of the development set was used for training basic feature extractors and the transformation.
+Considering the results on the   validation part of the development set, not very large numbers of iterations seem to be more beneficial.
+A number of $40$ iterations was chosen for the linear transformation, and $20$ for the elementwise linear transformation.
+For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be archivable using smaller numbers like $20$, making training and clustering faster.
 

### 2017-06-01 paper/paper.tex
Send this to Milan

@@
 % TODO: explain BFE training in The proposed approach
+% TODO: consistency: use only "training set" and "test set" (not dataset, not train) (https://en.wikipedia.org/wiki/Test_set)
 % TODO: convert Related work to present
@@
 \begin{table}
-	\caption{Basic characteristics of training datasets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
+	\caption{Basic characteristics of training sets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
 	\label{tab:dataset-characteristics}
@@
 
-For each of the three subtasks a training dataset is publicly available\footnotemark[1].
+For each of the three subtasks a training set is publicly available\footnotemark[1].
 \citet{rosso-2016} explain that they are collections of various documents which are part of Webis-TRC-12 dataset \citep{potthast-2013}.
@@
 authors) for one of the 150 topics in total.
-By varying different parameters such as the number and proportion of the authors, places in a document where an author switch occurs (between words, sentences or paragraphs), three training and test datasets were generated \citep{rosso-2016}.
+By varying different parameters such as the number and proportion of the authors, places in a document where an author switch occurs (between words, sentences or paragraphs), three training and test sets were generated \citep{rosso-2016}.
 Test datasets are currently not publicly available and we could not use them for evaluation of our approach.
-Some basic characteristics of the training datasets are shown in Table \ref{tab:dataset-characteristics}.
+Some basic characteristics of the training sets are shown in Table \ref{tab:dataset-characteristics}.
 
@@
 Model B utilizes a trainable feature transformation that requires a fixed basic feature space.
-Therefore, the basic feature extractor must be trained on the trained on the whole training dataset.
+Therefore, the basic feature extractor must be trained on the trained on the whole training set.
 Conversely, Model A's basic feature transformation can be trained specifically allowing for use of less more important features, but it can't use a feature transformation trainable on multiple documents.
@@
 The \emph{segregation loss}  $L_\mathrm{s}$ is proportional to the sum of magnitudes (not magnitude of the sum) of forces between $c$ equally charged particles each located at one of the centroids.
-By minimizing the average loss (the error) across all documents in the training dataset with respect to the parameters of the transformation $\vect{\theta}_T$ we hope to benefit the clustering algorithm.
+By minimizing the average loss (the error) across all documents in the training set with respect to the parameters of the transformation $\vect{\theta}_T$ we hope to benefit the clustering algorithm.
 Instead of squared $L^2$ distance, some other distance measure may be used.
@@
 
-repo link
+repo link - move from Ivan1024 to an organization
 
-For experiments, we used the three PAN 2016 training datasets.
-The test datasets used in the competition have not been made publicly available.
+For experiments, we have used the three PAN 2016 training sets.
+The test sets used in the competition have not been made publicly available.
 Therefore, our evaluation results might be only moderately comparable to the results of other systems.
@@
 In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}.
-Model A covered all three tasks and had a several hyperparameters in each: context size, clustering algorithm and its hyperparameters.
+Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and its hyperparameters.
 
@@
 $16, 140, 140$).
-Although we tested different context size values again on a train set after optimal clustering algorithm selection and obtained no difference in results on a test set, they are probably biased to a certain extent.
+Although we tested different context size values again on a training set after optimal clustering algorithm selection and obtained no difference in results on a test set, they are probably biased to a certain extent.
 
@@
 We split the whole dataset into a training and a test set.
-For each algorithm we were examining, a grid search of its hyperparameters was performed on the train set.
-We selected an algorithm and hyperparameters that achieved the best performance on a train set (since this is an unsupervised approach), and reported a final performance on the test set.
+For each algorithm we were examining, a grid search of its hyperparameters was performed on the training set.
+We selected an algorithm and hyperparameters that achieved the best performance on a training set (since this is an unsupervised approach), and reported a final performance on the test set.
 
-\paragraph{Model B.} For Model B, we have decided to use choose a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).
+\paragraph{Model B.} For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).
 The length of the sliding window is set to $120$ characters.
@@
 For the both transformations $5\times 10^{-4}$ was chosen for the learning rate.
-All the hyperparameters are selected manually by  experimenting on the development dataset (approximately $70\%$ of the available dataset).
+All the hyperparameters are selected manually by  experimenting on the development dataset, which is approximately $70\%$ of the available dataset.
 $70\%$ of the development set was used for training basic feature extractors and the transformation.
@@
 \subsection{Intrinsic plagiarism detection results}
+
+don't forget to describe tolerance
 
@@
 
-\subsection{Intrinsic plagiarism detection}
-
-setup
-results
-don't forget to describe tolerance
-
-\subsection{Author diarization with known numbers of authors}
-
-setup
-
-\subsection{Author diarization with unknown numbers of authors}
-
-setup
-
-\paragraph{Segmentation generation.} something short
-
-features
-
-differences: fixed features + transformation vs document-dependent features
-
 \section{Conclusion}

### 2017-06-01 paper/paper.tex
Setup for tasks a and b.

@@
 
+In task \emph{a}, we used 50\% of dataset as a training set, and other half as a test set.
+Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results.
+Other algorithms which we evaluated were Gaussian mixtures and hierarchical agglomerative clustering.
+Agglomerative clustering with cosine affinity and average linkage achieved the best performance on the training set and we report its result on the test set.
+We measured macro $F_\mathrm{M}$.
+
+In task \emph{b} we also split dataset in two half.
+Grid search for the best hyperparameters was performed for agglomerative clustering.
+The best performance on the training set was obtained with euclidean affinity and average linkage.
+
+For task \emph{c}
+
 \paragraph{Model B.} For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).

### 2017-06-01 paper/paper.tex
Added a part of the abstract

--- 2017-06-01 paper/paper.tex
@@
 \abstract{ 
-This document provides the instructions on formatting the TAR system description paper in \LaTeX{}.
-This is where you write the abstract (i.e., summary) of the work you carried out within the project.
-The abstract is a paragraph of text ranging between 70 and 150 words.
-This document provides the instructions on formatting the TAR system description paper in \LaTeX{}.
-This is where you write the abstract (i.e., summary) of the work you carried out within the project.
-The abstract is a paragraph of text ranging between 70 and 150 words.
+In this paper we present an approach trying to solve the PAN 2016 author diarization and intrinsic plagiarism detection problem.
+We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window.
+There are two variants of the approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt if for clustering with a traineable feature transformation.
+Our results competitive results
 }
@@
 
+hard task, a lot of space for improvement
+
 Conclusion is the last enumerated section of the paper.

### 2017-06-01 software/inpladesys/models/clustering/auto_k_means.py

@@ -19,7 +19,7 @@ class AutoKMeans():
     def train(self, X, ks):
         old_max_iter = self.max_iter
         self.max_iter = 200
-        ps = np.linspace(0, 0.7, 1)
+        ps = np.linspace(0, 0.7, 8)
         errors = []
         l1errors = []
         hitses = []
@@ -40,6 +40,7 @@ class AutoKMeans():
             print(l1errors)
             print(hitses)
         self.p = ps[np.argmin(errors)]  # 0.3
+        print("AutoKMeans-p {}".format(self.p))
         self.max_iter = old_max_iter
 
     def fit_predict(self, X, cluster_count=None):

### 2017-06-01 software/inpladesys/models/pipeline_author_diarizer.py

@@ -62,9 +62,9 @@ class PipelineAuthorDiarizer():
                 plt.scatter(h[:, 0], h[:, 1], c=y1[0])
                 plt.pause(0.05)
 
-        #print("(5/4) Training clusterer...")
-        #if getattr(self.clusterer, "train", None) is not None:
-        #    self.clusterer.train(self.feature_transformer.transform(X), [s.author_count for s in segmentations])
+        print("(5/4) Training clusterer...")
+        if getattr(self.clusterer, "train", None) is not None:
+            self.clusterer.train(self.feature_transformer.transform(X), [s.author_count for s in segmentations])
 
     def predict(self, documents, author_counts=None):
         assert (len(documents) > 0)

### 2017-06-01 software/test-pipeline.py

@@ -1,4 +1,5 @@
 from inpladesys.datasets import Pan16DatasetLoader
+from inpladesys.datatypes import Segmentation
 from inpladesys.models.basic_feature_extraction.basic_feature_extractor import BasicFeatureExtractor
 from inpladesys.models.feature_transformation import GroupRepelFeatureTransformer
 from inpladesys.models.pipeline_author_diarizer import PipelineAuthorDiarizer
@@ -39,7 +40,7 @@ def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True, test
             learning_rate=5e-4,
             random_state=random_state)
     print(str(pl_params['feature_transformer']))
-    pl_params['clusterer'] = AutoKMeans(min_clusters=2, max_clusters=2) if dataset_index != 1 else AutoKMeans(2, 2)
+    pl_params['clusterer'] = AutoKMeans(2, 2) if dataset_index != 2 else AutoKMeans(2, 10)
     # pl_params['clusterer'] = Deoutliizer(0.3)
     if params['basic_feature_extender'] == 'f**2':
         pl_params['basic_feature_extender'] = lambda f: np.concatenate((f, f ** 2), axis=0)
@@ -74,11 +75,24 @@ def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True, test
                      author_counts=[s.author_count for d, s in validate_data] if dataset_index == 1 else None)
     ys = validate_data.segmentations
 
+    class KScorer():
+        def __init__(self, y: Segmentation, h: Segmentation):
+            self.y, self.h = y, h
+
+        def precision(self):
+            return int(self.y.author_count != self.h.author_count)
+
+        def recall(self):
+            return abs(self.y.author_count - self.h.author_count)
+
+        def f1_score(self):
+            return (self.y.author_count - self.h.author_count) ** 2
+
     def get_scores(scorer_factory, y, h):
         scorer = scorer_factory(y, h)
         return np.array([scorer.precision(), scorer.recall(), scorer.f1_score()])
 
-    scorer_factories = [MicroScorer, MacroScorer, BCubedScorer] if dataset_index == 0 else [BCubedScorer]
+    scorer_factories = [MicroScorer, MacroScorer, BCubedScorer] if dataset_index == 0 else [BCubedScorer, KScorer]
     for sf in scorer_factories:
         score_list = [get_scores(sf, y, h) for y, h in zip(ys, hs)]
[…]

### 2017-06-01 paper/paper.tex
Setup c partialy finished.

--- 2017-06-01 paper/paper.tex
@@
 
-For task \emph{c}
+For task \emph{c} we should have somehow determine the number of clusters.
+Due to lack of time we decided to test algorithms which can determine this number automatically, i.e.
+this is not a hyperparameter which should be known in advance.
+Since we noticed that grid searches take a lot of time, we reduced a training set from 50\% to 10\% and repeated all experiments.
+We tested DBSCAN, affinity propagation, and mean shift algorithms.
+
+The best results were obtained with DBSCAN, and for other ones they were very low.
+We noticed that the estimated number of clusters with the best hyerparameters (eps=100, min\_samples=71, metric=manhattan) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
+In all grid searches we used BCubed F measure and only DBSCAN achieved acceptable level.
+Our opinion is that this was a consequence of a larger number of smaller clusters which had a positive influence on BCubed precision and therefore on overall performance.
+
+Since the relatively good Bcubed F measure is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search for DBSCAN, but now we set the Calinski-Harabaz index as evaluation measure since it does not require the real number of clusters for clustering evaluation.
+Finally, from all results on training set we chose (eps=0.23, min\_samples=64, metric=cosine) for the final hyperparameters.
+This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document.
+
+Što s noisy opisati.
 

### 2017-06-01 paper/paper.tex
no message

--- 2017-06-01 paper/paper.tex
@@
 We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window.
-There are two variants of the approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt if for clustering with a traineable feature transformation.
-Our results competitive results
+There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt if for clustering with a traineable feature transformation.
+We have evaluated our approach on the available datasets from PAN 2016.
 }
@@
 We used counts of all character sequences which satisfied a regular expression defined as \verb/[^\\w]{1,4}/.
-Although character $n$-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose since \citet{koppel-2009} mentioned that authors can have different punctuation habbits.
+Although character $n$-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose since \citet{koppel-2009} mentioned that authors can have different punctuation habits.
 	\item \textit{POS tag counts}.
 This is syntactic feature which \citet{koppel-2009} and \citet{stamatatos-2009a} also identified as a discriminative one in authorship analysis and it was used by \citet{kuznetsov-2016}.
-We used all $12$ tags from the universal tagset.
+We used all $12$ tags from the universal tag set
 	\item \textit{Average token length}.
@@
 We included this feature because it boosted performance of our initial testing, even without words been previously stemmed or lemmatized (stop words were excluded).
-Counts of maximum of 100 unigrams were used.
+Counts of a maximum of 100 unigrams were used.
 	\item \textit{Type-token ratio}.
@@
 
+Our results, as well as the the results of others, suggest that author diarization and intrinsic plagiarism detection are challenging problems. Our approach
+
+ and that there is a lot of room for improvement for our approach
+
+ as well as in exploring other
+
 Conclusion is the last enumerated section of the paper.
@@
 
-\section{Further work}
+% 2-nd paragraph further work
 % more systematic parameter choice, model development

### 2017-06-01 software/inpladesys/models/clustering/auto_k_means.py

@@ -19,7 +19,7 @@ class AutoKMeans():
     def train(self, X, ks):
         old_max_iter = self.max_iter
         self.max_iter = 200
-        ps = np.linspace(0, 0.7, 8)
+        ps = np.linspace(-2, 0.5, 26)
         errors = []
         l1errors = []
         hitses = []
@@ -39,6 +39,7 @@ class AutoKMeans():
             print(errors) # 43
             print(l1errors)
             print(hitses)
+        print(ps)
         self.p = ps[np.argmin(errors)]  # 0.3
         print("AutoKMeans-p {}".format(self.p))
         self.max_iter = old_max_iter

### 2017-06-02 paper/paper.tex
Added more text to "Results", described auto-k-means

@@
 
-\subsection{Evaluation measures}
+\subsection{Evaluation measures} \label{subsec:evaluation-measures}
 
@@
 The transformation is implemented using TensorFlow\footnote{\url{https://www.tensorflow.org}}.
+Parameters are randomly initialized with values from a truncated normal distribution withe standard deviation $0.1$.
 It is trained on-line (one document per optimization step) using RMSProp \citep{tielman-2012} with default parameters and learning rate $5\times 10^{-4}$.
@@
 In the first variant of our approach for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
-In the second variant we used k-means for clustering in all tasks, and tried our modification of k-means, which we called Auto-k-means in task \emph{c}.
-The reason for choosing those algorithms is described in section \ref{sec:experimental-results}
+In the second variant we used k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule.
+This is described in more detail in section \ref{sec:experimental-results}.
 
@@
 Since the relatively good Bcubed F measure is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search for DBSCAN, but now we set the Calinski-Harabaz index as evaluation measure since it does not require the real number of clusters for clustering evaluation.
-Finally, from all results on training set we chose (eps=0.23, min\_samples=64, metric=cosine) for the final hyperparameters.
+Finally, from all results on training set we chose (eps=$0.23$, min\_samples=64, metric=cosine) for the final hyperparameters.
 This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document.
@@
 Model B uses k-means clustering.
-We have chosen two trainable feature transformations: linear and elementwise linear.
-For the both transformations $5\times 10^{-4}$ was chosen for the learning rate.
+We have chosen two trainable feature transformations: linear and elementwise linear (weighting).
+For both of the transformations $5\times 10^{-4}$ was chosen for the learning rate.
 All the hyperparameters are selected manually by  experimenting on the development dataset, which is approximately $70\%$ of the available dataset.
@@
 A number of $40$ iterations was chosen for the linear transformation, and $20$ for the elementwise linear transformation.
-For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be archivable using smaller numbers like $20$, making training and clustering faster.
+For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be achievable using smaller numbers like $20$, making training and clustering faster.
+
+For task \emph{c} we have implemented a simple wrapper for the k-means algorithm that tries to predict the correct number of authors.
+It computes the k-means error for each number $k$ in the specified range for the number of clusters.
+Based on ratios of relative improvements in the score between consecutive $k$-s, it chooses the $k$ giving the best ratio modulated with a modulation function dependent on $k$, simply $k^\alpha$ was chosen, where $\alpha$ is selected using linear search.
+Being limited in time, we didn't put much effort into optimizing the selection of the best number of clusters.
+Moreover, even if knowing the number of clusters in advance, it seems that even the transformed features are not satisfactory for correct clustering.
+We notice that using the correct numbers of authors compared to using a fixed $k=2$ results in relative decrease in BCubed precision, recall, and $F_1$-score by factors of $0.95$, $0.64$ and $0.79$ respectively.
+
+\subsection{Evaluation results}
+
+We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}.
+
+The results of evaluation for the intrinsic plagiarism problem (task \emph{a}) are shown in table \ref{tab:results-task-a}.
+For author diarization with known (task \emph{b}) and unknown (task \emph{c}) numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.
 
@@
 	\caption{Results on the intrinsic plagiarism detection task.}
-	\label{tab:narrow-table}
+	\label{tab:results-task-a}
 	\begin{center}
@@
 	\caption{Results on the author diarization task.}
-	\label{tab:narrow-table}
+	\label{tab:results-task-b-c}
 	\begin{center}

### 2017-06-02 software/inpladesys/models/clustering/auto_k_means.py

@@ -19,7 +19,7 @@ class AutoKMeans():
     def train(self, X, ks):
         old_max_iter = self.max_iter
         self.max_iter = 200
-        ps = np.linspace(-2, 0.5, 26)
+        ps = np.linspace(-1.5, 0.5, 21)
         errors = []
         l1errors = []
         hitses = []

### 2017-06-02 software/inpladesys/models/pipeline_author_diarizer.py

@@ -62,9 +62,9 @@ class PipelineAuthorDiarizer():
                 plt.scatter(h[:, 0], h[:, 1], c=y1[0])
                 plt.pause(0.05)
 
-        print("(5/4) Training clusterer...")
-        if getattr(self.clusterer, "train", None) is not None:
-            self.clusterer.train(self.feature_transformer.transform(X), [s.author_count for s in segmentations])
+        #print("(5/4) Training clusterer...")
+        #if getattr(self.clusterer, "train", None) is not None:
+        #    self.clusterer.train(self.feature_transformer.transform(X), [s.author_count for s in segmentations])
 
     def predict(self, documents, author_counts=None):
         assert (len(documents) > 0)

### 2017-06-02 software/test-pipeline.py

@@ -40,7 +40,7 @@ def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True, test
             learning_rate=5e-4,
             random_state=random_state)
     print(str(pl_params['feature_transformer']))
-    pl_params['clusterer'] = AutoKMeans(2, 2) if dataset_index != 2 else AutoKMeans(2, 10)
+    pl_params['clusterer'] = AutoKMeans(2, 2) if dataset_index != 2 else AutoKMeans(2, 2)
     # pl_params['clusterer'] = Deoutliizer(0.3)
     if params['basic_feature_extender'] == 'f**2':
         pl_params['basic_feature_extender'] = lambda f: np.concatenate((f, f ** 2), axis=0)
@@ -204,6 +204,7 @@ Standard error: 0.0439617652085
 95.0% confidence interval: (0.54720825480421598, 0.74072664047420889)
 <class 'inpladesys.evaluation.BCubedScorer'>
 [ 0.55661435  0.81782488  0.64396745] +- [ 0.17287733  0.13548413  0.14580468]
+[ 0.52577781  0.52042712  0.50930703] +- [ 0.15178143  0.18369707  0.13211388] - known number of authors
 """
 """ Weighting
 Standard error: 0.0380707132254

### 2017-06-02 paper/paper.tex
no message

@@
 Agglomerative clustering with cosine affinity and average linkage achieved the best performance on the training set and we report its result on the test set.
-We measured macro $F_\mathrm{M}$.
+We measured macro-averaged $F_1$-score.
 
@@
 We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}.
+The results of our models are compared to the reuslts of our baselines, a well as the results of the two teams that took part in the PAN 2016 competition for this problem.
+The results of the two teams have been evaluated on test sets that is not publicly available.
+Only the training sets from the competition have been available to us.
 
-The results of evaluation for the intrinsic plagiarism problem (task \emph{a}) are shown in table \ref{tab:results-task-a}.
-For author diarization with known (task \emph{b}) and unknown (task \emph{c}) numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.
+The results of evaluation for the intrinsic plagiarism problem are shown in table \ref{tab:results-task-a}.
+For author diarization with known and unknown numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.
 
-\subsection{Intrinsic plagiarism detection results}
+{Intrinsic plagiarism detection results}
 
 don't forget to describe tolerance
+
+{Author diarization results}
 
@@
 
-\subsection{Author diarization results}
-
 \begin{table*}
-	\caption{Results on the author diarization task.}
+	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (task \emph{c}) numbers of authors.}
 	\label{tab:results-task-b-c}

### 2017-06-02 paper/paper.tex
Added somem more text about evaluation results

@@
 More precisely, \citet{koppel-2009} explain that methods used in authorship analysis must be able to distinguish writing styles, but also tolerate shallow differences within the same style because an author's stylistic habits can consciously or unconsciously vary over time.
-Therefore, most of related work tries to find the better features and methods which writing style will be quantified and measured with.
+Therefore, most of related work tries to find better features and methods which writing style will be quantified and measured with.
 
@@
 For author diarization with known and unknown numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.
+It should be noted that the evaluated Model B uses a fixed number of clusters $k=2$ for task \emph{c} and that the results are actually not very good.
+By trying a more honest approach with predicting the number of clusters the BCubed $F_1$-score drops below $0.5$.
 
@@
 \begin{table*}
-	\caption{Results on the intrinsic plagiarism detection task.}
+	\caption{Results on the intrinsic plagiarism detection task. The standard errors both for $F_\mathrm{\mu}$ and $F_\mathrm{M}$ are for Model A within $\pm0.04$ and for Model B within $\pm0.06$.}
 	\label{tab:results-task-a}
@@
 \begin{table*}
-	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (task \emph{c}) numbers of authors.}
+	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (task \emph{c}) numbers of authors.
+The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$.
+}
 	\label{tab:results-task-b-c}

### 2017-06-02 paper/paper.tex
Chap 5 probably finished.

--- 2017-06-02 paper/paper.tex
@@
 
+In the third baseline, \textit{simple fixed baseline}, we used default k-means clustering of vectorized document's sentences.
+Average token length, sentence length, POS tag counts and bag of maximum 100 words (with stop words) served as a features.
+
 We performed initial testing of usefulness of all features except for the accidentally wrongly implemented type-token ratio which was added afterwards.
@@
 
-Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
+\paragraph{Model A.}Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
 We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values.
@@
 $16, 140, 140$).
-Although we tested different context size values again on a training set after optimal clustering algorithm selection and obtained no difference in results on a test set, they are probably biased to a certain extent.
+However, they are probably biased to a certain extent.
 
@@
 Other algorithms which we evaluated were Gaussian mixtures and hierarchical agglomerative clustering.
-Agglomerative clustering with cosine affinity and average linkage achieved the best performance on the training set and we report its result on the test set.
-We measured macro-averaged $F_1$-score.
+Cosine affinity and average linkage with agglomerative clustering achieved the best performance on the training set and we report its result on the test set.
+We measured $F_M$ score described in subsection \ref{subsec:evaluation-measures}
 
@@
 For task \emph{c} we should have somehow determine the number of clusters.
-Due to lack of time we decided to test algorithms which can determine this number automatically, i.e.
+Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e.
 this is not a hyperparameter which should be known in advance.
@@
 
-The best results were obtained with DBSCAN, and for other ones they were very low.
-We noticed that the estimated number of clusters with the best hyerparameters (eps=100, min\_samples=71, metric=manhattan) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
-In all grid searches we used BCubed F measure and only DBSCAN achieved acceptable level.
+The best results on task \emph{c} were obtained with DBSCAN, and for other ones they were very low.
+We noticed that the estimated number of clusters with the best hyerparameters (\texttt{eps=100, min\_samples=71, metric="manhattan"}) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
+In all grid searches we used BCubed $F$ measure and only DBSCAN achieved acceptable performance.
 Our opinion is that this was a consequence of a larger number of smaller clusters which had a positive influence on BCubed precision and therefore on overall performance.
 
-Since the relatively good Bcubed F measure is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search for DBSCAN, but now we set the Calinski-Harabaz index as evaluation measure since it does not require the real number of clusters for clustering evaluation.
-Finally, from all results on training set we chose (eps=$0.23$, min\_samples=64, metric=cosine) for the final hyperparameters.
-This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document.
-
-Što s noisy opisati.
+Since the relatively good Bcubed $F$ measure is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search in task \emph{c} for DBSCAN, but now we set the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
+Finally, from all results on training set we chose (\texttt{eps=$0.23$, min\_samples=64, metric="cosine"}) for the final hyperparameters.
+This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document and performed quite fast.
+If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size 10 (5 on each side), or the majority label from all samples if samples in the context weren't  clustered.
 

### 2017-06-02 paper/paper.tex
Added some text to the cocnlusion

--- 2017-06-02 paper/paper.tex
@@
 We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}.
-The results of our models are compared to the reuslts of our baselines, a well as the results of the two teams that took part in the PAN 2016 competition for this problem.
+The results of our models are compared to the results of our baselines, a well as the results of the two teams that took part in the PAN 2016 competition for this problem.
 The results of the two teams have been evaluated on test sets that is not publicly available.
@@
 
-Our results, as well as the the results of others, suggest that author diarization and intrinsic plagiarism detection are challenging problems. Our approach
+Our results, as well as the the results of others, suggest that author diarization and intrinsic plagiarism detection are very challenging problems.
+Our approach tries to solve the problem by clustering contextual writing style features extracted with a sliding window around each token.
+
+We have presented some ideas that are not completely refined but, based on the data we have available, seem to give comparable, or even better results that the other two approaches that tired to tackle the same problem.
 
@@
 % 2-nd paragraph further work
-% more systematic parameter choice, model development
+% basic feature extraction speed sliding window overlap?
+% more systematic parameter choice, further model development
 % mention possible applicability to author clustering and extrinsic plagiarism detections

### 2017-06-02 paper/paper.tex
Tables finished.

--- 2017-06-02 paper/paper.tex
@@
 
-Since the relatively good Bcubed $F$ measure is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search in task \emph{c} for DBSCAN, but now we set the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
+Since the best achieved Bcubed $F$ measure (0.61) is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search in task \emph{c} for DBSCAN, but now we set the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
 Finally, from all results on training set we chose (\texttt{eps=$0.23$, min\_samples=64, metric="cosine"}) for the final hyperparameters.
-This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document and performed quite fast.
+This wasn't the best combination, but it produced relatively acceptable amount of noisy elements per document, and performed quite fast but again din't estimate the correct number of clusters in most cases.
 If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size 10 (5 on each side), or the majority label from all samples if samples in the context weren't clustered.
@@
 
+\begin{table*}
+	\caption{Results on the intrinsic plagiarism detection task.
+The standard errors both for $F_\mathrm{\mu}$ and $F_\mathrm{M}$ are for Model A within $\pm0.04$ and for Model B within $\pm0.06$ at the 95\% confidence.
+Results of models denoted with * were obtained on the PAN 2016 test set which was not available to us.}
+	\label{tab:results-task-a}
+	\begin{center}
+		\begin{tabular}{l|ccc|ccc}
+			\toprule
+			Method & $P_\mathrm{\mu}$ & $R_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $P_\mathrm{M}$ & $R_\mathrm{M}$ & $F_\mathrm{M}$\\
+			\midrule
+			Single-author dummy BL 	& 0.13 & \textbf{1.00} & 0.22 & 0.13 & \textbf{1.00} & 0.22 \\
+			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & \textbf{0.25} \\
+			Simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
+			\midrule
+			\citet{kuznetsov-2016}* 	& \textbf{0.29} & 0.19 & 0.22 & \textbf{0.28} & 0.15 & 0.17 \\
+			\citet{sittar-2016}* 	& 0.14 & 0.07 & 0.08 & 0.14 & 0.10 & 0.10 \\
+			\midrule			
+			Model A 				& 0.18 & 0.43 & \textbf{0.25} & 0.18 & 0.43 & 0.24 \\			
+			Model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
+			Model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+\end{table*}
+
+\begin{table*}
+	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (task \emph{c}) numbers of authors.
+The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$ at the 95\% confidence.
+Results of models denoted with * were obtained on the PAN 2016 test set which was not available to us.}
+	\label{tab:results-task-b-c}
+	\begin{center}
+		\begin{tabular}{l|ccc|ccc}
+			\toprule
+			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
+			\cmidrule{2-7}
+			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
+			\midrule
+			Single-author dummy BL 		& 0.33 & \textbf{1.00} & 0.47 & 0.37 & \textbf{1.00} & 0.52 \\
+			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
+			Simple BL 					& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
+			\midrule
+			\citet{kuznetsov-2016}*		& \textbf{0.64} & 0.46 & 0.52 & 0.64 & 0.42 & 0.48 \\
+			\citet{sittar-2016}* 		& 0.28 & 0.47 & 0.32 & 0.31 & 0.47 & 0.35 \\
+			\midrule			
+			Model A 					& 0.61 & 0.65 & \textbf{0.62} & \textbf{0.71} & 0.50 & 0.54 \\			
+			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & \textbf{0.64} \\
+			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & \textbf{0.64} \\
+			\bottomrule
+		\end{tabular}
+	\end{center}
+\end{table*}
+
 We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}.
@@
 {Author diarization results}
-
-\begin{table*}
-	\caption{Results on the intrinsic plagiarism detection task. The standard errors both for $F_\mathrm{\mu}$ and $F_\mathrm{M}$ are for Model A within $\pm0.04$ and for Model B within $\pm0.06$.}
-	\label{tab:results-task-a}
-	\begin{center}
-		\begin{tabular}{l|ccc|ccc}
-			\toprule
-			Method & $P_\mathrm{\mu}$ & $R_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $P_\mathrm{M}$ & $R_\mathrm{M}$ & $F_\mathrm{M}$\\
-			\midrule
-			Single-author dummy BL 	& 0.13 & 1.00 & 0.22 & 0.13 & 1.00 & 0.22 \\
-			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
-			Simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
-			\midrule
-			\citet{kuznetsov-2016} 	& 0.29 & 0.19 & 0.22 & 0.28 & 0.15 & 0.17 \\
-			\citet{sittar-2016} 	& 0.14 & 0.07 & 0.08 & 0.14 & 0.10 & 0.10 \\
-			\midrule			
-			Model A 				&  &  &  &  &  & \\			
-			Model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
-			Model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-\end{table*}
-
-\begin{table*}
-	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (task \emph{c}) numbers of authors.
-The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$.
-}
-	\label{tab:results-task-b-c}
-	\begin{center}
-		\begin{tabular}{l|ccc|ccc}
-			\toprule
-			\multirow{2}{*}{Method} & \multicolumn{3}{c|}{Task \emph{b}} & \multicolumn{3}{c}{Task \emph{c}} \\
-			\cmidrule{2-7}
-			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
-			\midrule
-			Single-author dummy BL 		& 0.33 & 1.00 & 0.47 & 0.37 & 1.00 & 0.52 \\
-			Stochastic dummy BL 		& 0.35 & 0.59 & 0.41 & 0.39 & 0.59 & 0.45 \\
-			Simple BL 					& 0.43 & 0.50 & 0.45 & 0.45 & 0.54 & 0.45 \\
-			\midrule
-			\citet{kuznetsov-2016}		& 0.64 & 0.46 & 0.52 & 0.64 & 0.42 & 0.48 \\
-			\citet{sittar-2016} 		& 0.28 & 0.47 & 0.32 & 0.31 & 0.47 & 0.35 \\
-			\midrule			
-			Model A 					&  &  &  &  &  & \\			
-			Model B (linear) 			& 0.48 & 0.45 & 0.46 & 0.56 & 0.82 & 0.64 \\
-			Model B (weighting)			& 0.51 & 0.49 & 0.50 & 0.57 & 0.77 & 0.64 \\
-			\bottomrule
-		\end{tabular}
-	\end{center}
-\end{table*}
 

### 2017-06-02 paper/paper.tex
no message

--- 2017-06-02 paper/paper.tex
@@
 
-\citet{zu-2006} manually created a labelled corpus of plagiarized documents and used it for intrinsic plagiarism detection task.
+\citet{zu-2006} have manually created a labelled corpus of plagiarized documents and used it for the intrinsic plagiarism detection task.
 They used average sentence length, part of speech tags, average stop word number and the averaged word frequency class as input features for their linear discriminant analysis and support vector machine (SVM) models.
@@
 Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and its hyperparameters.
+Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.
 
-\paragraph{Model A.}Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
+\paragraph{Model A.} Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
 We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values.

### 2017-06-02 paper/paper.tex
Chap 5.

@@
 Average token length, sentence length, POS tag counts and bag of maximum 100 words (with stop words) served as a features.
+If the number of authors was unknown, it was randomly generated from $(0, 0.0003\times{l(d\in{D})})$ and increased by $1$ if the result was $0$.
 
@@
 In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}.
-Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and its hyperparameters.
+Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and clustering algorithm's hyperparameters.
 Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.
@@
 	\caption{Results on the intrinsic plagiarism detection task.
-The standard errors both for $F_\mathrm{\mu}$ and $F_\mathrm{M}$ are for Model A within $\pm0.04$ and for Model B within $\pm0.06$ at the 95\% confidence.
+The standard errors both for $F_\mathrm{\mu}$ and $F_\mathrm{M}$ are for Model A within $\pm0.04$ and for Model B within $\pm0.06$.
 Results of models denoted with * were obtained on the PAN 2016 test set which was not available to us.}
@@
 			Single-author dummy BL 	& 0.13 & \textbf{1.00} & 0.22 & 0.13 & \textbf{1.00} & 0.22 \\
-			Stochastic dummy BL 	& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & \textbf{0.25} \\
+			Stochastic dummy BL 	& 0.11 & 0.09 & 0.09 & 0.08 & 0.09 & 0.06 \\
 			Simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
@@
 			\midrule			
-			Model A 				& 0.18 & 0.43 & \textbf{0.25} & 0.18 & 0.43 & 0.24 \\			
+			Model A 				& 0.18 & 0.43 & \textbf{0.25} & 0.18 & 0.43 & \textbf{0.24} \\			
 			Model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
@@
 	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (task \emph{c}) numbers of authors.
-The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$ at the 95\% confidence.
+The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$.
 Results of models denoted with * were obtained on the PAN 2016 test set which was not available to us.}
@@
 By trying a more honest approach with predicting the number of clusters the BCubed $F_1$-score drops below $0.5$.
+The results of \textit{stohastic dummy} baseline for all tasks are obtained over the 50 runs, as well as for \textit{simple} baseline in task \emph{c}.
 
-{Intrinsic plagiarism detection results}
+For both Models A and B we calculated standard errors and wanted to obtain 95\% t-based confidence intervals.
+Since the sample sizes from all test sets but \emph{a} are less than 30, a normality test\footnote{\url{https://docs.scipy.org/doc/scipy-0.19.0/reference/generated/scipy.stats.normaltest.html}} at $p=0.05$ was performed first.
+The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution.
+In test of Model B's both $F_1$-scores, the data provided enough evidence to reject the null hypothesis.
+
+Although the Model A achieved the highest micro and macro-averaged $F_1$-scores on te task \emph{a}, this task seemed to be very difficult.
+$F_1$-scores of Model A are only slightly above the \textit{single-author dummy} baseline and 95\% lower limit for macro-$F_1$ is $0.15$.
+Model A also achieved the best, but actually not very good performance on the task \emph{b} with $(0.57, 0.67)$ 95\% confidence interval.
+Although Model B behaved reasonably well on the task \emph{c}, a better way of estimating a true number of clusters is needed.
 
 don't forget to describe tolerance
-
-{Author diarization results}
 
@@
 
-Conclusion is the last enumerated section of the paper.
-It should not exceed half of a column and is typically split into 2--3 paragraphs.
-No new information should be presented in the conclusion; this section only summarizes and concludes the paper.
-
 % 2-nd paragraph further work

### 2017-06-02 paper/paper.tex
no message

--- 2017-06-02 paper/paper.tex
@@
 
-% TODO: replace model A with Model A, for B as well
-% TODO: replace $n$-gram and \emph{n}-gram with n-gram, as it is common in literature
+% TODO: replace $n$-gram with n-gram, as it is common in literature
 % TODO: hange bi-grams to bigrams and tri-grams to trigrams
-% TODO: suggestion: remove \texttt-s 
+% TODO: suggestion: remove \texttt-s fromscikit-learn and NLTK
 % TODO: change \texit-s ti \emph-s
 % TODO: explain BFE training in The proposed approach
-% TODO: consistency: use only "training set" and "test set" (not dataset, not train) (https://en.wikipedia.org/wiki/Test_set)
-% TODO: convert Related work to present
+% TODO: move repsoitory to organization
+% TODO: write something about the seeming inappropriateness of BCubed
+% TODO: uppercase Task a ...
 
@@
 The term \emph{intrinsic} means that a decision whether a part of the document is plagiarized has to be made only by analysing the given document, without any comparisons with external sources.
-In the rest of the paper we refer to this subtask as task \emph{a}.
+In the rest of the paper we refer to this subtask as Task \emph{a}.
 
@@
 In the second subtask we need to segment a given document and group identified segments by author.
-In the rest of the paper we refer to the second subtask as a task \emph{b}.
+In the rest of the paper we refer to the second subtask as a Task \emph{b}.
 The third subtask differs from the second one in the fact that exact number of authors is unknown.
-In the rest of the paper we refer to the third subtask as a task \emph{c}.
+In the rest of the paper we refer to the third subtask as a Task \emph{c}.
 
@@
 
-\citet{stamatatos-2009b} created a feature vector of normalized occurrence of character tri-grams in the whole document.
-That vector represented a document's profile.
-Using a sliding window of fixed length he created same profiles for every window position and compared them with the profile of the whole document.
-The result of the comparison was an output from a style change function whose peaks indicate positions in the document where style changes occur.
-All values above the predefined passage criterion were considered a result of plagiarism.
-That approach was unsupervised.
+\citet{stamatatos-2009b} uses normalized occurrence of character tri-grams as features to represent a document's profile.
+Using a sliding window of fixed length he creates such profiles for every window position and compares them with the profile of the whole document.
+The result of the comparison is a style change function whose peaks indicate positions in the document where style changes occur.
+All values above some predefined threshold are considered indicators of plagiarism.
 
-\citet{rahman-2015} classified sections of documents from PAN 2011 dataset with the help of SVM.
-Those sections were again obtained by sliding a window of fixed length over the document.
-He also proposed a new kind of information theoretical features - entropy, relative entropy, correlation coefficient and $n$-gram frequency class calculated from character tri-gram frequency profiles of each window and the whole document.
-{{{He also used function word bi-gram and tri-gram frequency profiles with $1$, $2$, $3$ and $4$ skips.}}} The value of the style change function introduced by \citet{stamatatos-2009b} was also incorporated into the feature vectors.
+\citet{rahman-2015} classifies sections of documents from the PAN 2011 dataset with the help of an SVM.
+Those sections are again obtained by sliding a window of fixed length over the document.
+He also proposed new kinds of information theoretical features - entropy, relative entropy, correlation coefficient and $n$-gram frequency class calculated from character tri-gram frequency profiles of each window and the whole document.
+The approach also uses function word bi-gram and tri-gram frequency profiles with $1$, $2$, $3$ and $4$ skips.
+The value of the style change function introduced by \citet{stamatatos-2009b} is also incorporated into the feature vectors.
 
-\citet{stein-2011} defined IPD as a one class classification problem where the parts of text written by the main author is associated to the target class and the other parts of text are outliers.
-To find them, they estimated probability distributions of various stylistic features for the target class and outliers.
-Then a naive Bayes' algorithm was applied to feature vectors whose values lied outside the predefined uncertainty intervals.
+\citet{stein-2011} defined IPD as a one class classification problem where the parts of text written by the main author are associated to the target class and the other parts of text are outliers.
+To find them, they estimate probability distributions of various stylistic features for the target class and outliers.
+Then a naive Bayes' algorithm is applied to feature vectors whose values lie outside the predefined uncertainty intervals.
 Additional outlier post-processing methods were also tested.
@@
 
-\citet{brooke-2013} concluded that a very good initial segmentation of text, at least in poems written by T.
+\citet{brooke-2013} conclude that a very good initial segmentation of text, at least in poems written by T.
 S.
-Elliot, is needed for a good performance of their modified k-means algorithm in clustering of voices.
-Except common character, lexical and syntactic features, they used features such as average frequency in a large  external corpus \citep{brants-2006}.
+Elliot, is needed for good performance of their modified k-means algorithm in clustering of voices.
+Except common character, lexical and syntactic features, they use features such as average frequency in a large external corpus \citep{brants-2006}.
 One of the most promising feature they considered is the centroid of $20$ dimensional distributional vectors obtained by applying latent semantic analysis on a large web corpus \cite{landauer-1997}.
@@
 The works by \citet{kuznetsov-2016} and \citet{sittar-2016} were submitted on the PAN 2016 competition for three aforementioned tasks.
-For the task \emph{a}, \citet{kuznetsov-2016} trained a Gradient Boosting Regression Trees (GBRT) model on PAN 2011 dataset as a style change function used for threshold based outlier detection.
+For the Task \emph{a}, \citet{kuznetsov-2016} trained a Gradient Boosting Regression Trees (GBRT) model on the PAN 2011 dataset as a style change function used for threshold based outlier detection.
 Every sentence was vectorized using word frequencies, $n$-gram frequencies, punctuation symbols and the universal POS tags count, sentence length and mean length of sentence words.
-The final input to the model was concatenation of the center sentence vector and ones from the context of size $\pm2$.
-In task \emph{b} they used a Hidden Markov Model with Gaussian Emissions for document segmentation over the same sentence scores from task \emph{a}.
-To estimate the unknown number of authors $n$ in task \emph{c}, they chose $n\in\{2..20\}$ which maximizes their cluster discrepancy measure $Q(n)$.
+The final input to the model is the concatenation of the center sentence vector and vectors representing the the context of size $\pm2$.
+In Task \emph{b} they used a Hidden Markov Model with Gaussian Emissions for document segmentation over the same sentence scores from Task \emph{a}.
+To estimate the unknown number of authors $n$ in Task \emph{c}, they define a cluster discrepancy measure $Q(n)$ and choose the $n\in\{2..20\}$ which maximizes the measure.
 
-\citet{sittar-2016} used k-means algorithm to cluster \textit{ClustDist} scores of each sentence, where the number of groups was equal to the known number of authors in tasks \emph{a} and \emph{b}.
-In task \emph{c}, a number of groups was generated randomly.
-Although they defined a \emph{ClustDist} score for a single sentence as an average distance between current and every other sentence vector, which is again a similar concept like a style change function, in the provided example they used only a sum of unknown distance measures.
-$15$ features in total were used for sentence vectorization, including average word and sentence lengths, count and ratios of characters, digits uppercase letters, spaces and tabs.
+\citet{sittar-2016} use the k-means algorithm use a measure called \emph{ClustDist} to compute distaces between sentences and the document.
+For Task \emph{c}, the number of groups for clustering is generated randomly for each document.
+Although they defined a \emph{ClustDist} score for a single sentence as the average distance between the current and every other sentence vector, which is again a similar concept like a style change function, in the provided example they used only a sum of unknown distance measures.
+The sentences are represented with $15$ lexical features including average word and sentence lengths, counts and ratios of characters, digits, uppercase letters, spaces and tabs.
 
@@
 \begin{itemize}
-	\item \textit{Character tri-grams}.
+	\item \emph{Character tri-grams}.
 Frequencies of $n$-grams on character level have been very useful in quantifying the writing style \citep{stamatatos-2009b}.
@@
 Maximal dimension of this feature vector was set to $200$.
-	\item \textit{Stop words}.
-According to \citet{stamatatos-2009a}, sometimes also called \textit{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
+	\item \emph{Stop words}.
+According to \citet{stamatatos-2009a}, sometimes also called \emph{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
 They are used unconsciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' \citep{burrows-1987,argamon-2005}.
 We used frequencies of $156$ English stop words available in \texttt{NLTK}.
-	\item \textit{Special characters}.
+	\item \emph{Special characters}.
 We used counts of all character sequences which satisfied a regular expression defined as \verb/[^\\w]{1,4}/.
 Although character $n$-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose since \citet{koppel-2009} mentioned that authors can have different punctuation habits.
-	\item \textit{POS tag counts}.
+	\item \emph{POS tag counts}.
 This is syntactic feature which \citet{koppel-2009} and \citet{stamatatos-2009a} also identified as a discriminative one in authorship analysis and it was used by \citet{kuznetsov-2016}.
 We used all $12$ tags from the universal tag set
-	\item \textit{Average token length}.
+	\item \emph{Average token length}.
 Used by \citet{kuznetsov-2016}, \citet{sittar-2016},  \citet{brooke-2012} and \citet{stein-2011}.
 \citet{koppel-2009} characterized this feature as a complexity measure.
-	\item \textit{Bag of Words}.
+	\item \emph{Bag of Words}.
 Bag of words text representation more captures content, rather than style \citep{stamatatos-2009a}.
@@
 Counts of a maximum of 100 unigrams were used.
-	\item \textit{Type-token ratio}.
+	\item \emph{Type-token ratio}.
 We wanted to use that feature to measure the vocabulary richness in a token's context, but after we finished with performance evaluations we realized that there was a bug in implementation and its impact on final results was unknown to us.
@@
 The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens.
-The number of clusters was equal to the number of authors in tasks \emph{a} and \emph{b}, but in task \emph{c} it was unknown.
+The number of clusters was equal to the number of authors in tasks \emph{a} and \emph{b}, but in Task \emph{c} it was unknown.
 We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks.
-In the first variant of our approach for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
+In the first variant of our approach for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for Task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
 In the second variant we used k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule.
@@
 
-Mention cofidences.
-
-feature init test
-
-repo link - move from Ivan1024 to an organization
-
 For experiments, we have used the three PAN 2016 training sets.
@@
 In addition to the $2$ models from the teams that took part in solving the author diarization problem on the PAN 2016 competition, we defined $3$ baselines for evaluation purposes.
-The first baseline, \emph{single-author dummy baseline}, always assigns the whole document a single author label, or, in the case of intrinsic plagiarism detection, it labels the whole document as plagiarism.
-The second baseline, \emph{stochastic dummy baseline}, learns the average total lengths of authorial parts over all documents ranked by the length of their parts.
+The first baseline, \emph{Single-author dummy baseline}, always assigns the whole document a single author label, or, in the case of intrinsic plagiarism detection, it labels the whole document as plagiarism.
+The second baseline, \emph{Stochastic dummy baseline}, learns the average total lengths of authorial parts over all documents ranked by the length of their parts.
 For prediction, by modelling a Markov chain, it generates segmentations with similar label frequencies and predefined expected lengths.
@@
 
-In the third baseline, \textit{simple fixed baseline}, we used default k-means clustering of vectorized document's sentences.
+In the third baseline, \emph{Simple fixed baseline}, we used default k-means clustering of vectorized document's sentences.
 Average token length, sentence length, POS tag counts and bag of maximum 100 words (with stop words) served as a features.
@@
 We performed initial testing of usefulness of all features except for the accidentally wrongly implemented type-token ratio which was added afterwards.
-For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the dataset for task \emph{b}.
-As we were adding feature by feature, BCubed precision was becoming higher so we decided to use all features for model A in all tasks.
+For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the dataset for Task \emph{b}.
+As we were adding feature by feature, BCubed precision was becoming higher so we decided to use all features for Model A in all tasks.
 We don't know the exact impact of the wrongly implemented type-token ratio feature.
@@
 Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and its hyperparameters.
-Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.
+Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters being equal across all tasks.
 
@@
 We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values.
-The best result for task \emph{a} was $cs_a=16$ and for task \emph{b} $cs_b=140$.
-For task \emph{c}, we left $cs_c=140$ as for task \emph{b}.
+The best result for Task \emph{a} was $cs_a=16$ and for Task \emph{b} $cs_b=140$.
+For Task \emph{c}, we left $cs_c=140$ as for Task \emph{b}.
 This hyperparameter probably depends on document's length to a certain extent.
@@
 
-In task \emph{a}, we used 50\% of dataset as a training set, and other half as a test set.
+In Task \emph{a}, we used 50\% of dataset as a training set, and other half as a test set.
 Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results.
@@
 
-In task \emph{b} we also split dataset in two half.
+In Task \emph{b} we also split dataset in two half.
 Grid search for the best hyperparameters was performed for agglomerative clustering.
@@
 
-For task \emph{c} we should have somehow determine the number of clusters.
+For Task \emph{c} we should have somehow determine the number of clusters.
 Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e.
@@
 
-The best results on task \emph{c} were obtained with DBSCAN, and for other ones they were very low.
+The best results on Task \emph{c} were obtained with DBSCAN, and for other ones they were very low.
 We noticed that the estimated number of clusters with the best hyerparameters (\texttt{eps=100, min\_samples=71, metric="manhattan"}) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
@@
 
-Since the best achieved Bcubed $F$ measure (0.61) is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search in task \emph{c} for DBSCAN, but now we set the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
+Since the best achieved Bcubed $F$ measure (0.61) is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search in Task \emph{c} for DBSCAN, but now we set the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
 Finally, from all results on training set we chose (\texttt{eps=$0.23$, min\_samples=64, metric="cosine"}) for the final hyperparameters.
@@
 
-For task \emph{c} we have implemented a simple wrapper for the k-means algorithm that tries to predict the correct number of authors.
+For Task \emph{c} we have implemented a simple wrapper for the k-means algorithm that tries to predict the correct number of authors.
 It computes the k-means error for each number $k$ in the specified range for the number of clusters.
@@
 \begin{table*}
-	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (task \emph{c}) numbers of authors.
+	\caption{Results on the author diarization task for known (Task \emph{b}) and unknown (Task \emph{c}) numbers of authors.
 The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$ at the 95\% confidence.
@@
 For author diarization with known and unknown numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.
-It should be noted that the evaluated Model B uses a fixed number of clusters $k=2$ for task \emph{c} and that the results are actually not very good.
+It should be noted that the evaluated Model B uses a fixed number of clusters $k=2$ for Task \emph{c} and that the results are actually not very good.
 By trying a more honest approach with predicting the number of clusters the BCubed $F_1$-score drops below $0.5$.

### 2017-06-02 software/inpladesys/models/dummy_stochastic_author_diarizer.py

@@ -8,7 +8,7 @@ import random
 
 
 class DummyStochasticAuthorDiarizer(AbstractAuthorDiarizer):
-    def __init__(self, author_count=5, average_segment_length=500, random_state=-1):
+    def __init__(self, author_count=5, average_segment_length=200, random_state=-1):
         self.random_state = random_state
         self.n = author_count
         self.asl = average_segment_length
@@ -52,5 +52,5 @@ class DummyStochasticAuthorDiarizer(AbstractAuthorDiarizer):
             Segment(offset=offset, length=len(document) - offset, author=author))
         segm = Segmentation(self.n, segments)
         if(segm.author_count==2):
-            fix_segmentation_labels_for_plagiarism_detection(segm, plagiarism_majority=True)
+            fix_segmentation_labels_for_plagiarism_detection(segm, plagiarism_majority=False)
         return segm

### 2017-06-02 software/tests1.py

@@ -19,7 +19,7 @@ dataset_dirs = [
     "../data/pan16-author-diarization-training-dataset-problem-c-2016-02-16"
 ]
 print("Loading dataset...")
-dataset_index = 2
+dataset_index = 0
 dataset = Pan16DatasetLoader(dataset_dirs[dataset_index]).load_dataset()
 
 models = [
@@ -87,7 +87,7 @@ for model in models:
             pred = m.predict(d)
             if dataset_index == 0:  # task a
                 #micro = MicroScorer(truth, pred)  # use Micro AND Macro Scorer for task a!!
-                macro = MicroScorer(truth, pred)  # use Micro AND Macro Scorer for task a!!
+                macro = MacroScorer(truth, pred)  # use Micro AND Macro Scorer for task a!!
                 modelsToScores[model.name] += np.array([macro.precision(), macro.recall(), macro.f1_score()])
 
             else:  # tasks b and c

### 2017-06-02 paper/paper.tex

@@
 For evaluation of intrinsic plagiarism detection, \citet{stein-2010} define multiple measures for different aspects of a system's performance The main measures are binary macro-averaged and micro-averaged precision ($P$), recall ($R$) and $F_1$-score.
-For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$ measures described by \citet{amigo-2009}, which are specialized for evaluation of clustering results.
+For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$-score described by \citet{amigo-2009}, which are specialized for evaluation of clustering results.
 The same measures were used for evaluation on the PAN 2016 competition \citep{rosso-2016}.
@@
 In addition to the $2$ models from the teams that took part in solving the author diarization problem on the PAN 2016 competition, we defined $3$ baselines for evaluation purposes.
-The first baseline, \emph{Single-author dummy baseline}, always assigns the whole document a single author label, or, in the case of intrinsic plagiarism detection, it labels the whole document as plagiarism.
-The second baseline, \emph{Stochastic dummy baseline}, learns the average total lengths of authorial parts over all documents ranked by the length of their parts.
+The first baseline, Single-author dummy baseline, always assigns the whole document a single author label, or, in the case of intrinsic plagiarism detection, it labels the whole document as plagiarism.
+The second baseline, Stochastic dummy baseline, learns the average total lengths of authorial parts over all documents ranked by the length of their parts.
 For prediction, by modelling a Markov chain, it generates segmentations with similar label frequencies and predefined expected lengths.
-As we will later describe, these baseline models seem to behaved quite competitively.
 
-In the third baseline, \emph{Simple fixed baseline}, we used default k-means clustering of vectorized document's sentences.
-Average token length, sentence length, POS tag counts and bag of maximum 100 words (with stop words) served as a features.
+In the third baseline, Simple baseline, we use default k-means clustering of vectorized document's sentences.
+Average token length, sentence length, POS tag counts and bag of at most $100$ words (including stop words) serve as features.
+If the number of authors is unknown, it is randomly generated from a uniform distribution $(0,0.0003\times{l(d\in{D})})$ and increased by $1$ if the result is $0$.
 
@@
 \subsection{Experimental setup}
+
 In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}.
-Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and its hyperparameters.
-Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters being equal across all tasks.
+Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and clustering algorithm's hyperparameters.
+Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.
 
-\paragraph{Model A.} Context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
+\paragraph{Model A.} 
+Sliding widow context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
 We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values.
@@
 For Task \emph{c}, we left $cs_c=140$ as for Task \emph{b}.
-This hyperparameter probably depends on document's length to a certain extent.
+%This hyperparameter probably depends on document's length to a certain extent.
 If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs.
@@
 For each algorithm we were examining, a grid search of its hyperparameters was performed on the training set.
-We selected an algorithm and hyperparameters that achieved the best performance on a training set (since this is an unsupervised approach), and reported a final performance on the test set.
+We selected an algorithm and hyperparameters that achieved the best performance on the training set (since this is an unsupervised approach), and reported the final performance on the test set.
 
-In Task \emph{a}, we used 50\% of dataset as a training set, and other half as a test set.
+In Task \emph{a}, we used $50\%$ of the dataset as a training set, and the other half as a test set.
 Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results.
 Other algorithms which we evaluated were Gaussian mixtures and hierarchical agglomerative clustering.
-Cosine affinity and average linkage with agglomerative clustering achieved the best performance on the training set and we report its result on the test set.
-We measured $F_M$ score described in subsection \ref{subsec:evaluation-measures}
+Cosine affinity and average linkage with agglomerative clustering achieved the best macro $F_1$ (described in subsection \ref{subsec:evaluation-measures}) performance on the training set and we report its result on the test set.
 
-In Task \emph{b} we also split dataset in two half.
+For Task \emph{b} we split the dtaset in two halves as well.
 Grid search for the best hyperparameters was performed for agglomerative clustering.
 The best performance on the training set was obtained with euclidean affinity and average linkage.
-
-For Task \emph{c} we should have somehow determine the number of clusters.
+For Task \emph{c} we should have somehow determined the number of clusters.
 Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e.
 this is not a hyperparameter which should be known in advance.
-Since we noticed that grid searches take a lot of time, we reduced a training set from 50\% to 10\% and repeated all experiments.
+Since we noticed that grid searches take a lot of time, we reduced a training set from $50\%$ to $10\%$ and repeated all experiments.
 We tested DBSCAN, affinity propagation, and mean shift algorithms.
 
-The best results on Task \emph{c} were obtained with DBSCAN, and for other ones they were very low.
-We noticed that the estimated number of clusters with the best hyerparameters (\texttt{eps=100, min\_samples=71, metric="manhattan"}) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
-In all grid searches we used BCubed $F$ measure and only DBSCAN achieved acceptable performance.
+The best results on Task \emph{c} were obtained with DBSCAN.
+We noticed that the number of clusters is best estimated with the best hyerparameters (\texttt{eps=100, min\_samples=71, metric="manhattan"}) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
+In all grid searches we used the BCubed $F_1$-score and only DBSCAN achieved acceptable performance.
 Our opinion is that this was a consequence of a larger number of smaller clusters which had a positive influence on BCubed precision and therefore on overall performance.
 
-Since the best achieved Bcubed $F$ measure (0.61) is not of practical use in real life appliactions if the number of clusters is always wrongly estimated, we decided to repeat the grid search in Task \emph{c} for DBSCAN, but now we set the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
-Finally, from all results on training set we chose (\texttt{eps=$0.23$, min\_samples=64, metric="cosine"}) for the final hyperparameters.
+Since the model with the best achieved Bcubed $F_1$-score ($0.61$) is not of practical use in real life applications because the number of clusters is always wrongly estimated, we decided to repeat the grid search in Task \emph{c} for DBSCAN, but this time we used the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
+Finally, from all results on training set we chose (\texttt{eps=0.23, min\_samples=64, metric="cosine"}) for the final hyperparameters.
 This wasn't the best combination, but it produced relatively acceptable amount of noisy elements per document, and performed quite fast but again din't estimate the correct number of clusters in most cases.
-If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size 10 (5 on each side), or the majority label from all samples if samples in the context weren't clustered.
+If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context weren't clustered.
 
-\paragraph{Model B.} For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).
+\paragraph{Model B.} 
+For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).
 The length of the sliding window is set to $120$ characters.
@@
 \begin{table*}
-	\caption{Results on the author diarization task for known (Task \emph{b}) and unknown (Task \emph{c}) numbers of authors.
-The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$ at the 95\% confidence.
+	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (Task \emph{c}) numbers of authors.
+The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$.
 Results of models denoted with * were obtained on the PAN 2016 test set which was not available to us.}
@@
 For author diarization with known and unknown numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.
-It should be noted that the evaluated Model B uses a fixed number of clusters $k=2$ for Task \emph{c} and that the results are actually not very good.
+It should be noted that the evaluated Model B uses a fixed number of clusters $k=2$ for task \emph{c} and that the results are actually not very good.
 By trying a more honest approach with predicting the number of clusters the BCubed $F_1$-score drops below $0.5$.
+The results of Stohastic dummy baseline for all tasks are obtained over the 50 runs, as well as for Simple baseline in task \emph{c}.
 
-{Intrinsic plagiarism detection results}
+For both Models A and B we calculated standard errors and wanted to obtain $95\%$ t-based confidence intervals.
+Since the sample sizes from all test sets but \emph{a} are less than $30$, a normality test\footnote{\url{https://docs.scipy.org/doc/scipy-0.19.0/reference/generated/scipy.stats.normaltest.html}} at $p=0.05$ was performed first.
+The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution.
+In test of Model B's both $F_1$-scores, the data provided enough evidence to reject the null hypothesis.
 
-don't forget to describe tolerance
-
-{Author diarization results}
+Although the Model A achieved the highest micro and macro-averaged $F_1$-scores on te task \emph{a}, this task seemed to be very difficult.
+$F_1$-scores of Model A are only slightly above the \textit{single-author dummy} baseline and $95\%$ lower limit for macro-$F_1$ is $0.15$.
+Model A also achieved the best, but actually not very good performance on the task \emph{b} with $(0.57, 0.67)$ $95\%$ confidence interval.
+Although Model B behaved reasonably well on the task \emph{c}, a better way of estimating a true number of clusters is needed.
 

### 2017-06-02 paper/paper.tex
no comment

--- 2017-06-02 paper/paper.tex
@@
 
-don't forget to describe tolerance
-
 \section{Conclusion}
-
-hard task, a lot of space for improvement
 
@@
 
-We have presented some ideas that are not completely refined but, based on the data we have available, seem to give comparable, or even better results that the other two approaches that tired to tackle the same problem.
+We have presented some ideas that are not completely explored but, based on the data we have available, seem to give comparable, or even better results than the other two approaches that tired to tackle the same problem.
+There is a lot of room for improvement of our approach, as well as in exploring other new ideas.
 
- and that there is a lot of room for improvement for our approach
-
- as well as in exploring other
+For further work, we could include more basic features, try other clustering  algorithms and use more systematic approach for choosing (unknown) hyperparameters.
+Our transformation could be tested on other authorship analysis tasks.
 

### 2017-06-02 paper/paper.tex

--- 2017-06-02 paper/paper.tex
@@
 
-hard task, a lot of space for improvement
-
 Our results, as well as the the results of others, suggest that author diarization and intrinsic plagiarism detection are very challenging problems.
@@
 
-We have presented some ideas that are not completely refined but, based on the data we have available, seem to give comparable, or even better results that the other two approaches that tired to tackle the same problem.
+We have presented some ideas that are not completely explored but, based on the data we have available, seem to give comparable, or even better results than the other two approaches that tried to tackle the same problem.
+There is a lot of room for improvement of our approach, as well as in exploring other new ideas.
 
- and that there is a lot of room for improvement for our approach
-
- as well as in exploring other
+For further work, it would be good to search for more useful basic features, make a deeper examination of the feature transformation, try other clustering algorithms and use more systematic approach for choosing hyperparameters.
+It would be also interesting to try the trainable feature transformation approach on other authorship analysis problems.
 

### 2017-06-02 paper/paper.tex
no comment

@@
 
-\name{Ivan Grubišić, Milan Pavlović, Author3}
+\name{Ivan Grubišić, Milan Pavlović, Mate Šimović}
 
@@
 Unska 3, 10000 Zagreb, Croatia\\ 
-\texttt{\{ivan.grubisic, milan.pavlovic, \}@fer.hr}\\
+\texttt{\{ivan.grubisic, milan.pavlovic, mate.simovic\}@fer.hr}\\
 }
@@
 We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window.
-There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt if for clustering with a traineable feature transformation.
+There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt if for clustering with a trainable feature transformation.
 We have evaluated our approach on the available datasets from PAN 2016.
@@
 First they used normalized cuts algorithm with cosine similarity to obtain initial clusters of segments which were represented only by normalized counts of synonyms from Hebrew synsets.
-Samples from initial clusters were separated into core and non-core samples via an iterative procedure, and the core ones were labelled A SVM classifier was used to classify non-core samples, but now represented with bag-of-words feature vectors.
+Samples from initial clusters were separated into core and non-core samples via an iterative procedure, and the core ones were labelled.
+A SVM classifier was used to classify non-core samples, but now represented with bag-of-words feature vectors.
 The whole approach resulted with very good clusters.
@@
 Every sentence was vectorized using word frequencies, $n$-gram frequencies, punctuation symbols and the universal POS tags count, sentence length and mean length of sentence words.
-The final input to the model is the concatenation of the center sentence vector and vectors representing the the context of size $\pm2$.
+The final input to the model is the concatenation of the center sentence vector and vectors representing the context of size $\pm2$.
 In Task \emph{b} they used a Hidden Markov Model with Gaussian Emissions for document segmentation over the same sentence scores from Task \emph{a}.
@@
 
-\citet{sittar-2016} use the k-means algorithm use a measure called \emph{ClustDist} to compute distaces between sentences and the document.
+\citet{sittar-2016} use the k-means algorithm and a measure called \emph{ClustDist} to compute distaces between sentences and the document.
 For Task \emph{c}, the number of groups for clustering is generated randomly for each document.
@@
 
-Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations., i.e.
+Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e.
 $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$.
@@
 
-For evaluation of intrinsic plagiarism detection, \citet{stein-2010} define multiple measures for different aspects of a system's performance The main measures are binary macro-averaged and micro-averaged precision ($P$), recall ($R$) and $F_1$-score.
+For evaluation of intrinsic plagiarism detection, \citet{stein-2010} define multiple measures for different aspects of a system's performance.
+The main measures are binary macro-averaged and micro-averaged precision ($P$), recall ($R$) and $F_1$-score.
 For evaluating author diarization, we use \emph{BCubed} precision, recall and $F_1$-score described by \citet{amigo-2009}, which are specialized for evaluation of clustering results.
@@
 Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_\mathrm{b}}, f_\mathrm{t}:\Phi_{n_\mathrm{b}}\rightarrow \Phi_{n_\mathrm{t}}, f_\mathrm{c}:\Phi_{n_\mathrm{t}}\rightarrow C)$.
-Here $\Delta$ is the tokenized document domain as defined in section \ref{sec:author-diraization}.
-$\Phi_{n_\mathrm{b}}$ and $\Phi_{n_\mathrm{t}}$ are sets of variable-length sequences of feature vectors with dimension $n_\mathrm{b}$ and $n_\mathrm{t}$ respectively.
+Here $\Delta$ is the tokenized document domain as defined in section \ref{sec:author-diraization} $\Phi_{n_\mathrm{b}}$ and $\Phi_{n_\mathrm{t}}$ are sets of variable-length sequences of feature vectors with dimension $n_\mathrm{b}$ and $n_\mathrm{t}$ respectively.
 $n_\mathrm{b}$ and $n_\mathrm{t}$ can either be fixed or depend on the document being processed.
@@
 We develop two variants of our model which we will refer to as \emph{Model A} and \emph{Model B}.
-They are mainly differentiated by the the training of the basic feature extractor and feature transformation and in the feature transformation.
-Model B utilizes a trainable feature transformation that requires a fixed basic feature space.
-Therefore, the basic feature extractor must be trained on the trained on the whole training set.
-Conversely, Model A's basic feature transformation can be trained specifically allowing for use of less more important features, but it can't use a feature transformation trainable on multiple documents.
+They are mainly differentiated by the fitting of the basic feature extractor, feature transformation learning and in the feature transformation.
+Model B utilizes a trainable feature transformation that requires a set of basic features with a fixed dimension.
+Therefore, the basic feature extractor must be fitted on the whole training set.
+Conversely, Model A's basic feature transformation can be performed specifically allowing for use of less more important features, but it can't use a feature transformation trainable on multiple documents.
 In both approaches basic features are extracted from a sliding window which moves from token to token and includes the context of each token.
@@
 This is syntactic feature which \citet{koppel-2009} and \citet{stamatatos-2009a} also identified as a discriminative one in authorship analysis and it was used by \citet{kuznetsov-2016}.
-We used all $12$ tags from the universal tag set
+We used all $12$ tags from the universal tag set available in \texttt{NLTK}.
 	\item \emph{Average token length}.
@@
 
+%TODO potentially preprocessed
 \paragraph{Feature transformation.}
@@
 The transformation is implemented using TensorFlow\footnote{\url{https://www.tensorflow.org}}.
-Parameters are randomly initialized with values from a truncated normal distribution withe standard deviation $0.1$.
+Parameters are randomly initialized with values from a truncated normal distribution with standard deviation $0.1$.
 It is trained on-line (one document per optimization step) using RMSProp \citep{tielman-2012} with default parameters and learning rate $5\times 10^{-4}$.
@@
 We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks.
-In the first variant of our approach for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for Task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
-In the second variant we used k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule.
-This is described in more detail in section \ref{sec:experimental-results}.
+In Model A for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for Task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
+In Model B we used k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule.
+This is described in more detail in section \ref{sec:experimental-results}
 
@@
 In the third baseline, Simple baseline, we use default k-means clustering of vectorized document's sentences.
-Average token length, sentence length, POS tag counts and bag of at most $100$ words (including stop words) serve as features.
-If the number of authors is unknown, it is randomly generated from a uniform distribution $(0,0.0003\times{l(d\in{D})})$ and increased by $1$ if the result is $0$.
+Average token length, sentence length, universal POS tag counts and bag of at most $100$ words (including stop words) serve as features.
+If the number of authors is unknown, it is randomly generated from a uniform distribution $(0,0.0003\times{l(D)})$ and increased by $1$ if the result is $0$.
 
@@
 
-In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach}.
-Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and clustering algorithm's hyperparameters.
+In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach} Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and clustering algorithm's hyperparameters.
 Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.
@@
 
-For Task \emph{b} we split the dtaset in two halves as well.
+For Task \emph{b} we split the dataset in two halves as well.
 Grid search for the best hyperparameters was performed for agglomerative clustering.
@@
 The best results on Task \emph{c} were obtained with DBSCAN.
-We noticed that the number of clusters is best estimated with the best hyerparameters (\texttt{eps=100, min\_samples=71, metric="manhattan"}) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
+We noticed that the number of clusters  estimated with the best hyerparameters (\texttt{eps=100, min\_samples=71, metric="manhattan"}) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
 In all grid searches we used the BCubed $F_1$-score and only DBSCAN achieved acceptable performance.
@@
 For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).
-The length of the sliding window is set to $120$ characters.
+The length of the sliding window is set to $120$ tokens.
 Model B uses k-means clustering.
@@
 \begin{table*}
-	\caption{Results on the author diarization task for known (task \emph{b}) and unknown (Task \emph{c}) numbers of authors.
+	\caption{Results on the author diarization task for known (Task \emph{b}) and unknown (Task \emph{c}) numbers of authors.
 The standard errors for both tasks are for Model A within $\pm0.02$ and for Model B within $\pm0.05$.
@@
 
-We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures}.
-The results of our models are compared to the results of our baselines, a well as the results of the two teams that took part in the PAN 2016 competition for this problem.
-The results of the two teams have been evaluated on test sets that is not publicly available.
+We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures} The results of our models are compared to the results of our baselines, as well as the results of the two teams that took part in the PAN 2016 competition for this problem.
+The results of the two teams have been evaluated on test sets that are not publicly available.
 Only the training sets from the competition have been available to us.
 
-The results of evaluation for the intrinsic plagiarism problem are shown in table \ref{tab:results-task-a}.
-For author diarization with known and unknown numbers of authors, the results are shown in table \ref{tab:results-task-b-c}.
+The results of evaluation for the intrinsic plagiarism problem are shown in Table \ref{tab:results-task-a}.
+For author diarization with known and unknown numbers of authors, the results are shown in Table \ref{tab:results-task-b-c}.
 It should be noted that the evaluated Model B uses a fixed number of clusters $k=2$ for task \emph{c} and that the results are actually not very good.
@@
 
-Although the Model A achieved the highest micro and macro-averaged $F_1$-scores on te task \emph{a}, this task seemed to be very difficult.
-$F_1$-scores of Model A are only slightly above the \textit{single-author dummy} baseline and $95\%$ lower limit for macro-$F_1$ is $0.15$.
-Model A also achieved the best, but actually not very good performance on the task \emph{b} with $(0.57, 0.67)$ $95\%$ confidence interval.
-Although Model B behaved reasonably well on the task \emph{c}, a better way of estimating a true number of clusters is needed.
+Although the Model A achieved the highest micro and macro-averaged $F_1$-scores on the Task \emph{a}, this task seemed to be very difficult.
+$F_1$-scores of Model A are only slightly above the Single-author dummy baseline and lower $95\%$ limit for macro-$F_1$ is $0.15$.
+Model A also achieved the best, but actually not very good performance on the Task \emph{b} with $(0.57, 0.67)$ $95\%$ confidence interval.
+Although Model B behaved reasonably well on the Task \emph{c}, a better way of estimating a true number of clusters is needed.
 
@@
 
-\section*{Acknowledgements}
-
-If suitable, you can include the \emph{Acknowledgements} section before inserting the literature references  in order to thank those who helped you in any way to deliver the paper, but are not co-authors of the paper.
-
 \bibliographystyle{tar2016}

### 2017-06-03 paper/paper.tex
Final push before moving the repository

@@
 
-For further work, it would be good to search for more useful basic features, make a deeper examination of the feature transformation, try other clustering algorithms and use more systematic approach for choosing hyperparameters.
+For further work, it would be good to search for more useful basic features, make a deeper examination of the feature transformation, try other clustering algorithms and a use more systematic approach for choosing hyperparameters.
 It would be also interesting to try the trainable feature transformation approach on other authorship analysis problems.

### 2017-06-03 paper/paper.tex
Moved some sentences to the present tense

@@
 \paragraph{Clustering.}
-The final step in our approach was clustering of obtained feature vectors which represented stylistic contexts of tokens.
-The number of clusters was equal to the number of authors in tasks \emph{a} and \emph{b}, but in Task \emph{c} it was unknown.
+The final step in our approach is clustering of obtained feature vectors which represent stylistic contexts of tokens.
+The number of clusters is equal to the number of authors in tasks \emph{a} and \emph{b}, but in Task \emph{c} it is unknown.
 We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks.
 In Model A for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for Task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
-In Model B we used k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule.
+In Model B we use k-means for clustering in all tasks, and tried predicting the number of clusters based on the elbow rule.
 This is described in more detail in section \ref{sec:experimental-results}

### 2017-06-03 paper/paper.tex
no comment

@@
 % details for each component
-\paragraph{Tokenization.} As a preprocessing step, we tokenize each document using \texttt{NLTK}\footnote{\url{http://www.nltk.org}} by \citet{bird-2009} to obtain a sequence of tokens $D$.
+\paragraph{Tokenization.} As a preprocessing step, we tokenize each document using NLTK\footnote{\url{http://www.nltk.org}} by \citet{bird-2009} to obtain a sequence of tokens $D$.
 We also perform part-of-speech tagging with the same tool, to speed up basic feature extraction which we describe below.
@@
 They are used unconsciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' \citep{burrows-1987,argamon-2005}.
-We used frequencies of $156$ English stop words available in \texttt{NLTK}.
+We used frequencies of $156$ English stop words available in NLTK.
 	\item \emph{Special characters}.
@@
 This is syntactic feature which \citet{koppel-2009} and \citet{stamatatos-2009a} also identified as a discriminative one in authorship analysis and it was used by \citet{kuznetsov-2016}.
-We used all $12$ tags from the universal tag set available in \texttt{NLTK}.
+We used all $12$ tags from the universal tag set available in NLTK.
 	\item \emph{Average token length}.
@@
 The number of clusters is equal to the number of authors in tasks \emph{a} and \emph{b}, but in Task \emph{c} it is unknown.
-We tested various clustering algorithms available in \texttt{scikit-learn}\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks.
+We tested various clustering algorithms available in scikit-learn\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks.
 In Model A for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for Task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
@@
 We performed initial testing of usefulness of all features except for the accidentally wrongly implemented type-token ratio which was added afterwards.
-For testing purposes we used the implementation of the k-means algorithm from \texttt{scikit-learn} with the default settings and all documents from the dataset for Task \emph{b}.
+For testing purposes we used the implementation of the k-means algorithm from scikit-learn with the default settings and all documents from the dataset for Task \emph{b}.
 As we were adding feature by feature, BCubed precision was becoming higher so we decided to use all features for Model A in all tasks.
@@
 Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.
+All the source code for our experiments is available in our repository\footnote{\url{https://github.com/Coolcumber/inpladesys/}}.
 
@@
 Sliding widow context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
-We used a whole dataset and default implementation of k-means from \texttt{scikit-learn} and tested different values.
-The best result for Task \emph{a} was $cs_a=16$ and for Task \emph{b} $cs_b=140$.
-For Task \emph{c}, we left $cs_c=140$ as for Task \emph{b}.
+We used a whole dataset and default implementation of k-means from scikit-learn and tested different values.
+The best result for Task \emph{a} was $\mathit{cs}_\mathrm{a}=16$ and for Task \emph{b} $\mathit{cs}_\mathrm{b}=140$.
+For Task \emph{c}, we left $\mathit{cs}_\mathrm{c}=140$ as for Task \emph{b}.
 %This hyperparameter probably depends on document's length to a certain extent.
@@
 Finally, from all results on training set we chose (\texttt{eps=0.23, min\_samples=64, metric="cosine"}) for the final hyperparameters.
-This wasn't the best combination, but it produced relatively acceptable amount of noisy elements per document, and performed quite fast but again din't estimate the correct number of clusters in most cases.
+This wasn't the best combination, but it produced relatively acceptable amount of noisy elements per document, and performed quite fast but again didn't estimate the correct number of clusters in most cases.
 If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context weren't clustered.
@@
 All the hyperparameters are selected manually by experimenting on the development dataset, which is approximately $70\%$ of the available dataset.
-$70\%$ of the development set was used for training basic feature extractors and the transformation.
+$70\%$ of the development set was used for fitting basic feature extractors and learning the transformation.
 Considering the results on the validation part of the development set, not very large numbers of iterations seem to be more beneficial.
@@
 By trying a more honest approach with predicting the number of clusters the BCubed $F_1$-score drops below $0.5$.
-The results of Stohastic dummy baseline for all tasks are obtained over the 50 runs, as well as for Simple baseline in task \emph{c}.
+The results of Stohastic dummy baseline for all tasks are obtained over the 50 runs, as well as for Simple baseline in Task \emph{c}.
 

### 2017-06-03 paper/paper.tex
no comment

@@
 The term \emph{intrinsic} means that a decision whether a part of the document is plagiarized has to be made only by analysing the given document, without any comparisons with external sources.
+This was our main motivation for solving this and other subtasks.
 In the rest of the paper we refer to this subtask as Task \emph{a}.
@@
 The number of clusters is equal to the number of authors in tasks \emph{a} and \emph{b}, but in Task \emph{c} it is unknown.
-We tested various clustering algorithms available in scikit-learn\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks.
+We tested several clustering algorithms available in scikit-learn\footnote{\url{http://scikit-learn.org}} Python toolkit by \citet{scikit-learn} in all tasks.
 In Model A for tasks  \emph{a} and \emph{b} we propose hierarchical agglomerative clustering, and for Task \emph{c} DBSCAN algorithm which estimates the number of clusters automatically.
@@
 We selected an algorithm and hyperparameters that achieved the best performance on the training set (since this is an unsupervised approach), and reported the final performance on the test set.
+We didn't include the k-means algorithm in clustering model selection since we used it for context size estimation.
 
@@
 Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results.
-Other algorithms which we evaluated were Gaussian mixtures and hierarchical agglomerative clustering.
-Cosine affinity and average linkage with agglomerative clustering achieved the best macro $F_1$ (described in subsection \ref{subsec:evaluation-measures}) performance on the training set and we report its result on the test set.
+Other algorithm which we evaluated was hierarchical agglomerative clustering which achieved the best macro $F_1$ (described in subsection \ref{subsec:evaluation-measures}) with cosine affinity and average linkage on the train set.
+We report its result on the test set.
 
@@
 Since we noticed that grid searches take a lot of time, we reduced a training set from $50\%$ to $10\%$ and repeated all experiments.
-We tested DBSCAN, affinity propagation, and mean shift algorithms.
+We tested DBSCAN and affinity propagation algorithms.
 
@@
 Finally, from all results on training set we chose (\texttt{eps=0.23, min\_samples=64, metric="cosine"}) for the final hyperparameters.
-This wasn't the best combination, but it produced relatively acceptable amount of noisy elements per document, and performed quite fast but again didn't estimate the correct number of clusters in most cases.
+This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document, and performed quite fast but again didn't estimate the correct number of clusters in most cases.
 If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context weren't clustered.

### 2017-06-04 paper/paper.tex
no comment

@@
 As its feature transformation $f_\mathrm{t}$, Model A uses feature scaling to zero mean and unit variance for each document separately.
-Model B uses a trainable transformation which requires a fixed basic feature space.
+Model B uses a trainable transformation which requires a basic feature space of fixed dimension.
 Let $(\vect{b}_i)_{i=1}^n = f_\mathrm{b}(D)$ be a sequence of basic feature vectors and $(\vect{b}_i')_{i=1}^n$ the corresponding sequence of potentially preprocessed basic feature vectors with elements from $\mathbb{R}^{n_{b}'}$.
@@
 Grid search for the best hyperparameters was performed for agglomerative clustering.
-The best performance on the training set was obtained with euclidean affinity and average linkage.
+The best performance on the training set was obtained with Euclidean affinity and average linkage.
 For Task \emph{c} we should have somehow determined the number of clusters.

### 2017-06-04 software/inpladesys/models/feature_transformation/grouprepel_feature_transformer.py
Modified presentation, added test-pipeline-anim.py for GroupRepel animation

@@ -13,6 +13,7 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
                  input_dimension=None,
                  nonlinear_layer_count=0,
                  nonlinearity=tf.nn.tanh,
+                 a = 0.5,
                  learning_rate=1e-3,
                  iteration_count=10000,
                  regularization=1,
@@ -24,6 +25,8 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
 
         self.x, self.labels, self.y = [None] * 3
         self.train_step_nd, self.loss_nd = [None] * 2
+
+        self.a=a
 
         def initialize(input_dimension):
             self.graph = tf.Graph()
@@ -168,9 +171,8 @@ class GroupRepelFeatureTransformer(AbstractFeatureTransformer):
         centroid_loss = get_centroid_loss(centroids, centroid_count)
         r_loss = sum(tf.reduce_mean(p ** 2) for p in r_params)
 
-        a = 0.5
-        group_loss = a * group_loss + 1e-6
-        centroid_loss = (1 - a) * centroid_loss + 1e-6
+        group_loss = self.a * group_loss + 1e-6
+        centroid_loss = (1 - self.a) * centroid_loss + 1e-6
         loss = centroid_loss + group_loss #+ 0.5*r_loss  # +
         # 0.2 * tf.reduce_mean(tf.reduce_sum(centroids**2, axis=1)) + r_loss
         # loss = 1/(1/group_loss + 1/centroid_loss)

### 2017-06-04 software/inpladesys/models/pipeline_author_diarizer.py

@@ -19,7 +19,7 @@ class PipelineAuthorDiarizer():
         self.cacher = Cacher.dummy() if cacher is None else cacher
         self.bfe_trained = False
 
-    def train(self, dataset: Dataset):
+    def train(self, dataset: Dataset, animate=False):
         @self.cacher("preprocessed-training-labels")
         def get_bydoc_labels(bydoc_tokens, segmentations):
             o2a = lambda i, offset: segmentations[i].offsets_to_authors(offset)
@@ -46,7 +46,7 @@ class PipelineAuthorDiarizer():
         print("(4/4) Training feature transformer...")
         #bydoc_features = [preprocessing.scale(f) for f in bydoc_features]
         X, Y = bydoc_features[:], bydoc_labels[:]
-        if True:
+        if not animate:
             self.feature_transformer.fit(X, Y)
         else:
             import matplotlib.pyplot as plt

### 2017-06-04 software/test-pipeline-anim.py

@@ -1,0 +1,212 @@
+from inpladesys.datasets import Pan16DatasetLoader
+from inpladesys.datatypes import Segmentation
+from inpladesys.models.basic_feature_extraction.basic_feature_extractor import BasicFeatureExtractor
+from inpladesys.models.feature_transformation import GroupRepelFeatureTransformer
+from inpladesys.models.pipeline_author_diarizer import PipelineAuthorDiarizer
+from inpladesys.models.clustering.auto_k_means import AutoKMeans
+from inpladesys.util.cacher import Cacher
+from sklearn.cluster import KMeans
+from inpladesys.evaluation import get_confusion_matrix, BCubedScorer, MicroScorer, MacroScorer
+import numpy as np
+from inpladesys.models.misc import perform_confidence_interval_test
+
+dataset_dirs = [
+    "../data/pan16-author-diarization-training-dataset-problem-a-2016-02-16",
+    "../data/pan16-author-diarization-training-dataset-problem-b-2016-02-16",
+    "../data/pan16-author-diarization-training-dataset-problem-c-2016-02-16"
+]
+
+
+def evaluate(params: dict, dataset_index: int, cache_dir=None, linear=True, test=False):
+    features_file_name = 'inpladesys/models/basic_feature_extraction/features_files/cng-sw-bow.json'
+    random_state = 0xBeeFeed
+    pl_params = dict()
+    pl_params['basic_feature_extractor'] = BasicFeatureExtractor(
+        features_file_name=features_file_name,
+        context_size=params['context_size'])
+    from inpladesys.models.feature_transformation import SimpleGroupRepelFeatureTransformer
+    pl_params['feature_transformer'] = GroupRepelFeatureTransformer(
+        output_dimension=params['gr_output_dimension'],
+        reinitialize_on_fit=False,
+        nonlinear_layer_count=params['gr-nonlinear_layer_count'],
+        a=0.001,
+        iteration_count=params['gr-iteration_count'],
+        learning_rate=2e-3,  # 5e-4
+        random_state=random_state)
+    print(str(pl_params['feature_transformer']))
[…]

### 2017-07-03 paper/paper.tex
Some minor changes

@@
 
-In author diarization document segments have to be clustered into $c$ clusters, where $c$ is the number of authors that may or may not be known to the system.
-We divide the segments from the true segmentation $S$ and the predicted segmentation $\hat{S}$ each into sets of segments $S_i$, $i=1..c$ and $\hat{S}_j, j=1..\hat{c}$, where $c$ is the true number of authors, and $\hat{c}$ the predicted number of authors.
+In author diarization, document segments have to be clustered into $c$ clusters, where $c$ is the number of authors that may or may not be known to the system.
+We divide the segments from the true segmentation $S$ and the predicted segmentation $\hat{S}$ each into sets of segments $S_i$, $i\in\{1..c\}$, and $\hat{S}_j$, $j\in\{1..\hat{c}\}$, where $c$ is the true number of authors, and $\hat{c}$ the predicted number of authors.
 We use the following \emph{BCubed} measures for evaluation:
 \begin{align}
-P_\mathrm{\mathrm{B}^3} &= \sum_{i=1}^c \frac{1}{l(S_i)}\sum_{j=1}^{\hat{c}}
-	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2 \\
-R_\mathrm{\mathrm{B}^3} &= \sum_{j=1}^{\hat{c}} \frac{1}{l(\hat{S}_j)}\sum_{i=1}^{c}
-	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2 \\
-F_\mathrm{\mathrm{B}^3} &= \frac{2}{P_\mathrm{\mathrm{B}^3}^{-1}+R_\mathrm{\mathrm{B}^3}^{-1}}.
+P_{\mathrm{B}^3} &= \sum_{i=1}^c \frac{1}{l(S_i)}\sum_{j=1}^{\hat{c}}
+	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2, \\
+R_{\mathrm{B}^3} &= \sum_{j=1}^{\hat{c}} \frac{1}{l(\hat{S}_j)}\sum_{i=1}^{c}
+	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2, \\
+F_{\mathrm{B}^3} &= \frac{2}{P_{\mathrm{B}^3}^{-1}+R_{\mathrm{B}^3}^{-1}}.
 \end{align}
@@
 Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i'))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_\mathrm{t}}$.
-We define the following loss in order to optimize the transformation $T$:
+In order to optimize the transformation $T$, we define the following loss:
 \begin{equation}
@@
 \begin{equation}
-\vect{\mu}_a = \frac{1}{N_a}\sum_{i=1}^n T(\vect{b}_i')[a_i=a]
+\vect{\mu}_a = \frac{1}{N_a}\sum_{i=1}^n T(\vect{b}_i')[a_i=a].
 \end{equation}	
@@
 			\cmidrule{2-7}
-			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_\mathrm{\mathrm{B}^3}$ \\
+			& $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_{\mathrm{B}^3}$ & $P_{\mathrm{B}^3}$ & $R_{\mathrm{B}^3}$ & $F_{\mathrm{B}^3}$ \\
 			\midrule

### 2017-07-04 paper/paper.tex
Fixes.

@@
 
-\title{Token-level author diarization using clustering of stylistic contexts}
+\title{Stylistic Context Clustering for Token-Level Author Diarization}
 
@@
 \begin{table}
-	\caption{Basic characteristics of training sets. * represents that there is a true author and plagiarism segments which don't have to originate from a single author.}
+	\caption{Basic characteristics of training sets. * represents that there is a true author and plagiarism segments which do not have to originate from a single author.}
 	\label{tab:dataset-characteristics}
@@
 The next step in the pipeline is the feature transformation $f_\mathrm{t}$ that maps the basic features to a space that they can be better clustered in.
-The dimension of the new feature space $n_\mathrm{t}$ generally doesn't equal $n_\mathrm{b}$.
+The dimension of the new feature space $n_\mathrm{t}$ generally does not equal $n_\mathrm{b}$.
 The final step in the pipeline is clustering denoted with $f_\mathrm{c}$.
@@
 Therefore, the basic feature extractor must be fitted on the whole training set.
-Conversely, Model A's basic feature transformation can be performed specifically allowing for use of less more important features, but it can't use a feature transformation trainable on multiple documents.
+Conversely, Model A's basic feature transformation can be performed specifically allowing for use of less more important features, but it can not use a feature transformation trainable on multiple documents.
 In both approaches basic features are extracted from a sliding window which moves from token to token and includes the context of each token.
@@
 We also perform part-of-speech tagging with the same tool, to speed up basic feature extraction which we describe below.
-We didn't use other preprocessing techniques such as lemmatization, stemming and stop word removal because they would take away a lot of stylometric data from text \cite{stamatatos-2009a}.
+We did not use other preprocessing techniques such as lemmatization, stemming and stop word removal because they would take away a lot of stylometric data from text \cite{stamatatos-2009a}.
 The final output from the tokenization step was a finite sequence $\{(t_i, o_i, l(t_i), \mathit{POS}_i)\}_{i=1}^n$ where $o_i$ is the offset of token $t_i$, $l(t_i)$ its length in characters and $\mathit{POS}_i$ its POS tag.
@@
 For the transformation $T$ we have tried a nonlinear transformations represented as neural networks with one or more hidden layers.
-We didn't explore nonlinear transformations much because they were slower and didn't give as good results as a linear transformation or an elementwise linear transformation:
+We did not explore nonlinear transformations much because they were slower and did not give as good results as a linear transformation or an elementwise linear transformation:
 \begin{align}
@@
 As we were adding feature by feature, BCubed precision was becoming higher so we decided to use all features for Model A in all tasks.
-We don't know the exact impact of the wrongly implemented type-token ratio feature.
+We do not know the exact impact of the wrongly implemented type-token ratio feature.
 Instead of the context's vocabulary size, we divided the size of document's vocabulary with the context size so this feature had the same value in all vectors.
@@
 We selected an algorithm and hyperparameters that achieved the best performance on the training set (since this is an unsupervised approach), and reported the final performance on the test set.
-We didn't include the k-means algorithm in clustering model selection since we used it for context size estimation.
+We did not include the k-means algorithm in clustering model selection since we used it for context size estimation.
 
@@
 Finally, from all results on training set we chose (\texttt{eps=0.23, min\_samples=64, metric="cosine"}) for the final hyperparameters.
-This wasn't the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document, and performed quite fast but again didn't estimate the correct number of clusters in most cases.
-If some samples weren't clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context weren't clustered.
+This was not the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document, and performed quite fast but again did not estimate the correct number of clusters in most cases.
+If some samples were not clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context were not clustered.
 
@@
 Based on ratios of relative improvements in the score between consecutive $k$-s, it chooses the $k$ giving the best ratio modulated with a modulation function dependent on $k$, simply $k^\alpha$ was chosen, where $\alpha$ is selected using linear search.
-Being limited in time, we didn't put much effort into optimizing the selection of the best number of clusters.
+Being limited in time, we did not put much effort into optimizing the selection of the best number of clusters.
 Moreover, even if knowing the number of clusters in advance, it seems that even the transformed features are not satisfactory for correct clustering.

### 2017-07-05 paper/paper.tex
Fixed related work.

@@
 \abstract{ 
-In this paper we present an approach trying to solve the PAN 2016 author diarization and intrinsic plagiarism detection problem.
+In this paper we present an approach to tackle the PAN 2016 author diarization and intrinsic plagiarism detection problem.
 We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window.
@@
 \section{Introduction}
-In this paper we will focus on the author diarization task proposed on the PAN 2016 competition\footnote{\url{http://pan.webis.de/clef16/pan16-web/author-identification.html}}.
-The aim of this task is to decompose a document into its authorial parts, i.e.
-to split a text into segments and assign an author to every segment \citep{koppel-2011,aldebei-2015}.
+In this paper we will focus on the author diarization task proposed on the PAN 2016 competition.\footnote{\url{http://pan.webis.de/clef16/pan16-web/author-identification.html}} The aim of this task is to decompose a document into its authorial parts, i.e., to split a text into segments and assign an author to every segment \citep{koppel-2011,aldebei-2015}.
 This is one of the unsupervised variants of a well known authorship attribution problem since text samples of known authorship are not available \citep{rosso-2016}.
@@
 
-For each of the three subtasks a training set is publicly available\footnotemark[1].
-\citet{rosso-2016} explain that they are collections of various documents which are part of Webis-TRC-12 dataset \citep{potthast-2013}.
-Every document in that dataset is constructed from texts of various search results (i.e.
-authors) for one of the 150 topics in total.
+For each of the three subtasks a training set is publicly available.\footnotemark[1] \citet{rosso-2016} explain that they are collections of various documents which are part of Webis-TRC-12 dataset \citep{potthast-2013}.
+Every document in that dataset is constructed from texts of various search results (i.e., authors) for one of the 150 topics in total.
 By varying different parameters such as the number and proportion of the authors, places in a document where an author switch occurs (between words, sentences or paragraphs), three training and test sets were generated \citep{rosso-2016}.
@@
 The basic assumption in authorship analysis is that texts of different authors are mutually separable because each author has a more or less unique writing style \citep{stamatatos-2009a,ding-2016}.
-More precisely, \citet{koppel-2009} explain that methods used in authorship analysis must be able to distinguish writing styles, but also tolerate shallow differences within the same style because an author's stylistic habits can consciously or unconsciously vary over time.
-Therefore, most of related work tries to find better features and methods which writing style will be quantified and measured with.
+Therefore, the most of related work tries to distinguish writing styles by finding better features and methods which writing style will be quantified and measured with.
 
-\citet{zu-2006} have manually created a labelled corpus of plagiarized documents and used it for the intrinsic plagiarism detection task.
-They used average sentence length, part of speech tags, average stop word number and the averaged word frequency class as input features for their linear discriminant analysis and support vector machine (SVM) models.
-They approached that task in a supervised fashion.
+\citet{zu-2006} used the average sentence length, part of speech tags, the average stop word number and the averaged word frequency class as input features for their linear discriminant analysis and support vector machine (SVM) models.
+\citet{stamatatos-2009b} introduced a sliding window approach with character tri-grams as input features for a style change function whose peaks indicate positions in the document where style changes occur.
+This is similar to an outlier detection approach from \citet{stein-2011}, but they applied a naive Bayes’ algorithm.
+\citet{rahman-2015} also used a sliding window and an SVM, but introduced new kinds of information theoretical features.
 
-\citet{stamatatos-2009b} uses normalized occurrence of character tri-grams as features to represent a document's profile.
-Using a sliding window of fixed length he creates such profiles for every window position and compares them with the profile of the whole document.
-The result of the comparison is a style change function whose peaks indicate positions in the document where style changes occur.
-All values above some predefined threshold are considered indicators of plagiarism.
-
-\citet{rahman-2015} classifies sections of documents from the PAN 2011 dataset with the help of an SVM.
-Those sections are again obtained by sliding a window of fixed length over the document.
-He also proposed new kinds of information theoretical features - entropy, relative entropy, correlation coefficient and $n$-gram frequency class calculated from character tri-gram frequency profiles of each window and the whole document.
-The approach also uses function word bi-gram and tri-gram frequency profiles with $1$, $2$, $3$ and $4$ skips.
-The value of the style change function introduced by \citet{stamatatos-2009b} is also incorporated into the feature vectors.
-
-\citet{stein-2011} defined IPD as a one class classification problem where the parts of text written by the main author are associated to the target class and the other parts of text are outliers.
-To find them, they estimate probability distributions of various stylistic features for the target class and outliers.
-Then a naive Bayes' algorithm is applied to feature vectors whose values lie outside the predefined uncertainty intervals.
-Additional outlier post-processing methods were also tested.
-The most successful was the unmasking technique described by \citet{koppel-2009}.
-The main sense of unmasking is to iteratively remove the best features that distinguish two classes and observe the speed with which cross-validation accuracy of the again trained classifier drops.
-If the drop is slow and smooth, the outliers are indeed outliers because after $n$ iterations of removing discriminative features they are still separable from the main author's work.
-
-\citet{koppel-2011} used two staged approach in clustering of pre-segmented mixed biblical text written by two authors.
-First they used normalized cuts algorithm with cosine similarity to obtain initial clusters of segments which were represented only by normalized counts of synonyms from Hebrew synsets.
-Samples from initial clusters were separated into core and non-core samples via an iterative procedure, and the core ones were labelled.
-A SVM classifier was used to classify non-core samples, but now represented with bag-of-words feature vectors.
-The whole approach resulted with very good clusters.
-They also tried this method on an unsegmented case.
-The text was first split in a way that minimizes doubly-represented synonyms in segments and the same procedure was repeated.
-The clustering performance was lower than in pre-segmented case.
-
-\citet{brooke-2013} conclude that a very good initial segmentation of text, at least in poems written by T.
+\citet{koppel-2011} used normalized cuts algorithm to  obtain initial clusters of segments which were represented only by normalized counts of synonyms from Hebrew synsets.
+An SVM was then used to classify bag-of-words feature vectors of non-representative cluster samples.
+\citet{brooke-2013} concluded that a very good initial segmentation of text, at least in poems written by T.
 S.
 Elliot, is needed for good performance of their modified k-means algorithm in clustering of voices.
-Except common character, lexical and syntactic features, they use features such as average frequency in a large external corpus \citep{brants-2006}.
-One of the most promising feature they considered is the centroid of $20$ dimensional distributional vectors obtained by applying latent semantic analysis on a large web corpus \cite{landauer-1997}.
 
 The works by \citet{kuznetsov-2016} and \citet{sittar-2016} were submitted on the PAN 2016 competition for three aforementioned tasks.
-For the Task \emph{a}, \citet{kuznetsov-2016} trained a Gradient Boosting Regression Trees (GBRT) model on the PAN 2011 dataset as a style change function used for threshold based outlier detection.
-Every sentence was vectorized using word frequencies, $n$-gram frequencies, punctuation symbols and the universal POS tags count, sentence length and mean length of sentence words.
-The final input to the model is the concatenation of the center sentence vector and vectors representing the context of size $\pm2$.
-In Task \emph{b} they used a Hidden Markov Model with Gaussian Emissions for document segmentation over the same sentence scores from Task \emph{a}.
-To estimate the unknown number of authors $n$ in Task \emph{c}, they define a cluster discrepancy measure $Q(n)$ and choose the $n\in\{2..20\}$ which maximizes the measure.
+Their approaches mostly focused on initial segmentation with the help of a style change function and clustering as the final step.
+To estimate the unknown number of authors in Task \emph{c}, \citet{kuznetsov-2016} defined a cluster discrepancy measure which was than maximized, while \citet{sittar-2016} generated that number randomly.
 
-\citet{sittar-2016} use the k-means algorithm and a measure called \emph{ClustDist} to compute distaces between sentences and the document.
-For Task \emph{c}, the number of groups for clustering is generated randomly for each document.
-Although they defined a \emph{ClustDist} score for a single sentence as the average distance between the current and every other sentence vector, which is again a similar concept like a style change function, in the provided example they used only a sum of unknown distance measures.
-The sentences are represented with $15$ lexical features including average word and sentence lengths, counts and ratios of characters, digits, uppercase letters, spaces and tabs.
-
-The most of the described approaches combine supervised and unsupervised methods and operate on the level of longer text segments or sentences.
+The most of the described approaches operate on the level of longer text segments or sentences.
 Since the style change in our tasks can occur even between two tokens in the same sentence, we wanted our model to be able to work on the token level.
@@
 
-Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e.
-$\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$.
-The goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e.
-makes good predictions given unseen documents.
+Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e., $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$.
+The goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e., makes good predictions given unseen documents.
 
@@
 Let $(a_i)_{i=1}^n$ be the sequence of true author labels with elements from $\{1..c\}$.
-We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_\mathrm{b}'}\rightarrow\mathbb{R}^{n_\mathrm{t}}$ with trainable parameters $\vect{\theta}_T$, i.e.
-we want to maximize segregation and compactness of groups of transformed feature vectors grouped by their target author label.
+We want to maximize the \emph{clusterability} of the feature vectors obtained by the feature transformation $T:\mathbb{R}^{n_\mathrm{b}'}\rightarrow\mathbb{R}^{n_\mathrm{t}}$ with trainable parameters $\vect{\theta}_T$, i.e., we want to maximize segregation and compactness of groups of transformed feature vectors grouped by their target author label.
 Let $(\vect{t}_i)_{i=1}^n = (T(\boldsymbol{b}_i'))_{i=1}^n = f_\mathrm{t}((\vect{b}_i)_{i=1}^n)$ be the sequence of transformed feature vectors with elements from $\mathbb{R}^{n_\mathrm{t}}$.
@@
 $L_\mathrm{c}$ is proportional to the average variance of groups, and $L_\mathrm{s}$ penalizes centroids being too close to each other.
-Let $N_a$ represent the number of tokens associated with author $a$, i.e.
-$N_a = \sum_{i=1}^n[a_i=a]$, where, for $\varphi$ being a logical proposition $[\varphi]$ evaluates to either $1$ if $\varphi$ is true or $0$ otherwise.
+Let $N_a$ represent the number of tokens associated with author $a$, i.e., $N_a = \sum_{i=1}^n[a_i=a]$, where, for $\varphi$ being a logical proposition $[\varphi]$ evaluates to either $1$ if $\varphi$ is true or $0$ otherwise.
 %, the following notation\footnote{It is called \emph{the Iverson bracket}.} is introduced:
@@
 \end{equation}
-The transformation is implemented using TensorFlow\footnote{\url{https://www.tensorflow.org}}.
-Parameters are randomly initialized with values from a truncated normal distribution with standard deviation $0.1$.
+The transformation is implemented using TensorFlow.\footnote{\url{https://www.tensorflow.org}} Parameters are randomly initialized with values from a truncated normal distribution with standard deviation $0.1$.
 It is trained on-line (one document per optimization step) using RMSProp \citep{tielman-2012} with default parameters and learning rate $5\times 10^{-4}$.
@@
 Instead of the context's vocabulary size, we divided the size of document's vocabulary with the context size so this feature had the same value in all vectors.
-
-\subsection{Experimental setup}
-
-In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach} Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and clustering algorithm's hyperparameters.
-Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.
-All the source code for our experiments is available in our repository\footnote{\url{https://github.com/Coolcumber/inpladesys/}}.
-
-\paragraph{Model A.} 
-Sliding widow context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
-We used a whole dataset and default implementation of k-means from scikit-learn and tested different values.
-The best result for Task \emph{a} was $\mathit{cs}_\mathrm{a}=16$ and for Task \emph{b} $\mathit{cs}_\mathrm{b}=140$.
-For Task \emph{c}, we left $\mathit{cs}_\mathrm{c}=140$ as for Task \emph{b}.
-%This hyperparameter probably depends on document's length to a certain extent.
-If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs.
-$16, 140, 140$).
-However, they are probably biased to a certain extent.
-
-For clustering algorithm selection we used manual search over several algorithms.
-We split the whole dataset into a training and a test set.
-For each algorithm we were examining, a grid search of its hyperparameters was performed on the training set.
-We selected an algorithm and hyperparameters that achieved the best performance on the training set (since this is an unsupervised approach), and reported the final performance on the test set.
-We did not include the k-means algorithm in clustering model selection since we used it for context size estimation.
-
-In Task \emph{a}, we used $50\%$ of the dataset as a training set, and the other half as a test set.
-Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results.
-Other algorithm which we evaluated was hierarchical agglomerative clustering which achieved the best macro $F_1$ (described in subsection \ref{subsec:evaluation-measures}) with cosine affinity and average linkage on the train set.
-We report its result on the test set.
-
-For Task \emph{b} we split the dataset in two halves as well.
-Grid search for the best hyperparameters was performed for agglomerative clustering.
-The best performance on the training set was obtained with Euclidean affinity and average linkage.
-For Task \emph{c} we should have somehow determined the number of clusters.
-Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e.
-this is not a hyperparameter which should be known in advance.
-Since we noticed that grid searches take a lot of time, we reduced a training set from $50\%$ to $10\%$ and repeated all experiments.
-We tested DBSCAN and affinity propagation algorithms.
-
-The best results on Task \emph{c} were obtained with DBSCAN.
-We noticed that the number of clusters  estimated with the best hyerparameters (\texttt{eps=100, min\_samples=71, metric="manhattan"}) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
-In all grid searches we used the BCubed $F_1$-score and only DBSCAN achieved acceptable performance.
-Our opinion is that this was a consequence of a larger number of smaller clusters which had a positive influence on BCubed precision and therefore on overall performance.
-
-Since the model with the best achieved Bcubed $F_1$-score ($0.61$) is not of practical use in real life applications because the number of clusters is always wrongly estimated, we decided to repeat the grid search in Task \emph{c} for DBSCAN, but this time we used the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
-Finally, from all results on training set we chose (\texttt{eps=0.23, min\_samples=64, metric="cosine"}) for the final hyperparameters.
-This was not the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document, and performed quite fast but again did not estimate the correct number of clusters in most cases.
-If some samples were not clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context were not clustered.
-
-\paragraph{Model B.} 
-For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).
-The length of the sliding window is set to $120$ tokens.
-Model B uses k-means clustering.
-We have chosen two trainable feature transformations: linear and elementwise linear (weighting).
-For both of the transformations $5\times 10^{-4}$ was chosen for the learning rate.
-All the hyperparameters are selected manually by experimenting on the development dataset, which is approximately $70\%$ of the available dataset.
-$70\%$ of the development set was used for fitting basic feature extractors and learning the transformation.
-Considering the results on the validation part of the development set, not very large numbers of iterations seem to be more beneficial.
-A number of $40$ iterations was chosen for the linear transformation, and $20$ for the elementwise linear transformation.
-For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be achievable using smaller numbers like $20$, making training and clustering faster.
-
-For Task \emph{c} we have implemented a simple wrapper for the k-means algorithm that tries to predict the correct number of authors.
-It computes the k-means error for each number $k$ in the specified range for the number of clusters.
-Based on ratios of relative improvements in the score between consecutive $k$-s, it chooses the $k$ giving the best ratio modulated with a modulation function dependent on $k$, simply $k^\alpha$ was chosen, where $\alpha$ is selected using linear search.
-Being limited in time, we did not put much effort into optimizing the selection of the best number of clusters.
-Moreover, even if knowing the number of clusters in advance, it seems that even the transformed features are not satisfactory for correct clustering.
-We notice that using the correct numbers of authors compared to using a fixed $k=2$ results in relative decrease in BCubed precision, recall, and $F_1$-score by factors of $0.95$, $0.64$ and $0.79$ respectively.
-
-\subsection{Evaluation results}
 
@@
 
+\subsection{Experimental setup}
+
+In every task we used the same tokenization procedure as described in section \ref{sec:the-proposed-approach} Model A covers all three tasks and has several hyperparameters for each of them: context size, clustering algorithm and clustering algorithm's hyperparameters.
+Model B uses a smaller set of features and trainable feature transformations with most of the hyperparameters equal among the tasks.
+All the source code for our experiments is available in our repository.\footnote{\url{https://github.com/Coolcumber/inpladesys/}}
+
+\paragraph{Model A.} 
+Sliding widow context size was determined manually for tasks \emph{a} and \emph{b}, in a similar way as feature selection.
+We used a whole dataset and default implementation of k-means from scikit-learn and tested different values.
+The best result for Task \emph{a} was $\mathit{cs}_\mathrm{a}=16$ and for Task \emph{b} $\mathit{cs}_\mathrm{b}=140$.
+For Task \emph{c}, we left $\mathit{cs}_\mathrm{c}=140$ as for Task \emph{b}.
+%This hyperparameter probably depends on document's length to a certain extent.
+If we compare that sizes with the average document lengths in tokens across datasets, we can see that there is a correspondence ($1679, 3767, 3298$ vs.
+$16, 140, 140$).
+However, they are probably biased to a certain extent.
+
+For clustering algorithm selection we used manual search over several algorithms.
+We split the whole dataset into a training and a test set.
+For each algorithm we were examining, a grid search of its hyperparameters was performed on the training set.
+We selected an algorithm and hyperparameters that achieved the best performance on the training set (since this is an unsupervised approach), and reported the final performance on the test set.
+We did not include the k-means algorithm in clustering model selection since we used it for context size estimation.
+
+In Task \emph{a}, we used $50\%$ of the dataset as a training set, and the other half as a test set.
+Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results.
+Other algorithm which we evaluated was hierarchical agglomerative clustering which achieved the best macro $F_1$ (described in subsection \ref{subsec:evaluation-measures}) with cosine affinity and average linkage on the train set.
+We report its result on the test set.
+
+For Task \emph{b} we split the dataset in two halves as well.
+Grid search for the best hyperparameters was performed for agglomerative clustering.
+The best performance on the training set was obtained with Euclidean affinity and average linkage.
+For Task \emph{c} we should have somehow determined the number of clusters.
+Due to a lack of time we decided to test algorithms which can determine this number automatically, i.e., this is not a hyperparameter which should be known in advance.
+Since we noticed that grid searches take a lot of time, we reduced a training set from $50\%$ to $10\%$ and repeated all experiments.
+We tested DBSCAN and affinity propagation algorithms.
+
+The best results on Task \emph{c} were obtained with DBSCAN.
+We noticed that the number of clusters  estimated with the best hyerparameters (\texttt{eps=100, min\_samples=71, metric="manhattan"}) was in almost every case greater than a real one, and solid number of examples were not even clustered because they were not close enough to any core sample to be a part of a cluster.
+In all grid searches we used the BCubed $F_1$-score and only DBSCAN achieved acceptable performance.
+Our opinion is that this was a consequence of a larger number of smaller clusters which had a positive influence on BCubed precision and therefore on overall performance.
+
+Since the model with the best achieved Bcubed $F_1$-score ($0.61$) is not of practical use in real life applications because the number of clusters is always wrongly estimated, we decided to repeat the grid search in Task \emph{c} for DBSCAN, but this time we used the Calinski-Harabaz index defined by \citet{calinski-1974} as evaluation measure since it does not require the real number of clusters for clustering evaluation.
+Finally, from all results on training set we chose (\texttt{eps=0.23, min\_samples=64, metric="cosine"}) for the final hyperparameters.
+This was not the best combination, but it produced relatively acceptable amount of noisy (non-clustered) elements per document, and performed quite fast but again did not estimate the correct number of clusters in most cases.
+If some samples were not clustered, we assigned them the majority label from neighborhood (context) of size $10$ ($5$ on each side), or the majority label from all samples if samples in the context were not clustered.
+
+\paragraph{Model B.} For Model B, we have decided to use a smaller set of basic features: character tri-gram counts (for $120$ tri-grams), stop word counts, average token length and bag-of-words (for $120$ words).
+The length of the sliding window is set to $120$ tokens.
+Model B uses k-means clustering.
+We have chosen two trainable feature transformations: linear and elementwise linear (weighting).
+For both of the transformations $5\times 10^{-4}$ was chosen for the learning rate.
+All the hyperparameters are selected manually by experimenting on the development dataset, which is approximately $70\%$ of the available dataset.
+$70\%$ of the development set was used for fitting basic feature extractors and learning the transformation.
+Considering the results on the validation part of the development set, not very large numbers of iterations seem to be more beneficial.
+A number of $40$ iterations was chosen for the linear transformation, and $20$ for the elementwise linear transformation.
+For the output dimension of the linear transformation we have chosen $n_\mathrm{t}=40$, though not much different results seem to be achievable using smaller numbers like $20$, making training and clustering faster.
+
+For Task \emph{c} we have implemented a simple wrapper for the k-means algorithm that tries to predict the correct number of authors.
+It computes the k-means error for each number $k$ in the specified range for the number of clusters.
+Based on ratios of relative improvements in the score between consecutive $k$-s, it chooses the $k$ giving the best ratio modulated with a modulation function dependent on $k$, simply $k^\alpha$ was chosen, where $\alpha$ is selected using linear search.
+Being limited in time, we did not put much effort into optimizing the selection of the best number of clusters.
+Moreover, even if knowing the number of clusters in advance, it seems that even the transformed features are not satisfactory for correct clustering.
+We notice that using the correct numbers of authors compared to using a fixed $k=2$ results in relative decrease in BCubed precision, recall, and $F_1$-score by factors of $0.95$, $0.64$ and $0.79$ respectively.
+
+\subsection{Evaluation results}
+
 We have evaluated our models using micro-averaged and macro-averaged precision, recall and $F_1$-score for intrinsic plagiarism detection and the analogous BCubed scores for author diarization, as defined in subsection \ref{subsec:evaluation-measures} The results of our models are compared to the results of our baselines, as well as the results of the two teams that took part in the PAN 2016 competition for this problem.

### 2017-07-05 paper/paper.tex
Removed an mathematical expression

--- 2017-07-04 paper/paper.tex
@@
 A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ is a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is associated with the same author label.
-For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
-\begin{equation}
-	\bigcup_{s\in S}s = T_D  \wedge \bigcap_{s\in S}s = \{\}.
-\end{equation}
+For a segmentation to be valid, the segments must cover all terms in the document and not overlap.
+
 The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$.
-
 Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e.

### 2017-07-06 paper/paper.tex
Fixed error.

--- 2017-07-05 paper/paper.tex
@@
 A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ is a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is associated with the same author label.
-For a segmentation to be valid, the segments must cover all terms in the document and not overlap:
-\begin{equation}
-	\bigcup_{s\in S}s = T_D  \wedge \bigcap_{s\in S}s = \{\}.
-\end{equation}
+For a segmentation to be valid, the segments must cover all terms in the document and not overlap.
+
 The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$.
-
 Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e., $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$.

### 2017-08-22 paper/paper.tex
no message

@@
 \paragraph{Basic feature extraction.} 
-We defined the stylistic context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-cs}^{i-1} \cup \{t_k\}_{k=i+1}^{i+cs}$ where $cs$ is a context size.
+We define the stylistic context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-cs}^{i+cs}\setminus\{t_i\}$ where $cs$ is a context size.
 From each context we extracted the most used stylometric features which we found in previous work.

### 2017-08-30 paper/paper.tex
Simplified model description, shortened

@@
 
-Let $\Delta$ be the domain of documents.
-We define a document $D\in \Delta$ as a finite sequence of tokens $(t_i)_{i=1}^n$, where $n$ can differ among documents.
+We define a document $D$ as a finite sequence of tokens $(t_i)_{i=1}^n$, where $n$ can differ among documents.
 Given a document, each of its tokens is unique and defined by its character sequence and position in the document.
-Therefore, a document can be equivalently represented by its set of tokens $T_D=\{t_i\}_{i=1}^n$.
+Therefore, a document can be equivalently represented by its set of tokens $\{t_i\}_{i=1}^n$.
 
@@
 The labels $a_i$ are indices of authors of the document.
-Each token $t_i\in T_D$ is assigned a document-level label $a_i \in \{1..c\}$ associating it to one of $c$ authors.
+Each token $t_i$ is assigned a document-level label $a_i \in \{1..c\}$ associating it to one of $c$ authors.
 The exact value of the label is not important.
@@
 Therefore, there are $m!$ equivalent such mappings given a document.
-In the case of intrinsic plagiarism detection, there are only $2$ labels: $0$ representing the main author, and $1$ representing plagiarized text.
+In the case of intrinsic plagiarism detection, there are only $2$ labels: $0$ (the main author), and $1$ (plagiarized text).
 
-Equivalently, the codomain of the mapping can also be defined as a set of segmentations $\Sigma$.
-A segmentation $S\in \Sigma$ is a minimal set of segments, where each segment $s$ is a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is associated with the same author label.
+Equivalently, the codomain of the mapping can also be defined as a set of segmentations.
+A segmentation $S$ is a minimal set of segments, where each segment $s$ is a set of consecutive tokens $\{t_i\}_{i=i_1}^{i_2}$ where each token is associated with the same author label.
 For a segmentation to be valid, the segments must cover all terms in the document and not overlap.
 
-The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma: \Delta\rightarrow\Sigma$.
-Let $\mathcal{D} \subset \Delta\times\Sigma$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e., $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$.
-The goal is to find the model $\hat{\sigma}$ that best approximates the correct mapping $\sigma$, i.e., makes good predictions given unseen documents.
+The correct mapping of a documents to the corresponding segmentations will be denoted with $\sigma$.
+Let $\mathcal{D}$ be a dataset consisting of a finite set of pairs of documents and corresponding segmentations, i.e., $\mathcal{D} = \{\left(D_i, \sigma(D_i)\right)\}_{i=1}^N$.
+The goal is to find the model $\hat{\sigma}$ that approximates the correct mapping $\sigma$ and generalizes well.
 
@@
 R_\mathrm{\mu} &= \frac{l(\hat{S}_\mathrm{tp})}{l(S_\mathrm{p})}, \\
-F_\mathrm{\mu} &= \frac{2}{P_\mathrm{\mu}^{-1}+R_\mathrm{\mu}^{-1}}.
+F_\mathrm{\mu} &= 2(P_\mathrm{\mu}^{-1}+R_\mathrm{\mu}^{-1})^{-1}.
 \end{align}
@@
 		\frac{{\sum_{s\in \hat{S}_\mathrm{p}} l(s\cap\hat{s})}}{l(s)}, \\
-F_\mathrm{M} &= \frac{2}{P_\mathrm{M}^{-1}+R_\mathrm{M}^{-1}}.
+F_\mathrm{M} &= 2(P_\mathrm{M}^{-1}+R_\mathrm{M}^{-1})^{-1}.
 \end{align}
@@
 	\sum_{s\in S_i}	\sum_{\hat{s}\in\hat{S}_j} l(s\cap \hat{s})^2, \\
-F_{\mathrm{B}^3} &= \frac{2}{P_{\mathrm{B}^3}^{-1}+R_{\mathrm{B}^3}^{-1}}.
+F_{\mathrm{B}^3} &= 2(P_{\mathrm{B}^3}^{-1}+R_{\mathrm{B}^3}^{-1})^{-1}.
 \end{align}
@@
 
-Our approach can generally be described as a pipeline $P = (f_\mathrm{b}:\Delta\rightarrow \Phi_{n_\mathrm{b}}, f_\mathrm{t}:\Phi_{n_\mathrm{b}}\rightarrow \Phi_{n_\mathrm{t}}, f_\mathrm{c}:\Phi_{n_\mathrm{t}}\rightarrow C)$.
-Here $\Delta$ is the tokenized document domain as defined in section \ref{sec:author-diraization} $\Phi_{n_\mathrm{b}}$ and $\Phi_{n_\mathrm{t}}$ are sets of variable-length sequences of feature vectors with dimension $n_\mathrm{b}$ and $n_\mathrm{t}$ respectively.
-$n_\mathrm{b}$ and $n_\mathrm{t}$ can either be fixed or depend on the document being processed.
-$C$ is the set of all sequences of length $n$ (the number of tokens in the document) with elements being indices of authors/clusters.
+Our approach can generally be described as a pipeline of three transformations: basic feature extraction $f_\mathrm{b}$, feature transformation $f_\mathrm{t}$ and clustering $f_\mathrm{c}$.
 
 The basic feature extractor denoted with $f_\mathrm{b}$ is used to extract stylistic features from the contexts of all tokens.
-If $D$ is a document with $n$ tokens, the basic feature extractor outputs a sequence of $n$ feature vectors, each vector representing the context of one token.
-$n_\mathrm{b}$ denotes the dimension of those vectors.
-The next step in the pipeline is the feature transformation $f_\mathrm{t}$ that maps the basic features to a space that they can be better clustered in.
-The dimension of the new feature space $n_\mathrm{t}$ generally does not equal $n_\mathrm{b}$.
+If $D$ is a document with $n$ tokens, the basic feature extractor outputs a sequence of $n$ $n_\mathrm{b}$-dimensional feature vectors representing the contexts of tokens.
+The next step in the pipeline is the feature transformation $f_\mathrm{t}$ that maps the basic features to a $n_\mathrm{t}$-dimensional space that they can be better clustered in.
 The final step in the pipeline is clustering denoted with $f_\mathrm{c}$.
@@
 
-The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D\in\Delta$, (2) for all tokens, features are extracted from their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (\vect{t}_i)_{i=1}^n = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n=|T_D|$, and (4) a segmentation $\hat{S}$ is generated based on the document $D$ and the sequence of predicted author labels.
+The following steps are done in predicting the segmentation: (1) raw text is tokenized giving a sequence of tokens $D$, (2) for all tokens, features are extracted from their contexts, giving a sequence of feature vectors $\phi_\mathrm{t} = (f_\mathrm{t}\circ f_\mathrm{b})(D)$, (3) the tokens are clustered based on $\phi_\mathrm{t}$, giving a sequence of author labels $(a_i)_{i=1}^{n}$, where $n$ is the number of tokens in $D$, and (4) a segmentation $\hat{S}=f_\mathrm{c}(\phi_\mathrm{t})$ is generated based on the obtained clusters.
 
-We develop two variants of our model which we will refer to as \emph{Model A} and \emph{Model B}.
+We develop two variants of our model which we will refer to as Model A and Model B.
 They are mainly differentiated by the fitting of the basic feature extractor, feature transformation learning and in the feature transformation.
@@
 Counts of a maximum of 100 unigrams were used.
-	\item \emph{Type-token ratio}.
-We wanted to use that feature to measure the vocabulary richness in a token's context, but after we finished with performance evaluations we realized that there was a bug in implementation and its impact on final results was unknown to us.
-The feature should be calculated as the ratio of vocabulary size and total number of tokens of the text \citep{stamatatos-2009a}.
+	\item \emph{Type-token ratio}\footnote{We wanted to use that feature to measure the vocabulary richness in a token's context, but after we finished with performance evaluations we realized that there was a bug in implementation and its impact on final results was unknown to us.}.
+This feature is the ratio of vocabulary size and total number of tokens of the text \citep{stamatatos-2009a}.
 \end{itemize}
@@
 $L_\mathrm{c}$ is proportional to the average variance of groups, and $L_\mathrm{s}$ penalizes centroids being too close to each other.
-Let $N_a$ represent the number of tokens associated with author $a$, i.e., $N_a = \sum_{i=1}^n[a_i=a]$, where, for $\varphi$ being a logical proposition $[\varphi]$ evaluates to either $1$ if $\varphi$ is true or $0$ otherwise.
+Let $N_a$ represent the number of tokens associated with author $a$, i.e., $N_a = \sum_{i=1}^n[a_i=a]$, where, $[\varphi]$ evaluates to $1$ if $\varphi$ is true and $0$ otherwise.
 %, the following notation\footnote{It is called \emph{the Iverson bracket}.} is introduced:
@@
 For both Models A and B we calculated standard errors and wanted to obtain $95\%$ t-based confidence intervals.
-Since the sample sizes from all test sets but \emph{a} are less than $30$, a normality test\footnote{\url{https://docs.scipy.org/doc/scipy-0.19.0/reference/generated/scipy.stats.normaltest.html}} at $p=0.05$ was performed first.
+Since the test sets are small, D’Agostino and Pearson’s normality test at $p=0.05$ was performed first.
 The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution.

### 2017-08-30 paper/paper.tex
Made the paper a bit shorter

@@
 \end{align}
-The macro-average evaluation measures treat all plagiarism segments as equally important and are not affected by their lengths:
+The macro-average evaluation measures treat all plagiarism segments equally regardless of their lengths:
 \begin{align}
@@
 \paragraph{Basic feature extraction.} 
-We define the stylistic context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-cs}^{i+cs}\setminus\{t_i\}$ where $cs$ is a context size.
-From each context we extracted the most used stylometric features which we found in previous work.
-The features that we have considered in our models are:
+We define the context of a token $t_i$ as a set of tokens $\{t_k\}_{k=i-cs}^{i+cs}\setminus\{t_i\}$ where $cs$ is context size.
+Based on previous work, we extract the most useful stylometric features from each context.
+The features considered in our models are:
 \begin{itemize}
@@
 	\item \emph{Stop words}.
-According to \citet{stamatatos-2009a}, sometimes also called \emph{function words}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
+According to \citet{stamatatos-2009a}, these are the most common used topic-independent words in text, such as articles, prepositions, pronouns and others.
 They are used unconsciously and found to be one of the most discriminative features in authorship attribution since they represent pure stylistic choices of authors' \citep{burrows-1987,argamon-2005}.
@@
 	\item \emph{Special characters}.
-We used counts of all character sequences which satisfied a regular expression defined as \verb/[^\\w]{1,4}/.
+We used counts of all character sequences which satisfied the following regular expression: \verb/[^\\w]{1,4}/.
 Although character $n$-grams can catch the use of those character sequences, we wanted to have a distinct feature for that purpose since \citet{koppel-2009} mentioned that authors can have different punctuation habits.
@@
 Bag of words text representation more captures content, rather than style \citep{stamatatos-2009a}.
-We included this feature because it boosted performance of our initial testing, even without words been previously stemmed or lemmatized (stop words were excluded).
-Counts of a maximum of 100 unigrams were used.
-	\item \emph{Type-token ratio}\footnote{We wanted to use that feature to measure the vocabulary richness in a token's context, but after we finished with performance evaluations we realized that there was a bug in implementation and its impact on final results was unknown to us.}.
+We include this feature because it boosted performance in our initial testing.
+Counts of at most 100 unigrams are used.
+	\item \emph{Type-token ratio}\footnote{We wanted to use this feature to measure the vocabulary richness, but after we have evaluated performance, we realized that there was a bug in our implementation.
+The inpact on the results is unknown to us.}.
 This feature is the ratio of vocabulary size and total number of tokens of the text \citep{stamatatos-2009a}.

### 2017-09-01 paper/paper.tex
Merged 2 paragraphs
Improved some text

@@
 Our approach can generally be described as a pipeline of three transformations: basic feature extraction $f_\mathrm{b}$, feature transformation $f_\mathrm{t}$ and clustering $f_\mathrm{c}$.
-
 The basic feature extractor denoted with $f_\mathrm{b}$ is used to extract stylistic features from the contexts of all tokens.
@@
 For both Models A and B we calculated standard errors and wanted to obtain $95\%$ t-based confidence intervals.
-Since the test sets are small, D’Agostino and Pearson’s normality test at $p=0.05$ was performed first.
+Since the test sets are small, D’Agostino and Pearson’s normality test with p-value $0.05$ was performed first.
 The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution.
@@
 Model A also achieved the best, but actually not very good performance on the Task \emph{b} with $(0.57, 0.67)$ $95\%$ confidence interval.
-Although Model B behaved reasonably well on the Task \emph{c}, a better way of estimating a true number of clusters is needed.
+Although Model B behaved reasonably well on the Task \emph{c}, a better way of estimating the number of clusters is needed.
 

### 2017-12-31 paper/paper.tex
no message
Weird fixes.

@@
 We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window.
-There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt if for clustering with a trainable feature transformation.
+There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt it for clustering with a trainable feature transformation.
 We have evaluated our approach on the available datasets from PAN 2016.
@@
 For both Models A and B we calculated standard errors and wanted to obtain $95\%$ t-based confidence intervals.
-Since the test sets are small, D’Agostino and Pearson’s normality test with p-value $0.05$ was performed first.
+Since the test sets are small, D’Agostino and Pearson’s normality test with signficance level $0.05$ was performed first.
 The Model A data in all tasks did not provide enough evidence to reject the null hypothesis that a sample comes from a normal distribution.

### 2018-01-06 paper/paper.tex
Fixed an error

@@
 
-\name{Ivan Grubišić, Milan Pavlović, Mate Šimović}
+\name{Ivan Grubišić, Milan Pavlović}
 
@@
 Unska 3, 10000 Zagreb, Croatia\\ 
-\texttt{\{ivan.grubisic, milan.pavlovic, mate.simovic\}@fer.hr}\\
+\texttt{\{ivan.grubisic, milan.pavlovic\}@fer.hr}\\
 }
@@
 We propose a method for unsupervised text diarization based on clustering of tokens using contextual style features obtained with a sliding window.
-There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adopt it for clustering with a trainable feature transformation.
+There are two variants of our approach - one that uses different features based on the document being analyzed, and one that uses a fixed feature space and tries to adapt it for clustering with a trainable feature transformation.
 We have evaluated our approach on the available datasets from PAN 2016.
